### 2014-02-05 docs/thesis/LaTeX_installation_guidelines.tex
mathematica notebooks and thesis commit

\documentclass[a4paper]{article}

\usepackage[bookmarks=false]{hyperref}
\hypersetup{colorlinks,%
	linkcolor=magenta,%
	citecolor=blue}
\hypersetup{pdftitle={Install and use LaTeX for your papers},%
	pdfauthor={Christophe Yamahata},%
	pdfdisplaydoctitle=true}

\title{Using \LaTeX\ to submit manuscripts to peer reviewed journals.}

\author{Christophe Yamahata \footnote{\href{mailto:christophe.yamahata@a3.epfl.ch}{christophe.yamahata@a3.epfl.ch}}}

\date{May 17$^{th}$, 2008}

\begin{document}

\maketitle

\begin{abstract}
Hereafter, I describe all the steps that have to  be followed if you want to 
prepare scientific papers with \LaTeX. This information is for a PC working 
under Windows XP or Vista. I take the example of a submission to 
J. Micromech. Microeng. but you can also find templates for the IEEE J. MEMS
or any \emph{serious} journal.
\end{abstract}

\section*{Basic steps}

\begin{flushleft}
\begin{enumerate}
\item Download the complete MikTeX 2.9 distribution \cite{MikTeX} \\
    (using `Net Installer': \href{http://miktex.org/2.9/setup}{http://miktex.org/2.9/setup}). \\
    It can take time if your network connection is slow\ldots

\item Install MikTeX using the same setup executable file.
    This step also takes long time (typically $\sim 30~$min).

\item ONLY ONCE MikTeX has been installed, you can download and install WinShell (\href{http://www.winshell.de/}{http://www.winshell.de/}) \cite{WinShell}.
	\begin{itemize}
    \item  Open `Winshell.exe'
    \item You can check in ``Options'' $>$ ``Programm Calls'' that MikTeX is the distribution used to compile \LaTeX.
	\end{itemize}

\item Create a new folder where you will copy  the \LaTeX\ template files 
	\begin{itemize}
	\item First, you can simply open the `.tex' file that I enclose in this e-mail. After conversion with PDFLaTeX, 
	it will look like the PDF file that I also enclose.
	\item Then, try with the template provided by IoP for \emph{J. Micromech. Microeng} \cite{JMM}. \\
    You can download these files and the guidelines here: \\
	\href{ftp://ftp.iop.org/pub/journals/ioplatexguidelines.zip}{ftp://ftp.iop.org/pub/journals/ioplatexguidelines.zip} \\
	\end{itemize}
\end{enumerate}
\end{flushleft}
If you need further information about the \LaTeX\ language, you can check 
``The Not So Short Introduction to \LaTeXe''. You can find it here: \\
	\indent \href{http://tobi.oetiker.ch/lshort/lshort.pdf}{http://tobi.oetiker.ch/lshort/lshort.pdf}

\begin{thebibliography}{10}
\bibitem{MikTeX} MikTeX {\emph{\href{http://www.miktex.org/}{www.miktex.org}  } }
\bibitem{WinShell} WinShell {\emph{\href{http://www.winshell.de/}{www.winshell.de}}}
\bibitem{JMM} J. Micromech. Microeng. {\emph{\href{http://www.iop.org/EJ/journal/JMM/}{www.iop.org/EJ/journal/JMM}} } 
\end{thebibliography}

\end{document}

### 2014-02-05 docs/thesis/annexes.tex
mathematica notebooks and thesis commit

\chapter{Annexes}
\label{app}

\section{Conception des masques}
\label{masque}

Le tableau \ref{masque} regoupe les dimensions du masque et les dimensions prévues .

\begin{table}[!ht]
\renewcommand{\arraystretch}{1}
\centering
\begin{tabular}{l r r }
\toprule
\textbf{}					&\multicolumn{2}{c}{\textbf{Dimensions}} \\ 
\textbf{Paramètres} 					& \textbf{sur masque}	& \textbf{sur wafer} \\
\midrule
Largeur des lames souples			& $3\mu m$ 				& $2.5\mu m$ 	\\
Largeur des lames rigides			& $2.5\mu m$ 			& $2  \mu m$ 	\\
Largeur d'une dent large			& $5 \mu m$				& $4.5 \mu m$	 \\
Largeur d'une dent étroite			& $4 \mu m$				& $3.5 \mu m$	 \\
Gap (rotor/stator)					& $1 \mu m$				& $1.5 \mu m$ 	 \\
\midrule
Largeur des lames du robot v 2.5	& $2.5\mu m$ 				& $2\mu m$ 	\\
Largeur des lames du robot v 2.0	& $2.0\mu m$ 				& $1.5\mu m$ 	\\
Largeur des lames du robot v 1.5	& $1.5\mu m$ 				& $1\mu m$ 	\\
Largeur des lames du robot v 1.0	& $1.0\mu m$ 				& $0.5\mu m$ 	\\
\bottomrule
\end{tabular}
\caption{Dimensions des paramètres sur le masque de la deuxième verison et dimensions prévues sur wafer}
\label{table:masque}
\end{table}

La fabrication et la mise au point du processus de fabrication a été donné à une personne externe. Le lecteur est invité à se référer aux annexes \ref{process flow} et \ref{runcard} pour le processus en lui-même.

\section{Constantes physiques et propriétés des matériaux}
\label{constantes}

Les valeures suivantes ont été utilisées pour les applications numériques. Afin de s'affranchir des propriétés anisotropes du silicium, les valeurs les plus contraignantes de ces propriétés ont été considérés. Un coefficient de sécurité de 10 a été pris pour les contraintes admissibles maximum.

\begin{table}[!ht]
\renewcommand{\arraystretch}{1}
\centering
\begin{tabular}{lcr@{}l}
\toprule
\textbf{Paramètres} 			& \textbf{Symboles}	& \multicolumn{2}{c}{\textbf{Valeurs}} \\
\midrule
Module de Young					& $E$				& $160$				& $GaOP$ \\
Contrainte admissible 			& $\sigma_{adm}$ 	& $7\times 10^8$ 			& $ Nm^-2$ \\
Permitivité de l'air 			& $\epsilon$ 		& $8,85\times 10^-12$ 		& $C^2 N^-1m^-2$ \\
\bottomrule
\end{tabular}
\caption{Constantes physiques et propriétés des matériaux}
\end{table}

%http://fr.wikipedia.org/wiki/Th%C3%A9orie_des_poutres

\section{Contenu du CD-ROM}
\label{cd}

Le CD-ROM contient les fichiers suivants:

\begin{itemize}
\item $Latex$: Rapport du projet de semestre.
\item $Matlab$: Programme de traitement d'image pour mesure dynamique.
\item $Labview$: Programme de commande du micromoteur.
\item $process flow$: Processus de fabrication
\item $runcard$: Protocole du processus de fabrication.
\item $solidworks$: Conception assistée par ordinateur du moteur.
\item $Cléwin$: Masques sous format .cif
\item $microscopie MEB$: Image prise par Microscopie Electronique à Balayage MEB.
\item $Excel$: Traitement des résultats.
\end{itemize}

\section{Processus de fabrication}
\label{process flow}

\section{Protocole du processus de fabrication}
\label{runcard}

\section{Article en cours d'impression: ``Three-Phase Electrostatic Rotary Stepper Micromotor with a Flexural Pivot Bearing''}
\label{annexe_confidential}

\section{Article de la conférence Transducers 2009: ``Single mask 3-phase electrostatic rotary stepper micromotor''}
\label{annexe_transducers}

### 2014-02-05 docs/thesis/chap-related_work.tex
mathematica notebooks and thesis commit

\chapter{Related Work}
\label{chapter-related_work}
\section{Status of MIR}
\subsection{TREC}
\subsection{TREC}
\subsection{CLEF}
\subsection{NTCIR}
\section{Mathematical based search projects}
\subsection{MIAS}
\subsection{EgoMath}
\subsection{DLMFSearch}
\subsection{MathWebSearch}
\section{Other related projects and initiatives}
\subsection{arXMLiv}
\thispagestyle{empty}

### 2014-02-05 docs/thesis/chap-technical_considerations.tex
mathematica notebooks and thesis commit

\chapter{Technical Considerations}
\label{chapter-technical_considerations}
In the previos chapter we presented different abstract models which can be suitable in the building of a math based search system.
In this section, we present different aspects that need to be considered when mapping from these theoretical models to a concrete implementation.

\section{Digital Representations of Mathematics}
\subsection{MathML}
\subsection{OpenMath}
\subsection{LaTeX}

\section{Math Extraction Tools}
\section{From LaTeX to MathML}
\subsection{From PDF to MathML}
\subsubsection{Maxtract}
\subsubsection{InftyReader}
\subsubsection{OCR analysis}
\subsection{Other projects}

\section{Computational Algebraic Systems}
In the previous section we discussed about algorithmical ways to tranform, simplify and detect patterns in mathematical equations. Here, we explore what tools are available for performing this type of operations and how they are suitable for our system.

\subsection{Mathematica}
\subsection{Mapple}
\subsection{Matlab}
\subsection{Octane}
\subsection{SAGE}

### 2014-02-05 docs/thesis/chap-theoretical_background.tex
mathematica notebooks and thesis commit

\chapter{Theoretical Background}
\label{chapter-theoretical_background}
Information Retrieval (IR) consists on the activity of identifying relevant documents from a collection based on some input parameters.
Different models have been developed through the evolution of the field. In the subsequent sections, the most relevant to this work are presented.

\section{Boolean Model}
This model was the first one to be developed and is currently one of the most used in the current implementation of IR systems because of its simplicity.

\section{Vector Space Model}

\thispagestyle{empty}

### 2014-02-05 docs/thesis/resume.tex
mathematica notebooks and thesis commit

\chapter*{Résumé}
\thispagestyle{empty}

Ce document présente la modélisation et la caractérisation expérimentale d'un micromoteur triphasé pas à pas ainsi que l'élaboration d'un bras robotisé basé sur ce micromoteur. Le micromoteur monolithique pivote sur un guidage flexible à lame renforcée de grande rigidité transversale. La structure monolithique, fabriquée en salle blanche avec une technologie SOI\footnote{SOI: $Silicon \ on \ Insulator$} à deux masques,  évite tout frottement et contact mécanique entre les éléments mobiles et permet donc une rotation répétée. Le mouvement bidirectionnel, précis et fiable du rotor,  ne nécessite pas de système de commande  à rétroaction. Un modèle mathématique de la rigidité du micromoteur a été établi ainsi que le design d'un  robot parallèle à deux degrés de liberté.
La caractérisation du micromoteur d'un diamètre de 1,4 mm a démontré une plage de rotation de 30 $^\circ$ ($\pm$ 15 $^\circ$  ) à une tension d'alimentation de 65V. La réalisation du robot et l'établissement d'un processus de fabrication à un seul masque n'ont pas pu être effectués faute de temps.

### 2014-02-05 src/cern/ch/mathexplorer/lucene/query/MathQueryParser.java
Added more patterns, sample notebook with some equations Extracted patterns to a separated class

@@ -148,10 +148,8 @@ public class MathQueryParser extends QParser {
 	}
 	
 	public static void main(String[] args) throws Exception {
-		Regex.cleanQuery(texToMathML("$H\\rightarrow W^+W^-$"));
-		MathQueryParser mqp = new MathQueryParser("<math alttext=\"\\mbox{\\bf\\{}(\\mathcal{H}|\\textrm{d}J\\,)\\mbox{\\bf,}\\,(\\mathcal{H}|\textrm{d}K\\,%)\\mbox{\\bf\\}}=({\\mathcal{M}}_{i}|{\\textrm{d}J}\\,\\overleftrightarrow{\\partial}^%{i}{\\textrm{d}K})\\,,\"><mrow><mtext>{</mtext><mrow><mo>(</mo><mi>ℋ</mi><mo>|</mo><mtext>d</mtext><mi>J</mi><mo>)</mo></mrow><mtext>,</mtext><mrow><mo>(</mo><mi>ℋ</mi><mo>|</mo><mtext>d</mtext><mi>K</mi><mo>)</mo></mrow><mtext>}</mtext><mo>=</mo><mrow><mo>(</mo><msub><mi>ℳ</mi><mi>i</mi></msub><mo>|</mo><mtext>d</mtext><mi>J</mi><msup><mover accent=\"true\"><mo>∂</mo><mo>↔</mo></mover><mi>i</mi></msup><mtext>d</mtext><mi>K</mi><mo>)</mo></mrow><mo>,</mo></mrow></math>", null, null, null);
+		String query = Regex.cleanQuery(texToMathML("$H\\rightarrow b\\bar{b}$"));
+		MathQueryParser mqp = new MathQueryParser(query, null, null, null);
 		mqp.parse();
-		
-		
 	}
 }

### 2014-02-05 src/cern/ch/mathexplorer/mathematica/MathematicaEngine.java

@@ -11,6 +11,7 @@ import java.util.HashSet;
 import java.util.List;
 import java.util.Map;
 import java.util.Set;
+import java.util.regex.Pattern;
 
 import cern.ch.mathexplorer.utils.Console;
 import cern.ch.mathexplorer.utils.Constants;
@@ -29,7 +30,6 @@ public class MathematicaEngine {
 	 */
 	// private static MathematicaEngine instance;
 	private KernelLink ml = null;
-	private ArrayList<StructuralPattern> features = new ArrayList<>();
 
 	private static final Map<String, MathematicaEngine> instances = new HashMap<String, MathematicaEngine>();
 
@@ -44,9 +44,6 @@ public class MathematicaEngine {
 	}
 
 	private MathematicaEngine() {
-		if (features.isEmpty()) {
-			loadFeatures();
-		}
 		try {
 			initLink();
 		} catch (MathLinkException e) {
@@ -90,39 +87,7 @@ public class MathematicaEngine {
 		}
 	}
 
-	private void loadFeatures() {
-		features.add(new StructuralPattern("simple_sum", "x_+y_"));
-		features.add(new StructuralPattern("simple_substraction", "x_-y_"));
-		features.add(new StructuralPattern("simple_product", "x_*y_"));
-		features.add(new StructuralPattern("simple_division", "x_/y_"));
-		features.add(new StructuralPattern("numeric_fraction",
-				"x_Integer/y_Integer"));
-		features.add(new StructuralPattern("numeric_fraction_1_numerator",
-				"1/x_Integer"));
-		features.add(new StructuralPattern("sine", "Sin[x_]"));
-		features.add(new StructuralPattern("cosine", "Cos[x_]"));
-		features.add(new StructuralPattern("tangent", "Tan[x_]"));
-		features.add(new StructuralPattern("exponential", "e^x_"));
-		features.add(new StructuralPattern("quadratic", "a_.+b_.x_+c_.x_^2"));
-		features.add(new StructuralPattern(
-				"sum_same_symbol_different_subscript",
-				"a_.* Subscript[x_, y_] + b_.* Subscript[x_, z_]"));
-		features.add(new StructuralPattern(
-				"product_same_symbol_different_subscript",
-				"a_.* Subscript[x_, y_] * b_.* Subscript[x_, z_]"));
-		features.add(new StructuralPattern("product_crossed_sub_super_index",
[…]

### 2014-02-05 src/cern/ch/mathexplorer/mathematica/Patterns.java

@@ -1,0 +1,57 @@
+package cern.ch.mathexplorer.mathematica;
+
+import java.util.ArrayList;
+
+public class Patterns {
+	private static final ArrayList<StructuralPattern> patterns = new ArrayList<>();
+	
+	static {
+		loadPatterns();
+	}
+	
+	static 	private void loadPatterns() {
+		patterns.add(new StructuralPattern("simple_sum", "x_+y_"));
+		patterns.add(new StructuralPattern("simple_substraction", "x_-y_"));
+		patterns.add(new StructuralPattern("simple_product", "x_*y_"));
+		patterns.add(new StructuralPattern("simple_division", "x_/y_"));
+		patterns.add(new StructuralPattern("numeric_fraction",
+				"x_Integer/y_Integer"));
+		patterns.add(new StructuralPattern("numeric_fraction_1_numerator",
+				"1/x_Integer"));
+		patterns.add(new StructuralPattern("sine", "Sin[x_]"));
+		patterns.add(new StructuralPattern("cosine", "Cos[x_]"));
+		patterns.add(new StructuralPattern("sum sine cosine", "a_.*Cos[x_] + b_.*Sin[x_]"));
+		patterns.add(new StructuralPattern("sum sine cosine h", "a_.*Cosh[x_] + b_.*Sinh[x_]"));
+		patterns.add(new StructuralPattern("tangent", "Tan[x_]"));
+		patterns.add(new StructuralPattern("exponential", "e^x_"));
+		patterns.add(new StructuralPattern("quadratic", "a_.+b_.x_+c_.x_^2"));
+		patterns.add(new StructuralPattern(
+				"sum_same_symbol_different_subscript",
+				"a_.* Subscript[x_, y_] + b_.* Subscript[x_, z_]"));
+		patterns.add(new StructuralPattern(
+				"product_same_symbol_different_subscript",
+				"a_.* Subscript[x_, y_] * b_.* Subscript[x_, z_]"));
+		patterns.add(new StructuralPattern("product_crossed_sub_super_index",
+				"a_.* Subscript[v1_, v2_]^v3_  * Subscript[v1_, v3_]^v2_"));
+		patterns.add(new StructuralPattern("sum_crossed_sub_super_index",
+				"a_.* Subscript[v1_, v2_]^v3_  +  b_.* Subscript[v1_, v3_]^v2_"));
[…]

### 2014-02-05 src/cern/ch/mathexplorer/utils/Constants.java

@@ -15,7 +15,7 @@ public final class Constants implements Serializable {
 	public static final String EQUATIONS_TEXT = "EQUATIONS_TEXT";
 	// Schrodinger Equation
 	public final static String SAMPLE_EQ_1 = "<math><mi>i</mi><mi>ℏ</mi><mfrac><mo>∂</mo><mrow><mo>∂</mo><mi>t</mi></mrow></mfrac>"
-			+ "<mi>Ψ</mi><mfenced close=\")\" open=\"(\"><mstyle mathvariant=\"bold\"><mi>r</mi></mstyle><mi>t</mi></mfenced><mo>=</mo>"
+			+ "<mi>Ψ</mi><mfenced close=\")\" open=\"(\"><mi>r</mi></mstyle><mi>t</mi></mfenced><mo>=</mo>"
 			+ "<mfenced close=\"]\" open=\"[\"><mrow><mfrac><mrow><mo>-</mo><msup><mi>ℏ</mi><mn>2</mn></msup></mrow><mrow><mn>2</mn>"
 			+ "<mi>m</mi></mrow></mfrac><msup><mo>∇</mo><mn>2</mn></msup><mo>+</mo><mi>V</mi><mfenced close=\")\" open=\"(\">"
 			+ "<mstyle mathvariant=\"bold\"><mi>r</mi></mstyle><mi>t</mi></mfenced></mrow></mfenced><mi>Ψ</mi>"
@@ -71,9 +71,17 @@ public final class Constants implements Serializable {
 			+ "<mtext>}</mtext><mo>=</mo><mrow><mo>(</mo><msub><mi>ℳ</mi><mi>i</mi></msub><mo>|</mo><mtext>d</mtext><mi>J</mi><msup>"
 			+ "<mover accent=\"true\"><mo>∂</mo><mo>↔</mo></mover><mi>i</mi></msup><mtext>d</mtext><mi>K</mi><mo>)</mo></mrow>"
 			+ "<mo>,</mo></mrow></math>";
+	public final static String SAMPLE_HEP_PROCESS = "<math xmlns=\"http://www.w3.org/1998/Math/MathML\"><mi>H</mi><mo>→</mo><msup><mi>W</mi><mo>+</mo>"
+			+ "</msup><msup><mi>W</mi><mo>-</mo></msup></math>";
[…]

### 2014-02-05 src/cern/ch/mathexplorer/utils/Regex.java

@@ -71,7 +71,12 @@ public class Regex {
 		queryString = queryString.replaceAll(" mathvariant=\".*?\"", "");
 		queryString = queryString.replaceAll("<mstyle>", "");
 		queryString = queryString.replaceAll("</mstyle>", "");
-		
+		queryString = queryString.replaceAll("<mo>=</mo>", "<mo>==</mo>");
+		queryString = queryString.replaceAll("<mo>≡</mo>", "<mo>==</mo>");
+		queryString = queryString.replaceAll("<mspace.*?>", "");
+		queryString = queryString.replaceAll("</mspace>", "");
+		queryString = queryString.replaceAll("<mo>.</mo></math>", "</math>");
+		queryString = queryString.replaceAll("<mo>,</mo></math>", "</math>");
 		
 		//queryString = queryString.replaceAll("&theta;", "θ");
 		queryString = StringEscapeUtils.unescapeHtml4(queryString);

### 2014-02-07 src/cern/ch/mathexplorer/mathematica/MathematicaEngine.java
Fixed problem of <mtext>: Remove completely
Killing of Mathematica processes also in windows

Added dataset (12k+ docs)

@@ -17,6 +17,7 @@ import org.apache.commons.lang3.StringEscapeUtils;
 
 import cern.ch.mathexplorer.utils.Console;
 import cern.ch.mathexplorer.utils.Constants;
+import cern.ch.mathexplorer.utils.OSUtils;
 import cern.ch.mathexplorer.utils.Regex;
 
 import com.wolfram.jlink.KernelLink;
@@ -79,11 +80,22 @@ public class MathematicaEngine {
 
 	private void killMathKernel() {
 		try {
-			String command1 = "killall -s 9 Mathematica";
-			String command2 = "killall -s 9 MathKernel";
+			if (OSUtils.getOS().equals(OSUtils.OS.LINUX) ||
+					OSUtils.getOS().equals(OSUtils.OS.MAC)) {
+				String command1 = "killall -s 9 Mathematica";
+				String command2 = "killall -s 9 MathKernel";
+				Runtime.getRuntime().exec(command1);
+				Runtime.getRuntime().exec(command2);
+			}
+			
+			if (OSUtils.getOS().equals(OSUtils.OS.WINDOWS)) {
+				String command1 = "taskkill /im MathKerel.exe";
+				String command2 = "taskkill /im Mathematica.exe";
+				
+				Runtime.getRuntime().exec(command1);
+				Runtime.getRuntime().exec(command2);
+			}
 
-			Runtime.getRuntime().exec(command1);
-			Runtime.getRuntime().exec(command2);
 		} catch (Exception e) {
 
 		}

### 2014-02-07 src/cern/ch/mathexplorer/utils/Regex.java

@@ -67,7 +67,7 @@ public class Regex {
 	public static String cleanQuery(String queryString) {
 		queryString = queryString.replaceAll("\\r|\\n|  +", "");
 		queryString = queryString.replaceAll(" selected=\".*?\"", "");
-		queryString = queryString.replaceAll("mtext", "mi");
+		queryString = queryString.replaceAll("<mtext.*?</mtext>", "");
 		queryString = queryString.replaceAll(" mathvariant=\".*?\"", "");
 		queryString = queryString.replaceAll("<mstyle>", "");
 		queryString = queryString.replaceAll("</mstyle>", "");

### 2014-02-07 docs/thesis/chap-cern_math_explorer.tex
added literature articles for the thesis

\chapter{CERN Math Explorer}
\label{chapter-cern_math_explorer}
In this chapter we propose our solution for a scalable math based oriented search engine. We present the key points of our system, and how they are related to previous built systems.

\section{Information Retrieval Model}
Our main goal is to develop a system that compliments the already available search capabilities in Invenio and in particular the CDS instance. Our system was developed using the Apache Solr/Lucene framework.

\subsection{Notational Features}
Notational features correspond to the elements that relate to the actual naming of the variables, constants and numeric quantities found in an equation. Here we extract tokens that represent single leaf nodes (E.g. <mi>, <mn>, <mo> tags), and simple constructs like subscript and superscript elements, fractions, roots.
We also extract bi-grams and tri-grams as analogue to that is done for text indexing in current systems.

After examining a set of relevant documents from our dataset, we identified some heuristics that could be applied to improve the recall of our system:

\begin{itemize}
  \item Unicode Normalizing:
  \item Numeric Approximation: Some equations relate specific numeric quantities. While most of the previously explorer systems, handled <mn> tags by only representing them as a constant identifier, this approach is not suitable. A lot of articles in CDS relate to specific experiments under certain conditions, and require a high level of precision in the measurements. 
  \item Grouping of similar operators:
\end{itemize}

\subsection{Structural Features}

\subsection{Development with Lucene/Solr}

\subsection{Integration with Mathematica}
This section describes some aspects that should be considered while implementing the integration with the Mathematica CAS.

\subsubsection{Recursive interpretation}

\subsubsection{Error handling}
Sometimes after certain time Mathematica will crash, launch an exception and following invocations would fails as well.
Also, re-instantiating a KernelLink will yield an Exception. For this scenario, killing the associated processes to Mathematica was necessary:

\begin{verbatim}
killall -s 9 Mathematica
killall -s 9 MathKernel
\end{verbatim}

or

\begin{verbatim}
taskkill /im Mathematica.exe
taskkill /im MathKernel.exe
\end{verbatim}

Depending on the OS the system is running on.

With this, the next creation of a new KernelLink works properly and the subsequent invocations work as expected.

\subsubsection{Timeout Handling}
Unfortunately, checking the quality of a LaTeX document is a difficult job and users have a lot of freedom in the way they write their document since the only visible result is the rendered version. 
One example we found during our work is the following TeX snippet:
\begin{verbatim}
	"\ \varphi\ are\ shown,\ as\ well\ as\ the\ weight\ and\ tension"
\end{verbatim}
A human can easily identify that this corresponds to text and that should be inserted into a proper "mbox" or "text" tag. In this case, the snippet produced the following MathML code
\begin{verbatim}
<math><mrow><mi>φ</mi><mo></mo><mrow><mi>a</mi><mo></mo><mi>r</mi>
<mo></mo><mi>e</mi></mrow><mo></mo><mrow><mi>s</mi><mo></mo>
<mi>h</mi><mo></mo><mi>o</mi><mo></mo><mi>w</mi><mo></mo><mi>n</mi>
</mrow><mo>,</mo><mrow><mi>a</mi><mo></mo>
<mi>s</mi></mrow><mo></mo><mrow><mi>w</mi><mo></mo>
<mi>e</mi><mo></mo><mi>l</mi><mo></mo><mi>l</mi>
</mrow><mo></mo><mrow><mi>a</mi><mo></mo>
<mi>s</mi></mrow><mo></mo><mrow><mi>t</mi><mo></mo>
<mi>h</mi><mo></mo><mi>e</mi></mrow><mo></mo>
<mrow><mi>w</mi><mo></mo><mi>e</mi><mo></mo>
<mi>i</mi><mo></mo><mi>g</mi><mo></mo><mi>h</mi>
<mo></mo><mi>t</mi></mrow><mo></mo><mrow>
<mi>a</mi><mo></mo><mi>n</mi><mo></mo><mi>d</mi>
</mrow><mo></mo><mrow><mi>t</mi><mo></mo><mi>e</mi>
<mo></mo><mi>n</mi><mo></mo><mi>s</mi><mo></mo>
<mi>i</mi><mo></mo><mi>o</mi><mo></mo><mi>n</mi>
</mrow></mrow></math>
\end{verbatim}

Mathematica took around 10 minutes to interpret it.
In the ideal case we would be able to identify the malformed expressions and pass to Mathematica only well-formed equations to be processed but as this simple example shows, that is a very challenging task and may require more work.
As a remedial situation, we used a fixed timeout to stop the processing of a given expression.

\subsection{Integration with CDS}

### 2014-02-07 docs/thesis/chap-related_work.tex
added literature articles for the thesis

@@
 \section{Mathematical based search projects}
-\subsection{MIAS}
+\subsection{MIaS}
+MIaS\cite{mias_1} (Math Indexer and Searcher), currently, is one of the flagship projects in the indexing and searching of mathematical content.
+As most of the other projects, it processes documents in MathML format.
+It allows the user to include in the queries mathematical expressions and textual content.
+During indexing time, equations are transformed following a set of heuristics that include:
+\begin{itemize}
+  \item Ordering of elements: Taking into account commutativity of certain operators (Addition, multiplication), elements are ordered such that $3 + a$ would be converted into $a + 3$ (Since the <mi> tag comes first than the <mn> tag)
+  \item Unification of variables: This process takes into the account the structure of the equations in despite of the naming of the variables.
+Expressions like $a+b^a$ and $x+y^x$ would be converted into an expressions of the form $id_1 + id_2^{id_1}$ which would match.
+  \item Unification of constants: This step consists of replacing all occurrences of constants (<mn> tags) by a const symbol. 
+\end{itemize}
+The extracted tokens from a given equation consist of all its valid sub-expressions.
+The original expression is given a weight value of 1, and following sub-expressions are given smaller weights depending on how general or specific they are.
+The system, also as most of the current projects, is developed by using the Apache Lucene framework. The system adapts the default scoring equation such that the given weight is taken into account.  
 \subsection{EgoMath}
+EgoMath\cite{egomath1} and its new version EgoMath$^2$\cite{egomath2}, is a system oriented to index the mathematical content from the Wikipedia.org database.
+The processing steps before indexing are similar to the ones in MIaS (Rearranging of symbols, unification of constants).
+The extraction process started from a complete dump of the Wikipedia database and filtering only the math articles, which are identified by the ”<math>" tag.
+This consists on around thirty thousand articles, from which 240.000 equations were identified.
+The processing step includes translating the equation from LaTeX into MathML format and then indexing both representation.
+Some additional effort is done into splitting large mathematical blocks like tables into single mathematical expressions.
+
 \subsection{DLMFSearch}
 \subsection{MathWebSearch}
+\subsection{LaTEXSearch}
+LaTEXSearch \url{http://latexsearch.com/} is a system developed by the scientific publisher Springer that allows to search over a database of around eight million latex snippets extracted from their publications.
+The system, unfortunately, is proprietary and no details are provided about the internals of the system.
+
 \section{Other related projects and initiatives}

### 2014-02-07 docs/thesis/chap-theoretical_background.tex
added literature articles for the thesis

@@
 
+\section{Tree Edit Distance}
+As it will be discussed, one of the most common formats to represent mathematical equations, MathML, is a XML based format, and whose structure represents a rooted tree.
+Because of this, it makes sense to consider some models to compare and analyse mathematical expressions taking into account their natural tree structure.
+The most natural way of addressing this, is through the well studied abstract problem of Tree Edit Distance problem, where the idea is to compute a distance between a pair of trees.
+It should be noted that the development of this problem is very similar to the String Edit Distance problem.
+The Tree Edit Distance problem can be formulated as follows:
+Let $\Sigma$ be a finite alphabet and let $\lambda \notin \Sigma$ be a special empty symbol. Finally let $\Sigma_\lambda = \Sigma \cup \lambda$. 
+Given two trees $T_1$ and $T_2$ that are labelled (That is, each node $N$ in the tree has assigned a label $l(N) \in \Sigma$ ) and ordered (That is, we are provided an order between sibling nodes), we define the following operations ($l(N_1) \rightarrow l(N_2)$) where $(l(N_1),l(N_2)) \in ((\Sigma \cup \lambda)\times(\Sigma \cup \lambda)\setminus(\lambda,\lambda)) $: \\
+\textbf{Relabelling:} If $l(N_1) \neq \lambda \wedge l(N_2) \neq \lambda $. We change the label of a node in the tree $T$ \\
+\textbf{Deletion:} If $l(N_2) = \lambda $. The children of $N_1$ become the children of $N_1$'s parent ($N_1$ is not the root of the tree) and occupy its position in the sibling ordering. \\
+\textbf{Insertion:} If $l(N_1) = \lambda $. This is the complement operation of deletion. \\
+
+For each of this operations $\omega = (l(N_1) \rightarrow l(N_2))$, we assign a cost function $cost(\omega)$ and for a given sequence of this transformations $\Omega = (\omega_1, \omega_2, ...
+, \omega_n)$ we assign a cost function $cost(\Omega) = \sum_{i=1}^{i=n} {cost(\omega_i)}$
+We also assume that $cost(\omega)$ is a distance metric. 
+With the previous definition, the distance between $T_1$ and $T_2$ can be expressed now as $ dist(T_1, T_2) = min\left\{ cost(\Omega)| \Omega \text{ is a sequence of operations that transform } T_1 \text{ into } T_2 \right\} $
+
+A recursive formulation of the problem can be defined in the following way:
+
+\begin{align*}
+dist(T,T) &= 0 \\
+dist(F_1, T) &= dist(F_1 - v, T) + cost(v \rightarrow \lambda) \\
+dist(T, F_2) &= dist(T, F_2 - w) + cost(\lambda \rightarrow w) \\
+dist(F_1, F_2)&=\left\{
+\begin{array}{ll}
+dist(F_1 - v, F_2) + cost(v \rightarrow \lambda) \\
+dist(F_1, F_2 - w) + cost(\lambda \rightarrow w) \\
+dist(F_1(v), F_2(w)) + dist(F_1 - T_1(v), F_2 - T_2(w)) + cost(v \rightarrow w)
+\end{array}
+\right.
+\end{align*}  
+Where $F$ is a forest, $v$ and $w$ nodes from a free, $F - v$ the forest $F$ with the deletion of the node $v$, $T(v)$  the tree rooted at $v$ and $F-T(v)$ the forest obtained by removing all the nodes in $T(v)$ from $F$
+
+The presented set of equations give a simple way to compute the edit distance between a pair of trees, and the most known algorithms like Zhang and Shasha's\cite{zhang_shasha} whose worst time case time bound is $O(|T_1|^2|T_2|^2)$, Klein's\cite{klein} that achieves a lower bound of $O(|T_1|^2|T_2|log|T_2|)$ or Demaine's\cite{demaine}, take into advantage the fact that the recursion relies in the solution of smaller sub-problems, so by carefully choosing which of this sub-problems to solve.
+
 \thispagestyle{empty}

### 2014-02-07 src/cern/ch/mathexplorer/mathematica/Patterns.java

@@ -21,7 +21,9 @@ public class Patterns {
 		patterns.add(new StructuralPattern("sine", "Sin[x_]"));
 		patterns.add(new StructuralPattern("cosine", "Cos[x_]"));
 		patterns.add(new StructuralPattern("sum sine cosine", "a_.*Cos[x_] + b_.*Sin[x_]"));
-		patterns.add(new StructuralPattern("sum sine cosine h", "a_.*Cosh[x_] + b_.*Sinh[x_]"));
+		patterns.add(new StructuralPattern("product sine cosine", "a_.*Cos[x_] * b_.*Sin[x_]"));
+		patterns.add(new StructuralPattern("sum sineh cosine h", "a_.*Cosh[x_] + b_.*Sinh[x_]"));
+		patterns.add(new StructuralPattern("product sineh cosine h", "a_.*Cosh[x_] * b_.*Sinh[x_]"));
 		patterns.add(new StructuralPattern("tangent", "Tan[x_]"));
 		patterns.add(new StructuralPattern("exponential", "e^x_"));
 		patterns.add(new StructuralPattern("quadratic", "a_.+b_.x_+c_.x_^2"));

### 2014-02-10 src/cern/ch/mathexplorer/core/MathExplorer.java
Added normalization in query

@@ -48,8 +48,8 @@ import uk.ac.ed.ph.snuggletex.SnuggleInput;
 import uk.ac.ed.ph.snuggletex.SnuggleSession;
 import cern.ch.mathexplorer.core.EquationResult.EquationBuilder;
 import cern.ch.mathexplorer.lucene.analysis.VecTextField;
-import cern.ch.mathexplorer.lucene.analysis.analyzers.SolrMathMLNotationalAnalyzer;
-import cern.ch.mathexplorer.lucene.analysis.analyzers.SolrNormalizerMathMLNotationalAnalyzer;
+import cern.ch.mathexplorer.lucene.analysis.analyzers.SolrNotationalAnalyzer;
+import cern.ch.mathexplorer.lucene.analysis.analyzers.SolrNormalizerNotationalAnalyzer;
 import cern.ch.mathexplorer.lucene.analysis.analyzers.SolrStructuralAnalyzer;
 import cern.ch.mathexplorer.lucene.query.MathQueryParser;
 import cern.ch.mathexplorer.utils.Console;
@@ -75,9 +75,9 @@ public class MathExplorer {
 	private Directory indexDirectory;
 	private IndexWriterConfig indexConfig;
 	
-	private Analyzer analyzer = new SolrMathMLNotationalAnalyzer(matchVersion);
+	private Analyzer analyzer = new SolrNotationalAnalyzer(matchVersion);
 	private Analyzer analyzer2 = new SolrStructuralAnalyzer(matchVersion);
-	private Analyzer analyzer3 = new SolrNormalizerMathMLNotationalAnalyzer(matchVersion);
+	private Analyzer analyzer3 = new SolrNormalizerNotationalAnalyzer(matchVersion);
 	
 	
 	private DirectoryReader ireader;

### 2014-02-10 src/cern/ch/mathexplorer/core/MathExplorer.java
rectored code in mathquery parser, made it easier to read.

@@ -54,6 +54,7 @@ import cern.ch.mathexplorer.lucene.analysis.analyzers.SolrStructuralAnalyzer;
 import cern.ch.mathexplorer.lucene.query.MathQueryParser;
 import cern.ch.mathexplorer.utils.Console;
 import cern.ch.mathexplorer.utils.Constants;
+import cern.ch.mathexplorer.utils.Constants.MATH_FIELD;
 import cern.ch.mathexplorer.utils.Regex;
 
 public class MathExplorer {
@@ -170,7 +171,7 @@ public class MathExplorer {
 			}
 			equationsInFile.add(text);
 			Document doc = new Document();
-			Field equationField = new VecTextField(Constants.MATH_NOTATIONAL_FIELD,
+			Field equationField = new VecTextField(MATH_FIELD.MATH_NOTATIONAL_FIELD.getName(),
 					text, Store.YES);
 			doc.add(equationField);
 			doc.add(new Field(FILENAME, currentFile.getName(),
@@ -245,7 +246,7 @@ public class MathExplorer {
 					.setLineNumber(
 							Integer.parseInt(hitDoc.getValues(LINE)[0]))
 					.setMathmlExpression(
-							hitDoc.getValues(Constants.MATH_NOTATIONAL_FIELD)[0]);
+							hitDoc.getValues(MATH_FIELD.MATH_NOTATIONAL_FIELD.getName())[0]);
 				}
 				else {//The indexed elements are individual equations {
 					eqBuilder
@@ -336,11 +337,11 @@ public class MathExplorer {
 	}
 
 	void testAnalyzer(String equation) throws Exception {
-		TokenStream ts1 = analyzer.tokenStream(Constants.MATH_NOTATIONAL_FIELD,
+		TokenStream ts1 = analyzer.tokenStream(MATH_FIELD.MATH_NOTATIONAL_FIELD.getName(),
 				new StringReader(equation));
-		TokenStream ts2 = analyzer2.tokenStream(Constants.MATH_STRUCTURAL_FIELD,
+		TokenStream ts2 = analyzer2.tokenStream(MATH_FIELD.MATH_STRUCTURAL_FIELD.getName(),
 				new StringReader(equation));
-		TokenStream ts3 = analyzer3.tokenStream(Constants.MATH_STRUCTURAL_FIELD,
+		TokenStream ts3 = analyzer3.tokenStream(MATH_FIELD.MATH_NORMALIZED_NOTATIONAL_FIELD.getName(),
[…]

### 2014-02-10 src/cern/ch/mathexplorer/lucene/query/MathQueryParser.java

@@ -30,141 +30,125 @@ import cern.ch.mathexplorer.mathematica.StructuralPattern;
 import cern.ch.mathexplorer.utils.Console;
 import cern.ch.mathexplorer.utils.Constants;
 import cern.ch.mathexplorer.utils.Constants.CHARACTER_CATEGORIES;
+import cern.ch.mathexplorer.utils.Constants.MATH_FIELD;
 import cern.ch.mathexplorer.utils.Regex;
 
 public class MathQueryParser extends QParser {
 	static Logger aLogger = java.util.logging.Logger
 			.getLogger(MathQueryParser.class.getName());
-	
-	public MathQueryParser(String qstr, SolrParams localParams, SolrParams params,
-			SolrQueryRequest req) {
+
+	public MathQueryParser(String qstr, SolrParams localParams,
+			SolrParams params, SolrQueryRequest req) {
 		super(qstr, localParams, params, req);
 	}
 
 	private static SnuggleEngine engine = new SnuggleEngine();
+
+	public void addNotationalTokens(BooleanQuery query, String mathML, MATH_FIELD field) {
+		Collection<String> tokenInQuery = Regex.extractElements(mathML);
+		for (String mathMLToken : tokenInQuery) {
+			query.add(new BooleanClause(new TermQuery(new Term(
+					field.getName(), mathMLToken)),
+					Occur.SHOULD));
+			addOperatorsCategory(mathMLToken, query, field);
+			Console.print(mathMLToken);
+		}
+	}
+
+	void addOperatorsCategory(String mathMLToken, BooleanQuery query, MATH_FIELD field) {
+		if (mathMLToken.startsWith("<mo>") && mathMLToken.endsWith("</mo>")) { // OPERATOR CATEGORY TOKEN
+			String operator = mathMLToken.replace("<mo>", "").replace("</mo>",
+					"");
+			CHARACTER_CATEGORIES category = null;
+			if ((category = (Constants.characterToCategoryMap.get(operator))) != null) {
+				query.add(new BooleanClause(new TermQuery(new Term(
+						field.getName(), category.name())),
+						Occur.SHOULD));
+			}
+		}
+	}
+
+	void addStructuralPatterns(BooleanQuery query, String mathML){
+		List<StructuralPattern> patterns = new ArrayList<>();
+		try {
[…]

### 2014-02-10 src/cern/ch/mathexplorer/utils/Constants.java

@@ -9,10 +9,20 @@ import java.util.Set;
 
 public final class Constants implements Serializable {
 
-	public static final String MATH_NOTATIONAL_FIELD = "math_notational_field";
-	public static final String MATH_NORMALIZED_NOTATIONAL_FIELD = "math_normalized_notational_field";
-	public static final String MATH_STRUCTURAL_FIELD = "math_structural_field";
-	
+	public static enum MATH_FIELD {
+		MATH_NOTATIONAL_FIELD("math_notational_field"),
+		MATH_NORMALIZED_NOTATIONAL_FIELD("math_normalized_notational_field"),
+		MATH_STRUCTURAL_FIELD("math_structural_field");
+		
+		String name;
+		MATH_FIELD(String name){
+			this.name = name;
+		}
+		
+		public String getName(){
+			return name;
+		}
+	}
 
 	public static final String EQUATIONS_TEXT = "EQUATIONS_TEXT";
 	// Schrodinger Equation

### 2014-02-10 src/cern/ch/mathexplorer/core/MathExplorer.java
Fixed bugs, added group for multiplications

@@ -268,7 +268,7 @@ public class MathExplorer {
 		
 		MathExplorer m = new MathExplorer(null, false);
 		m.testAnalyzer(Constants.SAMPLE_EQ_2);
-		
+		System.out.println("Finished");
 		//m.search(Constants.SAMPLE_EQUATION_2, true, INDEX_WHOLE_ARTICLE);
 		//testUnicodeNormalization();
 		

### 2014-02-10 src/cern/ch/mathexplorer/lucene/analysis/tokenizers/StructuralPatternsTokenizer.java

@@ -61,7 +61,7 @@ public final class StructuralPatternsTokenizer extends MathTokenizer {
 			return false;
 		}
 		clearAttributes();
-		featuresAtt.setEmpty().append(features.get(currentFeature).getName());
+		featuresAtt.setEmpty().append(features.get(currentFeature).getPattern());
 		currentFeature++;
 		return true;
 

### 2014-02-10 src/cern/ch/mathexplorer/lucene/query/MathQueryParser.java

@@ -2,6 +2,7 @@ package cern.ch.mathexplorer.lucene.query;
 
 import java.io.IOException;
 import java.util.ArrayList;
+import java.util.Arrays;
 import java.util.Collection;
 import java.util.HashSet;
 import java.util.List;
@@ -15,6 +16,7 @@ import org.apache.lucene.search.BooleanClause.Occur;
 import org.apache.lucene.search.BooleanQuery;
 import org.apache.lucene.search.Query;
 import org.apache.lucene.search.TermQuery;
+import org.apache.lucene.util.UnicodeUtil;
 import org.apache.solr.common.params.SolrParams;
 import org.apache.solr.request.SolrQueryRequest;
 import org.apache.solr.search.QParser;
@@ -57,8 +59,7 @@ public class MathQueryParser extends QParser {
 
 	void addOperatorsCategory(String mathMLToken, BooleanQuery query, MATH_FIELD field) {
 		if (mathMLToken.startsWith("<mo>") && mathMLToken.endsWith("</mo>")) { // OPERATOR CATEGORY TOKEN
-			String operator = mathMLToken.replace("<mo>", "").replace("</mo>",
-					"");
+			String operator = mathMLToken.replace("<mo>", "").replace("</mo>", "");
 			CHARACTER_CATEGORIES category = null;
 			if ((category = (Constants.characterToCategoryMap.get(operator))) != null) {
 				query.add(new BooleanClause(new TermQuery(new Term(
@@ -77,7 +78,7 @@ public class MathQueryParser extends QParser {
 				query.add(new BooleanClause(
 						new TermQuery(new Term(
 								MATH_FIELD.MATH_STRUCTURAL_FIELD.getName(), pattern
-										.getName())), Occur.SHOULD));
+										.getPattern())), Occur.SHOULD));
 			}
 		} catch (Exception e) {
 		}
@@ -129,7 +130,7 @@ public class MathQueryParser extends QParser {
 	}
 
 	public static String texToMathML(String texText) throws IOException {
-
+		texText = texText.trim();
 		texText.replaceAll("\\$\\$", "$");
 		if (!texText.endsWith("$")) {
 			texText += "$";
@@ -147,8 +148,7 @@ public class MathQueryParser extends QParser {
 	}
 
 	public static void main(String[] args) throws Exception {
-		String query = Regex
-				.cleanQuery(texToMathML("$ (\\cos(x))^2 + (\\sin(x))^2 $"));
[…]

### 2014-02-10 src/cern/ch/mathexplorer/mathematica/MathematicaEngine.java

@@ -1,8 +1,5 @@
 package cern.ch.mathexplorer.mathematica;
 
-import java.io.BufferedReader;
-import java.io.File;
-import java.io.FileReader;
 import java.util.ArrayList;
 import java.util.HashMap;
 import java.util.HashSet;
@@ -13,18 +10,15 @@ import java.util.concurrent.Callable;
 import java.util.concurrent.ExecutorService;
 import java.util.concurrent.Executors;
 import java.util.concurrent.Future;
-import java.util.concurrent.TimeUnit;
 import java.util.concurrent.TimeoutException;
 
 import org.apache.commons.lang3.StringEscapeUtils;
 
 import cern.ch.mathexplorer.utils.Console;
 import cern.ch.mathexplorer.utils.Constants;
-import cern.ch.mathexplorer.utils.OSUtils;
 
 import com.wolfram.jlink.KernelLink;
 import com.wolfram.jlink.MathLinkException;
-import com.wolfram.jlink.MathLinkFactory;
 
 public class MathematicaEngine {
 
@@ -34,11 +28,11 @@ public class MathematicaEngine {
 	private final static String TEXT_IN_EQUATION = "XML`MathML`Symbols`Multiscripts";
 	private final static String HOLD_COMPLETE = "HoldComplete";
 
-	/**
-	 * Singleton instance
-	 */
 	private KernelLink ml = null;
 
+	/**
+	 * Multiton pattern, one instance per type of element
+	 */
 	private static final Map<String, MathematicaEngine> instances = new HashMap<String, MathematicaEngine>();
 
 	public static MathematicaEngine getInstance(String key) {
@@ -61,8 +55,6 @@ public class MathematicaEngine {
 	}
 
 
-
-	
 	/**
 	 * This method should be called after an invokation of the tryInterpretRoot
 	 * sincew it relies on the Mathematica variable interpretedResults holding a
@@ -342,11 +334,11 @@ public class MathematicaEngine {
 
 	public static void main(String[] args) throws Exception {
 		MathematicaEngine mi = getInstance("TESTING");
-		String expression = Constants.SAMPLE_EQ_TIMEOUT;
+		String expression = Constants.SAMPLE_HEP_PROCESS;
 		Console.print(expression);
 		List<StructuralPattern> features = mi.getPatterns(expression);
 		for (StructuralPattern f : features) {
-			Console.print(f.getName());
+			Console.print(f.getPattern());
 		}
 		Console.print(mi.simplifyExpression(expression));
 	}

### 2014-02-10 src/cern/ch/mathexplorer/mathematica/Patterns.java

@@ -1,6 +1,8 @@
 package cern.ch.mathexplorer.mathematica;
 
 import java.util.ArrayList;
+import java.util.Arrays;
+import java.util.List;
 
 public class Patterns {
 	private static final ArrayList<StructuralPattern> patterns = new ArrayList<>();
@@ -10,50 +12,119 @@ public class Patterns {
 	}
 	
 	static 	private void loadPatterns() {
-		patterns.add(new StructuralPattern("simple_sum", "x_+y_"));
-		patterns.add(new StructuralPattern("simple_substraction", "x_-y_"));
-		patterns.add(new StructuralPattern("simple_product", "x_*y_"));
-		patterns.add(new StructuralPattern("simple_division", "x_/y_"));
-		patterns.add(new StructuralPattern("numeric_fraction",
-				"x_Integer/y_Integer"));
-		patterns.add(new StructuralPattern("numeric_fraction_1_numerator",
-				"1/x_Integer"));
-		patterns.add(new StructuralPattern("sine", "Sin[x_]"));
-		patterns.add(new StructuralPattern("cosine", "Cos[x_]"));
-		patterns.add(new StructuralPattern("sum sine cosine", "a_.*Cos[x_] + b_.*Sin[x_]"));
-		patterns.add(new StructuralPattern("product sine cosine", "a_.*Cos[x_] * b_.*Sin[x_]"));
-		patterns.add(new StructuralPattern("sum sineh cosine h", "a_.*Cosh[x_] + b_.*Sinh[x_]"));
-		patterns.add(new StructuralPattern("product sineh cosine h", "a_.*Cosh[x_] * b_.*Sinh[x_]"));
-		patterns.add(new StructuralPattern("tangent", "Tan[x_]"));
-		patterns.add(new StructuralPattern("exponential", "e^x_"));
-		patterns.add(new StructuralPattern("quadratic", "a_.+b_.x_+c_.x_^2"));
-		patterns.add(new StructuralPattern(
-				"sum_same_symbol_different_subscript",
-				"a_.* Subscript[x_, y_] + b_.* Subscript[x_, z_]"));
-		patterns.add(new StructuralPattern(
-				"product_same_symbol_different_subscript",
-				"a_.* Subscript[x_, y_] * b_.* Subscript[x_, z_]"));
[…]

### 2014-02-10 src/cern/ch/mathexplorer/mathematica/StructuralPattern.java

@@ -12,30 +12,22 @@ package cern.ch.mathexplorer.mathematica;
  */
 public class StructuralPattern {
 	/**
-	 * The name of this feature
-	 */
-	private String name;
-	
-	/**
 	 * The String representing the pattern in Mathematica Notation
 	 */
 	private String pattern;
 	
-	public StructuralPattern(String name, String pattern) {
+	public StructuralPattern(String pattern) {
 		super();
-		this.name = name;
 		this.pattern = pattern;
-	}
-	public String getName() {
-		return name;
-	}
-	public void setName(String name) {
-		this.name = name;
 	}
 	public String getPattern() {
 		return pattern;
 	}
 	public void setPattern(String pattern) {
 		this.pattern = pattern;
+	}
+	
+	public String toString(){
+		return pattern;
 	}
 }

### 2014-02-10 src/cern/ch/mathexplorer/servlets/InputServlet.java

@@ -2,14 +2,12 @@ package cern.ch.mathexplorer.servlets;
 
 import java.io.IOException;
 import java.io.PrintWriter;
-import java.util.List;
 
 import javax.servlet.ServletException;
 import javax.servlet.http.HttpServlet;
 import javax.servlet.http.HttpServletRequest;
 import javax.servlet.http.HttpServletResponse;
 
-import cern.ch.mathexplorer.core.EquationResult;
 import cern.ch.mathexplorer.core.MathExplorer;
 import cern.ch.mathexplorer.utils.Constants;
 
@@ -80,7 +78,7 @@ public class InputServlet extends AbstractServlet {
 		
 		String result = "<br/>Some MathML examples you can use: <table border=1><br/>\n";
 		
-		for (String s : Constants.SAMPLE_EQUATIONS) {
+		for (String s : Constants.SAMPLE_MATHML_EQUATIONS) {
 			result += "<tr><td>";
 			result += s+"\n";
 			result += "<xmp>"+s+"</xmp><br/>\n";

### 2014-02-10 src/cern/ch/mathexplorer/servlets/QueryServlet.java

@@ -5,7 +5,6 @@ import java.io.PrintWriter;
 import java.net.URLDecoder;
 import java.util.List;
 
-import javax.servlet.ServletContext;
 import javax.servlet.ServletException;
 import javax.servlet.http.HttpServlet;
 import javax.servlet.http.HttpServletRequest;

### 2014-02-10 src/cern/ch/mathexplorer/utils/Constants.java

@@ -70,6 +70,8 @@ public final class Constants implements Serializable {
 	public final static String SAMPLE_EQ_8 = "<math xmlns=\"http://www.w3.org/1998/Math/MathML\"><mi>A</mi><mo>=</mo><mi>d</mi><mi>N</mi>"
 			+ "<mo>/</mo><mi>d</mi><mi>t</mi></math>";
 	public final static String SAMPLE_EQ_9 = "<math><mn>1E+2</mn></math>";
+	
+	 public final static String SAMPLE_EQ_10 = "<math><mi>x</mi><mo>*</mo><mi>y</mi></math>"; 
 	public final static String SAMPLE_EQ_1_N = "<math><mi>i</mi><mi>ℏ</mi><mfrac><mn>1.0264</mn><mrow><mn>4.6</mn><mn>9</mn></mrow></mfrac>"
 			+ "<mn>9...15</mn><mfenced close=\")\" open=\"(\"><mstyle mathvariant=\"bold\"><mi>r</mi></mstyle><mi>t</mi></mfenced><mo>=</mo>"
 			+ "<mfenced close=\"]\" open=\"[\"><mrow><mfrac><mrow><mn>2300002500</mn><msup><mn>90000</mn><mn>2.0135</mn></msup></mrow><mrow><mn>2</mn>"
@@ -100,11 +102,24 @@ public final class Constants implements Serializable {
 			+ "</mrow><mo>)</mo></mrow><mo>, </mo><mrow><mi>T</mi><mo>⁢</mo><mi>s</mi><mo>⁢</mo><mi>u</mi><mo>⁢</mo><mi>k</mi><mo>⁢</mo><mi>u</mi><mo>⁢</mo><mi>b</mi>"
 			+ "<mo>⁢</mo><mi>a</mi></mrow><mo>, </mo><mrow><mi>I</mi><mo>⁢</mo><mi>b</mi><mo>⁢</mo><mi>a</mi><mo>⁢</mo><mi>r</mi><mo>⁢</mo><mi>a</mi><mo>⁢</mo><mi>k</mi>"
 			+ "<mo>⁢</mo><mi>i</mi></mrow><mo>, </mo><mrow><mi>J</mi><mo>⁢</mo><mi>a</mi><mo>⁢</mo><mi>p</mi><mo>⁢</mo><mi>a</mi><mo>⁢</mo><mi>n</mi></mrow></mrow></math>";
[…]

### 2014-02-10 src/cern/ch/mathexplorer/utils/Regex.java

@@ -57,8 +57,11 @@ public class Regex {
 		
 		for (Pattern p: PATTERNS) {
 			Matcher matcher = p.matcher(expression);
-			while (matcher.find()) {
-				result.add(matcher.group(GROUP));
+			for(int i = 0; i< expression.length(); i++) {
+				if (matcher.find(i)) {
+					i = matcher.start()+1;
+					result.add(matcher.group(GROUP));
+				}
 			}
 		}
 		return result;

### 2014-02-10 src/cern/ch/mathexplorer/webbeans/MathBean.java

@@ -2,7 +2,6 @@ package cern.ch.mathexplorer.webbeans;
 
 import java.io.IOException;
 import java.io.Serializable;
-import java.net.URLDecoder;
 import java.util.ArrayList;
 import java.util.List;
 
@@ -41,7 +40,7 @@ public class MathBean implements Serializable {
 		
 		mathExplorer = MathExplorer.getInstance(servletContext);
 		queryText  = "";
-		sampleEquations = Constants.SAMPLE_EQUATIONS;
+		sampleEquations = Constants.SAMPLE_MATHML_EQUATIONS;
 		queryResult = new ArrayList<>();
 		message = "";
 		inputFormat = Constants.MATHML;

### 2014-02-11 docs/thesis/chap-theoretical_background.tex
Wrote okapi/bm25 section

@@
 \section{Vector Space Model}
+
+\section{Probabilistic Relevance Model}
+The probabilistic relevance model was developed in 1976 by Robertson and Jones\cite{probabilistic_relevance_model}.
+The similarity of a document $d_{j}$ to a query $q$ is given by the probability of $d_{j}$ being relevant to $q$.
+It assumes there is a set $R$ that is preferred to be the answer set for $q$.
+The model assumes that the document in $R$ are relevant to $q$ and the documents in $\bar{R}$ are not relevant.
+$R$ then is the set that maximizes:
+
+$$sim(d_{j},q) = \frac{ P(R|d_{j})} {P(\bar{R} |d_{j})} $$
+
+The importance of this model is that it serves as a solid base for state of the art information retrieval models.
+
+\section{Okapi BM25}
+
+The Okapi BM25 ranking function is one of the current state-of-the-art models in information retrieval\cite{okapibm25}.
+The actual scoring function is called BM25 and Okapi refers to the first system implementing this function in the 1980s.
+Given a query $Q$ as a vector of keywords $q_{1}, q_{2}, ... , q_{n}$ then the score for a document $d$ is:
+
+$$score(d, Q) = \sum_{i=1}^{n}IDF{(q_i)}*\frac{ frec(q_i, D)}{frec(q_i, D)+k_1*((1-b)+b*\frac{|D|}{avgdl})} $$
+and $$IDF(q_i) = \log{\frac{N - df(q_i)+0.5}{df(q_i)+0.5}} $$
+
+where $frec(q_i, D)$ is the number of occurrences of keyword $q_i$ in $D$, $avgdl$ is the average length (In keywords) of a document, and $k_1$ and $b$ are free parameters.
+Usually $k_1 = 2$ and $b \in [0, 1]$ controls how important is the length normalization, being set normally to $0.75$.
+$N$ is the size of the collection, $df(q_i)$ is the number of documents that contain term $q_i$
+
+A further variation that takes into account structure in the form of a document containing different fields and each of them having its own length and importance (boost) can be formulated as follows, known as BM25F can be expressed as follows:
+
+$$score(d, Q) = \sum_{i=1}^{n} \frac{weigth(q_i, d)}{k+ weigth(q_i, d)} * IDF(q_i)$$
+and 
+$$weight(q_i, d) = \sum_{j=1}^m \frac{frec(q_i, D, field_j)*boost_j)}{((1-b_j) + b_j*\frac{|l_j|}{avgfl_j})} $$
+where $m$ is the number of different fields, $boost_j$ is the relative importance for each field, $b_j$ is analogous to the $b$ constant in the BM25 group of equations, $|l_j|$ is the length of the $field_j$ and $avgfl_j$ is the average length of the $field_j$.
 

### 2014-02-11 src/cern/ch/mathexplorer/mathematica/Patterns.java
added more constants, patterns

@@ -16,23 +16,38 @@ public class Patterns {
 		patterns.add(new StructuralPattern("x_-y_"));
 		patterns.add(new StructuralPattern("x_*y_"));
 		patterns.add(new StructuralPattern("x_/y_"));
+		
+		patterns.add(new StructuralPattern("x_.+y_."));
+		patterns.add(new StructuralPattern("x_.-y_."));
+		patterns.add(new StructuralPattern("x_.*y_."));
+		patterns.add(new StructuralPattern("x_./y_."));
+		
+		patterns.add(new StructuralPattern("x_.+y_.+z_."));
+		patterns.add(new StructuralPattern("x_.*y_.*z_."));
+		
+		patterns.add(new StructuralPattern("a_.x_^2+b_.y_^2"));
+		patterns.add(new StructuralPattern("a_.x_^3+b_.y_^3"));
+		patterns.add(new StructuralPattern("a_.x_^n_+b_.y_^n_"));
+		patterns.add(new StructuralPattern("a_.x_^n_+b_.y_^n_"));
+		patterns.add(new StructuralPattern("a_.+b_.x_+c_.x_^2"));
+		
+		patterns.add(new StructuralPattern("(x_+y_)^2"));
+		patterns.add(new StructuralPattern("(x_-y_)^2"));
+		patterns.add(new StructuralPattern("(x_+y_)^3"));
+		patterns.add(new StructuralPattern("(x_-y_)^3"));
+		
 		patterns.add(new StructuralPattern("x_Integer/y_Integer"));
 		patterns.add(new StructuralPattern("1/x_Integer"));
-		patterns.add(new StructuralPattern("Sin[x_]"));
-		patterns.add(new StructuralPattern("Cos[x_]"));
 		patterns.add(new StructuralPattern("a_.*Cos[x_] + b_.*Sin[x_]"));
 		patterns.add(new StructuralPattern("a_.*Cos[x_] * b_.*Sin[x_]"));
 		patterns.add(new StructuralPattern("a_.*Cosh[x_] + b_.*Sinh[x_]"));
 		patterns.add(new StructuralPattern("a_.*Cosh[x_] * b_.*Sinh[x_]"));
-		patterns.add(new StructuralPattern("Tan[x_]"));
 		patterns.add(new StructuralPattern("_.*e^x_"));
-		patterns.add(new StructuralPattern("a_.+b_.x_+c_.x_^2"));
[…]

### 2014-02-11 src/cern/ch/mathexplorer/utils/Constants.java

@@ -194,8 +194,10 @@ public final class Constants implements Serializable {
 		))), 
 		MULTIPLICATION(new HashSet<>(Arrays.asList(
 				"\u2062",	//Invisible times
-				"*",
+				//"*",		Needs to be considered in context
 				"×",
+				"✕",
+				"✖",
 				"·")))
 		, ARROWS(new HashSet<>(Arrays.asList("←" //
 				, "→" //

### 2014-02-11 src/cern/ch/mathexplorer/utils/Regex.java

@@ -24,6 +24,7 @@ public class Regex {
 	public final static int GROUP = 0;
 	private static List<Pattern> initPatternsList() {
 		List<Pattern> result = new ArrayList<Pattern>();
+		result.add(Pattern.compile("<math.*?</math>"));
 		result.add(Pattern.compile("<mi[^<]*?</mi>"));
 		result.add(Pattern.compile("<mo[^<]*?</mo>"));
 		result.add(Pattern.compile("<mn[^<]*?</mn>"));

### 2014-02-11 src/cern/ch/mathexplorer/mathematica/MathematicaEngine.java
removed x_/x_ and other variations that were always present

@@ -334,7 +334,7 @@ public class MathematicaEngine {
 
 	public static void main(String[] args) throws Exception {
 		MathematicaEngine mi = getInstance("TESTING");
-		String expression = Constants.SAMPLE_HEP_PROCESS;
+		String expression = Constants.SAMPLE_EQ_10;
 		Console.print(expression);
 		List<StructuralPattern> features = mi.getPatterns(expression);
 		for (StructuralPattern f : features) {

### 2014-02-11 src/cern/ch/mathexplorer/mathematica/Patterns.java

@@ -17,13 +17,9 @@ public class Patterns {
 		patterns.add(new StructuralPattern("x_*y_"));
 		patterns.add(new StructuralPattern("x_/y_"));
 		
-		patterns.add(new StructuralPattern("x_.+y_."));
-		patterns.add(new StructuralPattern("x_.-y_."));
-		patterns.add(new StructuralPattern("x_.*y_."));
-		patterns.add(new StructuralPattern("x_./y_."));
 		
-		patterns.add(new StructuralPattern("x_.+y_.+z_."));
-		patterns.add(new StructuralPattern("x_.*y_.*z_."));
+		patterns.add(new StructuralPattern("x_+y_+z_"));
+		patterns.add(new StructuralPattern("x_*y_*z_"));
 		
 		patterns.add(new StructuralPattern("a_.x_^2+b_.y_^2"));
 		patterns.add(new StructuralPattern("a_.x_^3+b_.y_^3"));
@@ -123,7 +119,6 @@ public class Patterns {
 		for(int i = 0; i< list1.size(); i++){
 			String a1 = list1.get(i);
 			for (int j = i; j<list2.size(); j++) {
-				
 				variations.add(a1+","+list2.get(j));
 			}
 		}
@@ -132,10 +127,17 @@ public class Patterns {
 	
 	static List<String> add2ArgsOperators() {
 		ArrayList<String> ret = new ArrayList<>();
-		List<String> operators = Arrays.asList("Plus[%s]", "Times[%s]", "Divide[%s]");
+		List<String> operators = Arrays.asList("Plus[%s]", "Times[%s]");
 		for(String operator: operators) {
 			for(String variation: sameArg2Variations()) {
 				ret.add(String.format(operator, variation));
+			}
+		}
+		
+		for(String variation: sameArg2Variations()) {
+			if(sameArg2Variations().contains("s1_")
+					||sameArg2Variations().contains("s2_") ) {
+				ret.add(String.format("Divide[%s]", variation));
 			}
 		}
 		return ret;

### 2014-02-11 src/cern/ch/mathexplorer/core/MathExplorer.java
fixed things included cleaning variables after simplifying

@@ -267,7 +267,7 @@ public class MathExplorer {
 	public static void main(String[] args) throws Exception {
 		
 		MathExplorer m = new MathExplorer(null, false);
-		m.testAnalyzer(Constants.SAMPLE_EQ_2);
+		m.testAnalyzer("<math><mn>2</mn><mo>+</mo><mn>3</mn></math>");
 		System.out.println("Finished");
 		//m.search(Constants.SAMPLE_EQUATION_2, true, INDEX_WHOLE_ARTICLE);
 		//testUnicodeNormalization();

### 2014-02-11 src/cern/ch/mathexplorer/lucene/analysis/analyzers/SolrNormalizerNotationalAnalyzer.java

@@ -10,7 +10,7 @@ import cern.ch.mathexplorer.lucene.analysis.filters.NumericRoundFilter;
 import cern.ch.mathexplorer.lucene.analysis.filters.RelatedOperatorsFilter;
 import cern.ch.mathexplorer.lucene.analysis.filters.UnicodeNormalizingFilter;
 import cern.ch.mathexplorer.lucene.analysis.tokenizers.MultiplePatternTokenizer;
-import cern.ch.mathexplorer.mathematica.MathematicaConfig.NORMALIZATION_MODE;
+import cern.ch.mathexplorer.mathematica.MathematicaConfig;
 import cern.ch.mathexplorer.utils.Regex;
 
 public final class SolrNormalizerNotationalAnalyzer extends SolrAnalyzer {
@@ -31,7 +31,7 @@ public final class SolrNormalizerNotationalAnalyzer extends SolrAnalyzer {
   protected TokenStreamComponents createComponents(final String fieldName,
       final Reader reader) {
 	  Tokenizer source2 = new MultiplePatternTokenizer(reader, Regex.PATTERNS, Regex.GROUP,
-			  NORMALIZATION_MODE.SIMPLE_SIMPLIFICATION);
+			  MathematicaConfig.NROMALIZATION_MODE);
 	  TokenStream unicodeNormalizer = new UnicodeNormalizingFilter(source2);
 	  TokenStream numericRounder 	= new NumericRoundFilter(unicodeNormalizer);
 	  TokenStream relatedOperators 	= new RelatedOperatorsFilter(numericRounder);

### 2014-02-11 src/cern/ch/mathexplorer/lucene/analysis/tokenizers/MathTokenizer.java

@@ -13,12 +13,12 @@ public abstract class MathTokenizer extends Tokenizer {
 
 	protected StringBuilder str = new StringBuilder();
 	final char[] buffer = new char[8192];
-	protected MathematicaConfig.NORMALIZATION_MODE normalizationMode = MathematicaConfig.NORMALIZATION_MODE.NO_SIMPLIFICATION;
+	protected MathematicaConfig.NORMALIZATION_MODES normalizationMode = MathematicaConfig.NORMALIZATION_MODES.NO_SIMPLIFICATION;
 	protected MathTokenizer(AttributeFactory factory, Reader input) {
 		super(factory, input);
 	}
 	
-	protected MathTokenizer(AttributeFactory factory, Reader input, MathematicaConfig.NORMALIZATION_MODE normalizationMode) {
+	protected MathTokenizer(AttributeFactory factory, Reader input, MathematicaConfig.NORMALIZATION_MODES normalizationMode) {
 		super(factory, input);
 		this.normalizationMode = normalizationMode;
 	}
@@ -34,14 +34,14 @@ public abstract class MathTokenizer extends Tokenizer {
 			sb.append(buffer, 0, len);
 		}
 		String tmp = str.toString();
-		if (normalizationMode.equals(MathematicaConfig.NORMALIZATION_MODE.NO_SIMPLIFICATION)){
+		if (normalizationMode.equals(MathematicaConfig.NORMALIZATION_MODES.NO_SIMPLIFICATION)){
 			
 		}
-		if (normalizationMode.equals(MathematicaConfig.NORMALIZATION_MODE.SIMPLE_SIMPLIFICATION)){
-			tmp = MathematicaEngine.getInstance("INDEXING").simplyExpressionWithTimeout(tmp);
+		if (normalizationMode.equals(MathematicaConfig.NORMALIZATION_MODES.STANDARD_SIMPLIFICATION)){
+			tmp = MathematicaEngine.getInstance("INDEXING").simplyExpressionWithTimeout(tmp, false);
 		}
-		if (normalizationMode.equals(MathematicaConfig.NORMALIZATION_MODE.FULL_SIMPLIFICATION)){
-			tmp = MathematicaEngine.getInstance("INDEXING").simplyExpressionWithTimeout(tmp);
+		if (normalizationMode.equals(MathematicaConfig.NORMALIZATION_MODES.FULL_SIMPLIFICATION)){
[…]

### 2014-02-11 src/cern/ch/mathexplorer/lucene/analysis/tokenizers/MultiplePatternTokenizer.java

@@ -28,8 +28,7 @@ import java.util.regex.Pattern;
 import org.apache.lucene.analysis.tokenattributes.CharTermAttribute;
 import org.apache.lucene.analysis.tokenattributes.OffsetAttribute;
 
-import cern.ch.mathexplorer.mathematica.MathematicaConfig;
-import cern.ch.mathexplorer.mathematica.MathematicaConfig.NORMALIZATION_MODE;
+import cern.ch.mathexplorer.mathematica.MathematicaConfig.NORMALIZATION_MODES;
 
 /**
  * This tokenizer uses regex pattern matching to construct distinct tokens for
@@ -85,7 +84,7 @@ public final class MultiplePatternTokenizer extends MathTokenizer {
 	}
 	
 	public MultiplePatternTokenizer(Reader input, List<Pattern> patterns,
-			int group, NORMALIZATION_MODE normalizationMode) {
+			int group, NORMALIZATION_MODES normalizationMode) {
 		this(AttributeFactory.DEFAULT_ATTRIBUTE_FACTORY, input, patterns, group);
 		this.normalizationMode = normalizationMode; 
 	}

### 2014-02-11 src/cern/ch/mathexplorer/lucene/query/MathQueryParser.java

@@ -148,7 +148,7 @@ public class MathQueryParser extends QParser {
 	}
 
 	public static void main(String[] args) throws Exception {
-		String query = Regex.cleanQuery(texToMathML(" $ x y \\times z $ "));
+		String query = Regex.cleanQuery(texToMathML(" \\Gamma(x) \\Gamma(1-x) "));
 		MathQueryParser mqp = new MathQueryParser(query, null, null, null);
 		mqp.parse();
 	}

### 2014-02-11 src/cern/ch/mathexplorer/mathematica/MathematicaConfig.java

@@ -5,18 +5,15 @@ import java.util.concurrent.TimeUnit;
 public class MathematicaConfig {
 	public final static boolean USE_MATHEMATICA = true;
 	
-	public final static int NO_SIMPLIFICATION = 0;
-	public final static int SINGLE_SIMPLIFICATION = 1;
-	public final static int FULL_SIMPLIFICATION = 2;
-	
-	public final static int SIMPLIFY = NO_SIMPLIFICATION;
-	
+		
 	public final static int TIMEOUT_TIME = 10;
 	public final static TimeUnit TIMEOUT_TIMEUNIT = TimeUnit.SECONDS;
 	
-	public enum NORMALIZATION_MODE{
+	public final static NORMALIZATION_MODES NROMALIZATION_MODE = NORMALIZATION_MODES.FULL_SIMPLIFICATION;
+	
+	public enum NORMALIZATION_MODES{
 		NO_SIMPLIFICATION,
-		SIMPLE_SIMPLIFICATION,
+		STANDARD_SIMPLIFICATION,
 		FULL_SIMPLIFICATION;
 	}
 

### 2014-02-11 src/cern/ch/mathexplorer/mathematica/MathematicaEngine.java

@@ -151,13 +151,22 @@ public class MathematicaEngine {
 	
 	}
 
+	public String simplyExpressionWithTimeout(String mathMLExpression){
+		if (MathematicaConfig.NROMALIZATION_MODE.equals(MathematicaConfig.NORMALIZATION_MODES.FULL_SIMPLIFICATION)) {
+			return simplyExpressionWithTimeout(mathMLExpression, true);
+		} else {
+			return simplyExpressionWithTimeout(mathMLExpression, false);
+		}
+	}
+
+	
 	/**
 	 * Calls the method for simplifyin a given string.
 	 * If the method takes more than the defined timeout, the original string is returned 
 	 */
-	public String simplyExpressionWithTimeout(String mathMLExpression){
+	public String simplyExpressionWithTimeout(String mathMLExpression, boolean full){
 		ExecutorService executor = Executors.newSingleThreadExecutor();
-        Future future = executor.submit(new MathematicaTask(mathMLExpression, TASK.SIMPLIFY_EXPRESSION));
+        Future future = executor.submit(new MathematicaTask(mathMLExpression, TASK.SIMPLIFY_EXPRESSION, full));
         try {
         	return (String) future.get(MathematicaConfig.TIMEOUT_TIME, MathematicaConfig.TIMEOUT_TIMEUNIT);
         } catch (TimeoutException te) {
@@ -173,16 +182,19 @@ public class MathematicaEngine {
 	 * expression If the process cannot be done, it return the original given
 	 * string
 	 */
-	private String simplifyExpression(String mathMLExpression) {
+	private String simplifyExpression(String mathMLExpression, boolean full) {
 		try {
 	
 			importString(mathMLExpression);
-			
-			String result = ml.evaluateToOutputForm("ExportString[Simplify[ReleaseHold[MakeExpression[importedString]]],\"MathML\"]", 0);
+			String mode = full? "FullSimplify":"Simplify";
+			String result = ml.evaluateToOutputForm("ExportString["+mode+"[ReleaseHold[MakeExpression[importedString]]],\"MathML\"]", 0);
+			clearVariables();
 			if (result.contains("<merror>") || result.contains("$Failed")) { // There was some error in the process, so we return the original string
 				return mathMLExpression;
 			}
 			result = result.replaceAll("\\r|\\n|  +", "");
+			result = result.replaceAll("<annotation.*?</annotation>", "");
+			
 			
[…]

### 2014-02-11 src/cern/ch/mathexplorer/mathematica/MathematicaUtils.java

@@ -36,6 +36,7 @@ public class MathematicaUtils {
 		try {
 			if (OSUtils.getOS().equals(OSUtils.OS.LINUX) ||
 					OSUtils.getOS().equals(OSUtils.OS.MAC)) {
+				Console.print("Killing processes in linux!!!!!!!");
 				String command1 = "killall -s 9 Mathematica";
 				String command2 = "killall -s 9 MathKernel";
 				Runtime.getRuntime().exec(command1);
@@ -43,7 +44,7 @@ public class MathematicaUtils {
 			}
 			
 			if (OSUtils.getOS().equals(OSUtils.OS.WINDOWS)) {
-				String command1 = "taskkill /im MathKerel.exe";
+				String command1 = "taskkill /im MathKernel.exe";
 				String command2 = "taskkill /im Mathematica.exe";
 				
 				Runtime.getRuntime().exec(command1);
@@ -54,4 +55,9 @@ public class MathematicaUtils {
 
 		}
 	}
+	public static void main(String[] args) {
+		killMathKernel();
+	}
 }
+
+

### 2014-02-11 src/cern/ch/mathexplorer/mathematica/Patterns.java

@@ -17,7 +17,6 @@ public class Patterns {
 		patterns.add(new StructuralPattern("x_*y_"));
 		patterns.add(new StructuralPattern("x_/y_"));
 		
-		
 		patterns.add(new StructuralPattern("x_+y_+z_"));
 		patterns.add(new StructuralPattern("x_*y_*z_"));
 		
@@ -95,20 +94,20 @@ public class Patterns {
 				String.format("Superscript[X_,%s]",secondArg), 
 				String.format("Superscript[X_,%s]",secondArg),
 				String.format("Power[X_,%s]",secondArg),
-				"SubPlus[X_]", 
-				"SubMinus[X_]", 
-				"SubStar[X_]", 
-				"SuperPlus[X_]", 
-				"SuperMinus[X_]", 
-				"SuperStar[X_]", 
-				"SuperDagger[X_]", 
+				//"SubPlus[X_]", 
+				//"SubMinus[X_]", 
+				//"SubStar[X_]", 
+				//"SuperPlus[X_]", 
+				//"SuperMinus[X_]", 
+				//"SuperStar[X_]", 
+				//"SuperDagger[X_]", 
 				String.format("Overscript[X_, %s]",secondArg), 
-				String.format("Underscript[X_,%s]",secondArg),
-				"OverBar[X_]", 
-				"OverVector[X_]", 
-				"OverHat[X_]", 
-				"OverDot[X_]", 
-				"UnderBar[X_]");
+				String.format("Underscript[X_,%s]",secondArg));
+				//"OverBar[X_]", 
+				//"OverVector[X_]", 
+				//"OverHat[X_]", 
+				//"OverDot[X_]", 
+				//"UnderBar[X_]");
 	}
 	
 	static List<String> sameArg2Variations() {
@@ -148,8 +147,6 @@ public class Patterns {
 	}
 	
 	public static void main(String[] args) {
-		for(StructuralPattern p: patterns) {
-			System.out.println(p);
-		}
+		System.out.println(patterns.size());
 	}
 }

### 2014-02-11 src/cern/ch/mathexplorer/utils/Regex.java

@@ -89,6 +89,6 @@ public class Regex {
 	}
 	
 	public static void main(String[] args) {
-		Console.print(new Regex().isTrivialEquation("<math alttext=\"\\alpha\"><mo>=</mo></math>"));
+		Console.print(extractElements("<math><mn>2</mn><mo>+</mo><mn>3</mn></math>"));
 	}
 }

### 2014-02-11 src/cern/ch/mathexplorer/mathematica/MathematicaEngine.java
focus on error while importing a string in mathematica

@@ -1,5 +1,8 @@
 package cern.ch.mathexplorer.mathematica;
 
+import java.io.BufferedReader;
+import java.io.File;
+import java.io.FileReader;
 import java.util.ArrayList;
 import java.util.HashMap;
 import java.util.HashSet;
@@ -71,7 +74,14 @@ public class MathematicaEngine {
         } catch (TimeoutException te) {
         	ml.abortEvaluation();
         } catch (Exception e) {
-        	
+        	try {
+				MathematicaUtils.killMathKernel(ml);
+				MathematicaUtils.initLink();
+
+			} catch (Exception e1) {
+				Console.print("Error while cleaning up");
+				e1.printStackTrace();
+			}
         }
 		return result;
 	}
@@ -140,7 +150,7 @@ public class MathematicaEngine {
 			// Just in case, we restart our link
 			// Cleanup operation can still fail
 			try {
-				MathematicaUtils.killMathKernel();
+				MathematicaUtils.killMathKernel(ml);
 				MathematicaUtils.initLink();
 			} catch (Exception e1) {
 				Console.print("Error while cleaning up");
@@ -172,7 +182,13 @@ public class MathematicaEngine {
         } catch (TimeoutException te) {
         	ml.abortEvaluation();
         } catch (Exception e) {
-        	
+        	try {
+				MathematicaUtils.killMathKernel(ml);
+				MathematicaUtils.initLink();
+			} catch (Exception e1) {
+				Console.print("Error while cleaning up");
+				e1.printStackTrace();
+			}
         }
 		return mathMLExpression;
 	}
@@ -204,7 +220,7 @@ public class MathematicaEngine {
 			// Just in case, we restart our link
 			// Cleanup operation can still fail
 			try {
-				MathematicaUtils.killMathKernel();
+				MathematicaUtils.killMathKernel(ml);
 				MathematicaUtils.initLink();
 			} catch (Exception e1) {
 				Console.print("Error while cleaning up");
@@ -350,6 +366,8 @@ public class MathematicaEngine {
 	}
 
 	public static void main(String[] args) throws Exception {
+		test();
+		
 		MathematicaEngine mi = getInstance("TESTING");
 		String expression = Constants.SAMPLE_EQ_5;
 		Console.print(expression);
@@ -360,6 +378,23 @@ public class MathematicaEngine {
 		Console.print(mi.simplifyExpression(expression, false));
[…]

### 2014-02-11 src/cern/ch/mathexplorer/mathematica/MathematicaUtils.java

@@ -5,6 +5,7 @@ import cern.ch.mathexplorer.utils.Constants;
 import cern.ch.mathexplorer.utils.OSUtils;
 
 import com.wolfram.jlink.KernelLink;
+import com.wolfram.jlink.MathKeyListener;
 import com.wolfram.jlink.MathLinkException;
 import com.wolfram.jlink.MathLinkFactory;
 
@@ -32,7 +33,10 @@ public class MathematicaUtils {
 		}
 	}
 	
-	static void killMathKernel() {
+	static void killMathKernel(KernelLink link) {
+		if (link !=null) {
+			link.close();
+		}
 		try {
 			if (OSUtils.getOS().equals(OSUtils.OS.LINUX) ||
 					OSUtils.getOS().equals(OSUtils.OS.MAC)) {
@@ -56,7 +60,7 @@ public class MathematicaUtils {
 		}
 	}
 	public static void main(String[] args) {
-		killMathKernel();
+		killMathKernel(null);
 	}
 }
 

### 2014-02-11 docs/thesis/chap-cern_math_explorer.tex
work on document

@@
 \begin{itemize}
-  \item Unicode Normalizing:
+  \item Unicode Normalizing: The first issue we discovered is that because of the big wide of different characters to represent the possible mathematical symbols, there is needed for an automatic way to match different possible variations of a single character.
+Some simple examples of this can be: $A$ and its compliment $\bar{A}$ in the case of set theory or ...
+\begin{tabular}{|c|c|c|c|c|c|c|}
+\hline 
+Character Rendering & Character Name & Latex Command & NFC & NFD & NFKC & NFKD \\ 
+\hline 
+A & LATIN CAPITAL LETTER  & A & 0x41 & 0x41 & 0x41 & 0x41 \\ 
+Ā & LATIN CAPITAL LETTER A WITH MACRON  & \={A} & 0x41 & 0x41 & 0x41 & 0x41 \\ 
+Å & LATIN CAPITAL LETTER A WITH RING  & \r{A} & 0x41 & 0x41 & 0x41 & 0x41 \\
+
+\hline 
+\end{tabular} 
   \item Numeric Approximation: Some equations relate specific numeric quantities.

### 2014-02-13 docs/thesis/chap-cern_math_explorer.tex
visio drawing

--- 2014-02-07 docs/thesis/chap-cern_math_explorer.tex
@@
 
+\subsubsection{Unicode Normalizing} 
+The first issue we discovered is that because of the big wide of different characters to represent the possible mathematical symbols, there is need for an automatic way to match different possible variations of a single character.
+An example of this situation is specification of an natural number, sometimes denoted by the letter N.
+In this case, at least three different common representations were identified: $ N = 1 $ (Using character with unicode code point 0x004e), $\mathcal{N} = 1$ (0xd835 0xdc41 or in latex expressed as \lstinline|\mathcal{N}|) and $\mathbb{N} = 1$ (0x2115 or in latex expressed as \lstinline|\mathbb{N}|).
+\\
+  For addressing this situation, we rely on the Unicode equivalence framework.
+In the unicode specification, sometimes the same character have two or more different code-points because of backwards compatibility with other encoding standards or because the same character has different essential meanings.
+Another group of equal characters with different code-points are pre-combined characters such as the Latin letter \~{N} which has Unicode point 0x00D1 and also is the sequence of code-points  0x004E (Latin letter N) and 0x0303 (the combining character tilde).
+Taking this sample into account, Unicode defines the character composition and decomposition operations as replacing the decomposed representation with the pre-composed one and vice-versa.
+Finally, Unicode defines two types of equivalences between characters: Canonical and compatible.
+Canonical equivalent characters are assumed to have the same appearance and meaning.
+Compatible ones are allowed to have slightly different graphical representations but the same meaning in some contexts.
+One example of compatible equivalent characters is the Roman number 12 {\unicodefontⅫ} with code-point 0x216b and the sequence of characters XII with codepoints 0x0058 0x0049 0x0049.
+Taking into account the composition or decomposition of characters and the canonical or compatible equivalences, Unicode specifies 4 different forms of a given character:
   \begin{itemize}
-  \item Unicode Normalizing:
-  \item Numeric Approximation: Some equations relate specific numeric quantities.
+  \item NFD: Normalization Form Canonical Decomposition
+  \item NFC: Normalization Form Canonical Composition
+  \item NFKD: Normalization Form Compatibility Decomposition
+  \item NFKC: Normalization Form Compatibility Composition
+  \end{itemize}
+
+Table \ref{unicode_characters} presents a small list of troubling characters classes that were identified in our datasets.
+
+\begin{longtable}{|m{4cm}|>{\centering\arraybackslash}m{2cm}|>{\centering\arraybackslash}m{1.65cm}|>{\centering\arraybackslash}m{1.65cm}|>{\centering\arraybackslash}m{1.65cm}|>{\centering\arraybackslash}m{1.65cm}|}
+\hline 
+Character Unicode Name & Visual Rendering & NFC & NFD & NFKC & NFKD \\ 
+\hline 
+LATIN CAPITAL LETTER A & A & 0x41 & 0x41 & 0x41 & 0x41 \\ 
+\hline 
+LATIN CAPITAL LETTER A WITH MACRON & \={A} & 0x100 & 0x41 0x304 & 0x100 & 0x41 0x304 \\
+\hline 
+LATIN CAPITAL LETTER A WITH RING ABOVE & \r{A} & 0xc5 & 0x41 0x30a & 0xc5 & 0x41 0x30a \\
+\hline 
+ANGSTROM SIGN (0x212b) &	\r{A} &	0xc5 &	0x41 0x30a &	0xc5 &	0x41 0x30a \\
+\hline
+LATIN CAPITAL LIGATURE IJ &	Ĳ &	0x132 &	0x132 &	0x49(I) 0x4a(J) &	0x49 0x4a \\
+\hline
+CYRILLIC CAPITAL LIGATURE A IE & {\unicodefont Ӕ} &	0x4d4 &	0x4d4 &	0x4d4 &	0x4d4 \\
+\hline
+LATIN CAPITAL LETTER AE	& {\unicodefont Ӕ}	& 0xc6	& 0xc6	& 0xc6	& 0xc6 \\
+\hline
+DOUBLE-STRUCK CAPITAL N	& {\unicodefont ℕ}	& 0x2115 & 0x2115 & 0x2115 & 0x4e \\
+\hline
+LATIN CAPITAL LETTER N	& N & 0x4e	& 0x4e & 	0x4e	& 0x4e \\
+\hline 
+MATHEMATICAL ITALIC CAPITAL N & $\mathcal{N}$	& 0xd835  0xdc41 &	0xd835  0xdc41 &	0x4e	 & 0x4e \\
+\hline 
+ROMAN NUMERAL TWELVE	& {\unicodefont Ⅻ}	&0x216b &	0x216b	& 0x58 0x49 0x49 &	0x58 0x49 0x49 \\
+\hline
+LATIN CAPITAL LETTER X - LATIN CAPITAL LETTER I - LATIN CAPITAL LETTER I &	XII &	0x58 0x49 0x49 &	0x58 0x49 0x49&	0x58(X) 0x49(I) 0x49(I) &	0x58 0x49 0x49 \\
+\hline
+VULGAR FRACTION ONE QUARTER	& \char"00BC &	0xbc &	0xbc &	0x31(1) 0x2044(/) 0x34(4) &	0x31 0x2044 0x34 \\
+\hline
+DIGIT ONE - SOLIDUS - DIGIT 4 &	1⁄4 &	0x31  0x2f 0x34 &	0x31 0x2f 0x34	& 0x31 0x2f 0x34 &	0x31 0x2f 0x34\\
+\hline
+DIGIT ONE - SOLIDUS - DIGIT 4 &	1⁄4 &	0x31  0x2f 0x34 &	0x31 0x2f 0x34	& 0x31 0x2f 0x34 &	0x31 0x2f 0x34\\
+\hline
+DIGIT ONE - FRACTION SLASH - DIGIT 4 & 1⁄4 &	0x31 0x2044 0x34 &	0x31 0x2044 0x34 &	0x31 0x2044 0x34 &	0x31 0x2044 0x34 \\
+\hline
+THERE EXISTS	& {\unicodefont ∃}&	0x2203 &	0x2203 &	0x2203 &	0x2203 \\
+\hline
+THERE DOES NOT EXIST	& {\unicodefont ∄} & 	0x2204	& 0x2203 0x338& 	0x2204 &	0x2203 0x338\\
+\hline
+LATIN CAPITAL LETTER OPEN E	& {\unicodefont Ɛ} &	0x190 &	0x190 &	0x190 &	0x190 \\
+\hline
+EULER CONSTANT	& {\unicodefont ℇ} & 0x2107 & 0x2107 & 0x190 & 0x190 \\
+\hline
+PLANCK CONSTANT	& {\unicodefont ℎ} &	0x210e &	0x210e &	0x68 &	0x68 \\
+\hline
+LATIN SMALL LETTER H &	h &	0x68 &	0x68 &	0x68 &	0x68 \\
+\hline
+PLANCK CONSTANT OVER TWO PI	& {\unicodefont ℏ} &	0x210f &	0x210f	& 0x127 &	0x127 \\
+\hline
+LATIN SMALL LETTER H WITH STROKE & ħ &	0x127	& 0x127	& 0x127	& 0x127 \\
+\hline
+GREEK CAPITAL LETTER OMEGA	& Ω &	0x3a9 &	0x3a9 &	0x3a9 &	0x3a9 \\
+\hline
+OHM SIGN & Ω &	0x2126 &	0x2126 &	0x3a9 &	0x3a9 \\
+\hline
+INTEGRAL & {\unicodefont ∫} &	0x222b &	0x222b &	0x222b &	0x222b \\
+\hline
+DOUBLE INTEGRAL	& {\unicodefont ∬} & 	0x222c &	0x222c &	0x222b 0x222b &	0x222b 0x222b \\
+\hline
+CONTOUR INTEGRAL	& {\unicodefont ∮} &	0x222e	 &0x222e &	0x222e &	0x222e \\
+\hline
+\caption{Characters with similar glyphs and/or semantics}
+\label{unicode_characters}
+\end{longtable}
+
+Since our goal is to match as much as possible similar characters, our system employs the NFKD representation of a character.
+For a given token, we test whether if it is already equal to its NFKD.
+If not, for all the characters that are not combining nor control characters, we add the token into the same position as the original one.
+For example, given the token <mi>\r{A}</mi>, this will lead to the sequence <mi>\r{A}</mi><mi>A</mi> and the token <mi>{\unicodefontⅫ}</mi> will produce <mi>{\unicodefontⅫ}</mi><mi>X</mi><mi>I</mi><mi>I</mi>.
+
+\subsubsection{Synonym Expansion}
+Even though the Unicode normalization step work for a big part of the cases presented in table \ref{unicode_characters}, there are still some groups of characters which would not be matched (Even partially), such as some types of integrals.
+For addressing these groups, a precomputed table was created for some general groups of characters which have some similar meaning.
+For each token that belongs to some of this predefined groups, a second token is created identifying the group.
+For example the token <mo>{\unicodefont ∮}</mo> is expanded into <mo>{\unicodefont ∮}</mo><mo>INTEGRALS</mo>, similarly the token token <mo>{\unicodefont ∫}</mo> is expanded into <mo>{\unicodefont ∫}</mo><mo>INTEGRALS</mo> and then both will have a partial match in the INTEGRALS token.
+Unicode specification does not define a strict rule to group similar characters based on their semantics.
+For general operators, we used the grouping provided by Xah Lee in his website\cite{math_groups}.
+
+\subsubsection{Numeric Approximation} 
+Some equations relate specific numeric quantities.
 While most of the previously explorer systems, handled <mn> tags by only representing them as a constant identifier, this approach is not suitable.
 A lot of articles in CDS relate to specific experiments under certain conditions, and require a high level of precision in the measurements.
-  \item Grouping of similar operators:
-\end{itemize}
 
@@
 \subsection{Development with Lucene/Solr}
-
+This section explains how the described features were implemented in the Apache Solr/Lucene framework.
 \subsection{Integration with Mathematica}

### 2014-02-13 docs/thesis/chap-evaluation.tex
visio drawing

\chapter{Evaluation}
...
The machine used for experiments has a Intel Core i7 processor running at 3.4Ghz with 4 cores. The available RAM is 8Gb, and the Java Virtual Machine used for running Solr was run with the $-Xms2G -Xmx5G$ parameters. The OS was Linux Mint 16 Petra, which is a fork based on Ubuntu, running on kernel 3.11.0-15.

\section{Dataset}

\section{Indexing Performance}
For this set of evaluations, we were only interested in observing how the performance of the indexing stage is affected by the different types of features that are employed. We selected the first 100 records from our dataset and measured the total time it required to index all the elements in Solr using a python script and the solrpy library to do the communication. The default similarity in Solr was used. We also measured the index size at the end of each experiment.
Our four scenarios were organized as follows:
\begin{itemize}
\item N : Only notational features over the original expression were used
\item N+S : Notational and structural features over the original expression
\item N+S+NN : Notational and structural features over the original expression and notational features over the normalized string using Mathematica's Simplify function
\item N+S+FN : Notational and structural features over the original expression and notational features over the normalized string using Mathematica's Full Simplify function
\end{itemize}

Table \ref{index_experiments_table} summarizes the results of this set of experiments. The first result is the significant increase in processing time when using Mathematica. Going from the N scenario to N+S represent an increase of almost 15x in the indexing time. Adding standard normalization increases the indexing time by a factor near to 1.44x and full normalization by a factor of 1.55x.

With respect to storage size, we see a small footprint (Less than 5\%)in the total size by going from N to N+S. Adding normalization represents an increase by a factor of 1.78x and the size of the fully normalized index represents a smaller increase (1.76x)

We can observe that there is a small trade-off between time and storage size depending on which normalization mode is employed.

\begin{tabular}{|c|c|p{2cm}|p{2cm}|p{2cm}|}
\hline 
Feature Set & Total time (sec) & Index Size (kb) & Avg. time per equation & Avg. size of equation (kb) \\ 
\hline 
N & 58 & 13926 & 0.00524 & 1.237 \\ 
\hline 
N+S & 884 & 14438 & 0.0785 & 1.282 \\ 
\hline 
N+S+NN & 1273 & 25780 & 0.113 & 2.345 \\ 
\hline 
N+S+FN & 1377 & 25548 & 0.122 & 2.269 \\ 
\hline 
\end{tabular}

### 2014-02-13 src/cern/ch/mathexplorer/mathematica/MathematicaEngine.java

@@ -368,15 +368,15 @@ public class MathematicaEngine {
 	
 	public static void test() throws Exception {
 		BufferedReader br = new BufferedReader(new FileReader(new File(
-				"/share/math/arxiv_cds/arx1312.6708.eq")));
+				"./data/arxiv_cds/arx1312.6708.eq")));
 		String line = "";
 		MathematicaEngine instance = getInstance("TESTING");
 		int count = 0;
 		while ((line = br.readLine()) != null) {
-			//instance.simplyExpressionWithTimeout(line);
-			//instance.getPatternsWithTimeout(line);
-			instance.getPatterns(line);
-			instance.simplifyExpression(line, true);
+			instance.simplyExpressionWithTimeout(line);
+			instance.getPatternsWithTimeout(line);
+			//instance.getPatterns(line);
+			//instance.simplifyExpression(line, true);
 			
 			Console.print(count++);
 		}

### 2014-02-17 docs/thesis/chap-cern_math_explorer.tex
more work on thesis document

@@
 
-\begin{longtable}{|m{4cm}|>{\centering\arraybackslash}m{2cm}|>{\centering\arraybackslash}m{1.65cm}|>{\centering\arraybackslash}m{1.65cm}|>{\centering\arraybackslash}m{1.65cm}|>{\centering\arraybackslash}m{1.65cm}|}
+\begin{longtable}{|m{4cm}|>{\centering\arraybackslash}m{2.15cm}|>{\centering\arraybackslash}m{1.65cm}|>{\centering\arraybackslash}m{1.65cm}|>{\centering\arraybackslash}m{1.65cm}|>{\centering\arraybackslash}m{1.65cm}|}
 \hline 
-Character Unicode Name & Visual Rendering & NFC & NFD & NFKC & NFKD \\ 
+\textbf{Character Name} & \textbf{Visual Rendering} & \textbf{NFC} & \textbf{NFD} & \textbf{NFKC} & \textbf{NFKD} \\ 
 \hline 
@@
 \subsection{Structural Features}
+\subsubsection{}
+\subsubsection{Algebraic structures}
+This set of structures consist on purely algebraic relationships between the expressions.
+Inspired by predefined integral tables for different kinds of expressions, we decided to extract from a given equation, whether it has the occurrence of these kind of patterns.
+An example of this type of structures would be: $X\textunderscore*(X\textunderscore + A\textunderscore)$ where $X\textunderscore$ and $A\textunderscore$ can be any type of expression.
+Sample equations matching this pattern can be $C (C+1)$ or $\frac{(\sin{\theta}\cos{\theta})^2}{2a} (\frac{(\sin{\theta}\cos{\theta})^2}{2a} + \tan{\frac{\theta+\phi}{2}})$.
+This structural analysis of equations is more powerful than the unification of variables and constants proposed in previously discussed projects because these patterns, as shown in the second example, can match an arbitrary complex expression.
+The drawback of our solution is the need to manually select representative and useful patterns.
+This selection was done based on standard based tables of integrals similar to the ones that Computational Algebraic Systems employ to compute them.
+
+\subsubsection{Specific domain structures}
+Additionally, we identified patterns that are relevant and frequent in specific domains of the high energy physics.
 
 \subsection{Development with Lucene/Solr}
-This section explains how the described features were implemented in the Apache Solr/Lucene framework.
+This section explains how the described features were implemented in the \verb|Apache Solr/Lucene| framework.
 \subsection{Integration with Mathematica}
-This section describes some aspects that should be considered while implementing the integration with the Mathematica CAS.
+This section describes some aspects that should be had to be considered while implementing the integration with the Mathematica CAS.
+Our system uses the provided \verb|JLink| library to create a connection with the underlying process \verb|MathKernel|.
+The main class for communicating java code and \verb|Mathematica| is \verb|KernelLink| and the main used method was \verb|evaluateToOutputForm(String expr, int pageWidth)| where \verb|expr| is the expression to be evaluated and \verb|pageWidth| affects the formatting of the result.
+
+\subsubsection{Pattern Extraction}
 
@@
 \subsubsection{Error handling}
-Sometimes after certain time Mathematica will crash, launch an exception and following invocations would fails as well.
+Sometimes, after certain time, the connection between \verb|KernelLink| and \verb|Mathematica| will be lost launch an exception and following invocations would fails as well.
 Also, re-instantiating a KernelLink will yield an Exception. For this scenario, killing the associated processes to Mathematica was necessary:
@@
 <mi>h</mi><mo></mo><mi>o</mi><mo></mo><mi>w</mi><mo></mo><mi>n</mi>
-</mrow><mo>,</mo><mrow><mi>a</mi><mo></mo>
-<mi>s</mi></mrow><mo></mo><mrow><mi>w</mi><mo></mo>
-<mi>e</mi><mo></mo><mi>l</mi><mo></mo><mi>l</mi>
-</mrow><mo></mo><mrow><mi>a</mi><mo></mo>
-<mi>s</mi></mrow><mo></mo><mrow><mi>t</mi><mo></mo>
-<mi>h</mi><mo></mo><mi>e</mi></mrow><mo></mo>
-<mrow><mi>w</mi><mo></mo><mi>e</mi><mo></mo>
-<mi>i</mi><mo></mo><mi>g</mi><mo></mo><mi>h</mi>
-<mo></mo><mi>t</mi></mrow><mo></mo><mrow>
-<mi>a</mi><mo></mo><mi>n</mi><mo></mo><mi>d</mi>
-</mrow><mo></mo><mrow><mi>t</mi><mo></mo><mi>e</mi>
-<mo></mo><mi>n</mi><mo></mo><mi>s</mi><mo></mo>
-<mi>i</mi><mo></mo><mi>o</mi><mo></mo><mi>n</mi>
-</mrow></mrow></math>
+</mrow><mo>,</mo><mrow><mi>a</mi><mo></mo><mi>s</mi></mrow><mo></mo>
+<mrow><mi>w</mi><mo></mo><mi>e</mi><mo></mo><mi>l</mi><mo></mo>
+<mi>l</mi></mrow><mo></mo><mrow><mi>a</mi><mo></mo><mi>s</mi>
+</mrow><mo></mo><mrow><mi>t</mi><mo></mo><mi>h</mi><mo></mo>
+<mi>e</mi></mrow><mo></mo><mrow><mi>w</mi><mo></mo><mi>e</mi><mo>
+</mo><mi>i</mi><mo></mo><mi>g</mi><mo></mo><mi>h</mi><mo></mo>
+<mi>t</mi></mrow><mo></mo><mrow><mi>a</mi><mo></mo><mi>n</mi><mo>
+</mo><mi>d</mi></mrow><mo></mo><mrow><mi>t</mi><mo></mo><mi>e</mi>
+<mo></mo><mi>n</mi><mo></mo><mi>s</mi><mo></mo><mi>i</mi>
+<mo></mo><mi>o</mi><mo></mo><mi>n</mi></mrow></mrow></math>
 \end{verbatim}

### 2014-02-17 docs/thesis/chap-evaluation.tex
more work on thesis document

@@
 ...
+
+\section{Dataset}
+Our dataset consists on 12234 latex documents fetched from ArXiV.
+This documents correspond to the latest records harvested for CDS.
+The documents were processed using LateXML as described in the extraction process.
+From the given dataset, the simpler equations were filtered out (The ones containing one or two elements).
+
+\section{Setup}
+
 The machine used for experiments has a Intel Core i7 processor running at 3.4Ghz with 4 cores.
 The available RAM is 8Gb, and the Java Virtual Machine used for running Solr was run with the $-Xms2G -Xmx5G$ parameters.
-The OS was Linux Mint 16 Petra, which is a fork based on Ubuntu, running on kernel 3.11.0-15.
+The complete specifications of the used software is presented in table \ref{sw_used}
 
-\section{Dataset}
+\begin{longtable}{|m{2cm}|>
+{\centering\arraybackslash}m{4cm}|>
+{\centering\arraybackslash}m{4cm}|
+}
+\hline 
+\textbf{Software} & 
+\textbf{Version} 
+\\
+\hline
+Operative System & Linux Mint 16 Petra (Ubuntu based) \\ \hline
+Linux Kernel & 3.11.0-15 \\ \hline
+Java Virtual Machine & 1.7.0-45 \\ \hline
+Apache Solr & 4.6 \\ \hline
+Python & 2.7.5+ \\ \hline
+\caption{Software used during evaluations}
+\label{sw_used}
+\end{longtable}
 
@@
 
-Table \ref{index_experiments_table} summarizes the results of this set of experiments.
+Table \ref{indexing_performance} summarizes the results of this set of experiments.
 The first result is the significant increase in processing time when using Mathematica.
@@
 
-\begin{tabular}{|c|c|p{2cm}|p{2cm}|p{2cm}|}
+\begin{longtable}{|c|c|p{2cm}|p{2cm}|p{2cm}|}
 \hline 
@@
 \hline
-\end{tabular}
+\caption{Indexing performance}
+\label{indexing_performance}
+\end{longtable}

### 2014-02-17 docs/thesis/chap-technical_considerations.tex
more work on thesis document

@@
 \section{Math Extraction Tools}
-\section{From LaTeX to MathML}
-\subsection{From PDF to MathML}
-\subsubsection{Maxtract}
-\subsubsection{InftyReader}
-\subsubsection{OCR analysis}
-\subsection{Other projects}
+One of the main steps in any information retrieval task is the extraction of the searchable content from the collection of documents.
+At CDS the most common storage format for publications is PDF.
+A big part of the harvested documents in CDS comes from the ArXiv pre-prints service and from here, the source code (\LaTeX) of the submissions is available for download.
+Smaller portions of other documents are stored in other formats like Microsoft Word, OpenOffice Documents.
+In practice, the main options from where to do the extraction from, are PDFs and \LaTeX  files.
+Also taking into account the previous discussion on the available format for representing mathematics, we focused our attention in tools that output MathML.
+\\
+A conscious exploration of available software for extracting mathematical content from this two types of documents allowed us to identify different tools with different approaches. 
+\LaTeX  files are easier to process and all of the tools implement their own compiler that XML + MathML outputs instead of the typical.
+Since the original math equation is provided in the document, there is relatively little ambiguity in the equation, and the major issues that the systems struggle with is in the coverage of all the possible commands and packages that are available.
+\\
+For extracting equations from PDF files, the process turns into an Optical Character Recognition (OCR).
+The reconstruction of the equation has to infer the mathematical structure based on physical positioning and size of the symbols, the length of the lines and so on.
 
-\section{Computational Algebraic Systems}
-In the previous section we discussed about algorithmical ways to tranform, simplify and detect patterns in mathematical equations.
-Here, we explore what tools are available for performing this type of operations and how they are suitable for our system.
+Table \ref{math_extraction_tools} presents the main features of the reviewed software.
 
-\subsection{Mathematica}
-\subsection{Mapple}
-\subsection{Matlab}
-\subsection{Octane}
-\subsection{SAGE}
+\begin{longtable}{|
+m{2.8cm}|>{\centering\arraybackslash}
+m{2cm}|>{\centering\arraybackslash}
+m{1.65cm}|>{\centering\arraybackslash}
+m{1.65cm}|>{\centering\arraybackslash}
+m{1.65cm}|>{\centering\arraybackslash}
+m{1.95cm}|>{\centering\arraybackslash}
+m{1.65cm}|>{\centering\arraybackslash}
+m{1.65cm}|
+}
+\hline 
+\textbf{Software} & \textbf{Type} & \textbf{Tested version} & \textbf{Input Format(s)} & \textbf{Output Format(s)} & \textbf{Licence Type} & \textbf{Latest Update}  \\
+\hline
+LaTeXML\cite{latexml} & Standalone Executable &0.7.9alpha & \LaTeX & XML + MathML & Open Source & 13 Feb 2014  \\
+\hline
+TeX4ht\cite{tex4ht1}\cite{tex4ht2} & Standalone Executable & 2009-01-31-07 & \LaTeX & XML + MathML & Open Source & 11 Jun 2009  \\
+\hline
+LaTeXmathML\cite{latexmathml} & Javascript Library & 30-October-2007 & \LaTeX & XML + MathML & Open Source & 30 Oct 2007  \\
+\hline
+Maxtract\cite{maxtract1}\cite{maxtract2} & Standalone Executable & v.1752 & PDF & \LaTeX / Annotated PDF & Free to download & 15 Nov 2012  \\
+\hline
+InftyReader\cite{infty1}\cite{infty2} & Standalone Executable (On Windows) & 2.9.6.2 & PDF, TIFF, BMP, GIF, PNG & \LaTeX, XML + MathML & Commercial & 22 Dec 2013  \\
+
+\hline
+\caption{Comparison of available Mathematical extraction tools}
+\label{math_extraction_tools}
+\end{longtable}
+
+For extraction from \LaTeX  files we concluded that the best option is LaTeXML.
+The tool is still in current development and has lot of support from the academic community.
+The performance on a small dataset also showed that the results are consistently better than from the other tools.
+A more thorough test\cite{latexcomparison} also confirms that LaTeXML provides the best results.
+For PDF files, the trial version of InftyReader worked very well giving better results and processing successfully more files than Maxtract.
+As said previously, a big portion of the documents stored in CDS, come from pre-printing services like ArXiV were fortunately the source code of an article is available and because of this reason, our base set for this work will consist on extracting equations from \LaTeX files.
+For licensing reasons, for this project we will not integrate our system with InftyReader for the moment and will proceed with LaTeXML as our extraction tool.
+
+\section{Computer Algebra Systems}
+Computer Algebra Systems (CASs) are software packages that allow performing symbolic transformations on mathematical objects.
+They allow to manipulate, simplify and analyse mathematical equations and offer interesting functionalities for a mathematical based search engine.
+The most important functionalities that we are looking for in such system are simplification and normalization of mathematical expressions and pattern matching.
+As discussed previously, the language for representing expressions will be MathML, so we also require that such system is able to import this format.
+Finally, we are also interested in integrating these functionalities in a bigger system, so integration trough APIs was also considered.
+
+\begin{longtable}{|m{2cm}|>
+{\centering\arraybackslash}m{2cm}|>
+{\centering\arraybackslash}m{1.65cm}|>
+{\centering\arraybackslash}m{1.65cm}|>
+{\centering\arraybackslash}m{1.65cm}|>
+{\centering\arraybackslash}m{1.95cm}|>
+{\centering\arraybackslash}m{1.65cm}|>
+{\centering\arraybackslash}m{1.65cm}|
+}
+\hline 
+\textbf{CAS} & 
+\textbf{Imports MathML} & 
+\textbf{Expression normalization} & 
+\textbf{Pattern Matching}  &
+\textbf{License Type}  &
+\textbf{Supported APIs}
+\\
+\hline
+Maple &  Yes & Yes & Yes & Commercial & C, Java, VB \\ \hline
+MatLab (Symbolic Math Toolbox) & Experimental & Yes & Yes & Commercial & C/C++, Fortran \\ \hline
+Mathematica &  Yes & Yes & Yes & Commercial & C, Java, .NET \\ \hline 
+Maxima &  Experimental & Yes & Yes & Open Source  & C++, Java (External Project) \\ \hline
+SymPy & No & Yes & Yes & Open Source & Python \\ \hline
+
+\caption{Comparison of main CAS}
+\label{CAS_comparison}
+\end{longtable}
+
+Table \ref{CAS_comparison} presents a comparison of the desired features in the main CASs.
+The systems that better fit our requirements are Maple and Mathematica.
+For licensing reasons, we will continue our project using Mathematica.

### 2014-02-17 docs/thesis/chap-theoretical_background.tex
work on document
more work on thesis document

@@
 \section{Boolean Model}
-This model was the first one to be developed and is currently one of the most used in the current implementation of IR systems because of its simplicity.
+The Boolean model of Information Retrieval (BIR) was the first one to be developed and is currently one of the most used in the current implementation of IR systems because of its simplicity.
+It is based on the mathematical concepts of Boolean Logic and Set Theory.
+A formalization of this framework can be stated as follows:
+
+Given a set of terms $T = {t_1, t_2, ...
+, t_n}$ which are the terms that will be indexed (In a standard search engine this can be the set of words in a language after some normalization steps), a set of documents $D = {d_1, d_2, ...
+, d_n} $ where $d_i \in \mathcal{P}(T) $ that the user will search for.
+A query element $q$ is a Boolean expression over the index terms and the operators $AND$ , $OR$ and $NOT$.
+We define the predicate $ Relevant(q, d_i) $ if a document $d_i$ satisfies the query expression $q$.
+Finally the result for query over a collection of documents can now be written as $Result(q, D) = \{d | Relevant(q, d)\}$
+The benefits of this model are its simplicity, both in its formalism and in its implementation. 
+The main disadvantage of  BIR are the fact that all terms are given the same importance which makes it difficult to rank results.
+Since all results have same importance, it is difficult also to limit the number of retrieved documents and therefore the output set can be difficult to process for the final user.
+
+One of the key data structures for an efficient implementation of this model is the inverted index where for a given term, the index stores which documents contain it.
+This structure is used to efficiently solve queries by only scanning document that contain at least one of the terms in the query.
+Scanning a document can be done by using a standard (Also called forward) index, where for a given document, the index stores the terms associated with it.
+Both indexes can be implemented using hash tables.
 

### 2014-02-17 docs/thesis/chap-cern_math_explorer.tex
more work on document

@@
-\chapter{CERN Math Explorer}
+\chapter{MASE(CDS)}
 \label{chapter-cern_math_explorer}
-In this chapter we propose our solution for a scalable math based oriented search engine. We present the key points of our system, and how they are related to previous built systems.
+In this chapter we present our solution called MASE(CDS), Math Aware Search Engine (For CDS). We present the key points of our system, and how they are related to previous built systems.
 
-\section{Information Retrieval Model}
+\section{Features Extraction}
 Our main goal is to develop a system that compliments the already available search capabilities in Invenio and in particular the CDS instance.
-Our system was developed using the Apache Solr/Lucene framework.
+Our system was developed on top of the  the Apache Solr/Lucene framework.
+CDS already uses Solr as a search engine layer, so developing MASE using this technology supposed a reasonable choice.
+One of the main steps while building an IR tool, is understanding the data and what kind of features can be extracted from it: If the system is based on text, then tasks as stemming, handling of synonyms, misspelling and so on, such be taken into consideration; if the system being developed is based on images, then examples of features can be histograms of colors, geometrical features and so on.
+During the literature review, we discovered that most of the projects handled the notational aspects of the expressions, that is, the real naming of the terms in a given equation and each project developed its own set of heuristics to handle the structural component.
 
@@
 A lot of articles in CDS relate to specific experiments under certain conditions, and require a high level of precision in the measurements.
+However, different experiments of the same phenomenon, can result in different measurements and we wanted to include this variability in our system.
+To handle this, when a token with a certain numeric quantity is discovered, we apply iterative rounding and index all the different approximations in the same position as the original element.
+For example the token <mn>2.0135</mn> will produce the following sequence of tokens: <mn>2.0135</mn><mn>2.014</mn><mn>2.01</mn><mn>2.0</mn>.
 
 \subsection{Structural Features}
-\subsubsection{}
+
 \subsubsection{Algebraic structures}
-This set of structures consist on purely algebraic relationships between the expressions.
+The first set of structures consist on purely algebraic relationships between the expressions.
 Inspired by predefined integral tables for different kinds of expressions, we decided to extract from a given equation, whether it has the occurrence of these kind of patterns.
@@
 This selection was done based on standard based tables of integrals similar to the ones that Computational Algebraic Systems employ to compute them.
+
+\subsubsection{Non-formal mathematical variations}
+This set of structures represent common operations that cat appear in a given expression, but its identification is based on notation factors.
+A simple example of this can be the matrix decomposition $A = VDV^{-1}$ where the actual name of the variables $A$ and $V$ is not meaningful but the real importance is the fact that a given variable appears alongside its inverse in a matrix multiplication form.
+We would like to assign a partial match to any other kind of this decomposition say $B = MRM^{-1}$.
+these types of structures live in-between the notational and structural categories but, as it will be discussed, we identify them using Mathematica and encompass them as structural features.
 

### 2014-02-17 docs/thesis/chap-evaluation.tex
more work on document

@@
 \end{longtable}
+
+\section{Results quality}
+In this section we are interested in evaluating the quality of the results provided by our system.
+The type of queries that MASE was designed for, are typical equations that can be found in a scientific publication. 
+Out main user case is that a user of CDS is interested in finding documents inside the collection whose equations are related to the one that is provided.
+
+\subsection{Equations}
+The evaluated queries were provided by physics experts working at CERN from their own research topics. The queries were provided in \LaTeX format as the users used them in their own publications.
+Table \ref{equations_table} presents the set of queries that were evaluated, and a simple explanation about it.
+
+\begin{longtable}{|m{1cm}|>
+{\centering\arraybackslash}m{3cm}|>
+{\centering\arraybackslash}m{5cm}|>
+{\centering\arraybackslash}m{5cm}|
+}
+\hline 
+\textbf{Id} & 
+\textbf{Description} &
+\textbf{MathML code} &
+\textbf{Visual Rendering}
+
+\\
+\hline
+Eq1 & Time-independent Schr\char"00F6dinger equation & \scriptsize {\codefont <math><mfenced close=")" open="("> <mrow> <mo>-</mo> <mfrac> <msup> <mi>ℏ</mi> <mn>2</mn> </msup> <mrow> <mn>2</mn> <msub> <mi>m</mi> <mi>e</mi> </msub> </mrow> </mfrac> <msup> <mo>∇</mo> <mn>2</mn> </msup> <mo>+</mo> <mi>V</mi> <mfenced close=")" open="("> <mi>r</mi> </mfenced> </mrow> </mfenced> <mi>ψ</mi> <mfenced close=")" open="("> <mi>r</mi> </mfenced> <mo>==</mo> <mi>E</mi> <mi>ψ</mi> <mfenced close=")" open="("> <mi>r</mi> </mfenced> </math>} & $\left (-\frac{\hbar^{2}}{2m_e}\nabla^{2} + V(\mathbf{r})\right )\psi(\mathbf{r}) = E\psi(\mathbf{r})$ \\ \hline
+
+\caption{Software used during evaluations}
+\label{equations_table}
+\end{longtable}
+
+\section{Querying Performance}
 

### 2014-02-17 docs/thesis/chap-related_work.tex
visio drawing
more work on document

@@
 \subsection{MathWebSearch}
+MathWebSearch\cite{mathwebsearch} (Currently on its 0.5 version) is a open-source search engine for mathematical equations.
+While most of the documentation relates on the architecture of the system and how they address scalability; the indexing technique is also very interesting.
+The system implements and idea proposed by Peter Graf in \cite{substitution_tree_indexing} called substitution tree indexing.
+This idea can be viewed as a generalization of the variable and constant unification employed by MIaS
+
 \subsection{LaTEXSearch}

### 2014-02-17 docs/thesis/chap-theoretical_background.tex
more work on document

@@
 \section{Vector Space Model}
+The vector space model\cite{vector_space_model} which was developed between the 1960s and 1970s alongside the SMART Information Retrieval System.
+In this model, documents (from a collection $D$) and queries are represented as vectors $d$ and $q$ in a vector space where each index term corresponds to a dimension.
+If a term $t_i$ occurs in a given query or document, its i-th  coordinate will have a non zero value.
+Index terms can be keywords or phrases in the context of textual search or any other type of feature that can be extracted from the elements in a given specific context.
+The scoring of a document for a given query is computed as the cosine of the angle between both vectors which can be expressed as: 
+$$score(d, q) = cos\theta = \frac{d \cdot q}{\parallel d \parallel \parallel q \parallel}  = \frac{\sum_{i=1}^{n}weight(d_i, d)*weight(q_i, q)}{\sqrt{\sum_{i=1}^{n}weight^2(d_i, d)}\sqrt{\sum_{i=1}^{n}weight^2(q_i, q)}} $$
+
+Different weighting schemes can be employed, and the most standard one is called tf-idf (Term frequency - Inverse document frequency) where terms that appear less frequently in the corpus, are assigned higher values (Intuitively the term "the" will be less useful for identifying a relevant document than the term "Shakespeare" in the context of an English word based search engine).
+Therefore:
+
+$$weight(t, d) = tf(t,d) idf(t)$$
+
+There are several variations for each of the two components.
+Some approaches for $tf$ include the raw frequency; Boolean frequency: $tf(t,d) = 1$ if $t$ occurs in $d$ or 0 if not; logarithmically scaled: $tf(t,d) = 	\log(frequency(t,d) +1)$
+and the augmented frequency: $tf(t,d) = 0.5 + \frac{0.5*frequency(t,d)}{ \max\{frequency(t^\prime,d) | t^\prime \in d\} }$.
+For computing the inverse document frequency the standard approach follows $idf = \log \frac{|D|}{1+\{d \in D: t \in d \}} $
+
+The main drawbacks of this approach reside in the assumption that the terms are independent.
 
@@
 The probabilistic relevance model was developed in 1976 by Robertson and Jones\cite{probabilistic_relevance_model}.
-The similarity of a document $d_{j}$ to a query $q$ is given by the probability of $d_{j}$ being relevant to $q$.
+The similarity of a document $d$ to a query $q$ is given by the probability of $d$ being relevant to $q$.
 It assumes there is a set $R$ that is preferred to be the answer set for $q$.
@@
 
-$$sim(d_{j},q) = \frac{ P(R|d_{j})} {P(\bar{R} |d_{j})} $$
+$$sim(d,q) = \frac{ P(R|d)} {P(\bar{R} |d)} $$
 
@@
 The actual scoring function is called BM25 and Okapi refers to the first system implementing this function in the 1980s.
-Given a query $Q$ as a vector of keywords $q_{1}, q_{2}, ... , q_{n}$ then the score for a document $d$ is:
+Given a query $q$ as a vector of keywords $q_{1}, q_{2}, ... , q_{n}$ then the score for a document $d$ is:
 
-$$score(d, Q) = \sum_{i=1}^{n}IDF{(q_i)}*\frac{ frec(q_i, D)}{frec(q_i, D)+k_1*((1-b)+b*\frac{|D|}{avgdl})} $$
+$$score(d, q) = \sum_{i=1}^{n}IDF{(q_i)}*\frac{ frec(q_i, D)}{frec(q_i, D)+k_1*((1-b)+b*\frac{|D|}{avgdl})} $$
 and $$IDF(q_i) = \log{\frac{N - df(q_i)+0.5}{df(q_i)+0.5}} $$
@@
 
-$$score(d, Q) = \sum_{i=1}^{n} \frac{weigth(q_i, d)}{k+ weigth(q_i, d)} * IDF(q_i)$$
+$$score(d, q) = \sum_{i=1}^{n} \frac{weigth(q_i, d)}{k+ weigth(q_i, d)} * IDF(q_i)$$
 and 

### 2014-02-17 src/cern/ch/mathexplorer/core/MathExplorer.java

@@ -91,7 +91,10 @@ public class MathExplorer {
 
 	public static final boolean INDEX_WHOLE_ARTICLE = false;
 	
-	private MathExplorer(ServletContext context, boolean forceRebuild) {
+	private MathExplorer(ServletContext context, boolean forceRebuild, boolean forceSkip) {
+		if (forceSkip){
+			return;
+		}
 		try {
 			working_dir = (context == null) ? LOCAL_PATH : context
 					.getRealPath("/data");
@@ -115,7 +118,7 @@ public class MathExplorer {
 	public static MathExplorer getInstance(ServletContext context) {
 		try {
 			if (singleton == null) {
-				singleton = new MathExplorer(context, true);
+				singleton = new MathExplorer(context, true, false);
 			}
 			return singleton;
 		} catch (Exception e) {
@@ -266,8 +269,8 @@ public class MathExplorer {
 
 	public static void main(String[] args) throws Exception {
 		
-		MathExplorer m = new MathExplorer(null, false);
-		m.testAnalyzer(Constants.SAMPLE_EQ_1);
+		MathExplorer m = new MathExplorer(null, false, true);
+		m.testAnalyzer(Constants.SAMPLE_EQ_1_N);
 		System.out.println("Finished");
 		//m.search(Constants.SAMPLE_EQUATION_2, true, INDEX_WHOLE_ARTICLE);
 		//testUnicodeNormalization();

### 2014-02-17 src/cern/ch/mathexplorer/lucene/query/MathQueryParser.java

@@ -148,7 +148,7 @@ public class MathQueryParser extends QParser {
 	}
 
 	public static void main(String[] args) throws Exception {
-		String query = Regex.cleanQuery(texToMathML(" \\Gamma(x) \\Gamma(1-x) "));
+		String query = Regex.cleanQuery(texToMathML("\\left (-\\frac{\\hbar^{2}}{2m_e}\\nabla^{2} + V(\\mathbf{r})\\right )\\psi(\\mathbf{r}) = E\\psi(\\mathbf{r})"));
 		MathQueryParser mqp = new MathQueryParser(query, null, null, null);
 		mqp.parse();
 	}

### 2014-02-19 docs/thesis/chap-cern_math_explorer.tex
Added aditional equations to document added gradient operator group

@@
 \hline
+NABLA	& {\unicodefont ∇} &	0x2207	 &0x2207 &	0x2207 &	0x2207 \\
+\hline
+WHITE DOWN-POINTING TRIANGLE	& {\unicodefont ▽} &	0x25bd	 &0x25bd &	0x25bd &	0x25bd \\
+\hline
+
 \caption{Characters with similar glyphs and/or semantics}
@@
 \subsection{Development with Lucene/Solr}
-This section explains how the described features were implemented in the \verb|Apache Solr/Lucene| framework.
+This section explains how the described features were implemented in the {\codefont Apache Solr/Lucene} framework.
 \subsection{Integration with Mathematica}
 This section describes some aspects that should be had to be considered while implementing the integration with the Mathematica CAS.
-Our system uses the provided \verb|JLink| library to create a connection with the underlying process \verb|MathKernel|.
-The main class for communicating java code and \verb|Mathematica| is \verb|KernelLink| and the main used method was \verb|evaluateToOutputForm(String expr, int pageWidth)| where \verb|expr| is the expression to be evaluated and \verb|pageWidth| affects the formatting of the result.
+Our system uses the provided {\codefont JLink} library to create a connection with the underlying process {\codefont MathKernel}.
+The main class for communicating java code and {\codefont Mathematica} is {\codefont KernelLink} and the main used method was {\codefont evaluateToOutputForm(String expr, int pageWidth)} where {\codefont expr} is the expression to be evaluated and {\codefont pageWidth} affects the formatting of the result.
 
@@
 \subsubsection{Error handling}
-Sometimes, after certain time, the connection between \verb|KernelLink| and \verb|Mathematica| will be lost launch an exception and following invocations would fails as well.
-Also, re-instantiating a KernelLink will yield an Exception. For this scenario, killing the associated processes to Mathematica was necessary:
-
-\begin{verbatim}
-killall -s 9 Mathematica
-killall -s 9 MathKernel
-\end{verbatim}
-
-or
-
-\begin{verbatim}
-taskkill /im Mathematica.exe
-taskkill /im MathKernel.exe
-\end{verbatim}
-
-Depending on the OS the system is running on.
+Sometimes, after certain time, the connection between {\codefont KernelLink} and {\codefont Mathematica} will be lost launch an exception and following invocations would fails as well.
+Also, re-instantiating a KernelLink will yield an Exception.
+For this scenario, killing the associated processes to Mathematica was necessary with {\codefont killall -s 9 Mathematica; killall -s 9 MathKernel
+} or {\codefont taskkill /im Mathematica.exe; taskkill /im MathKernel.exe} depending on the OS the system is running on.
 
@@
 \end{verbatim}
-A human can easily identify that this corresponds to text and that should be inserted into a proper "mbox" or "text" tag. In this case, the snippet produced the following MathML code
-\begin{verbatim}
-<math><mrow><mi>φ</mi><mo></mo><mrow><mi>a</mi><mo></mo><mi>r</mi>   
-<mo></mo><mi>e</mi></mrow><mo></mo><mrow><mi>s</mi><mo></mo>
-<mi>h</mi><mo></mo><mi>o</mi><mo></mo><mi>w</mi><mo></mo><mi>n</mi>
-</mrow><mo>,</mo><mrow><mi>a</mi><mo></mo><mi>s</mi></mrow><mo></mo>
-<mrow><mi>w</mi><mo></mo><mi>e</mi><mo></mo><mi>l</mi><mo></mo>
-<mi>l</mi></mrow><mo></mo><mrow><mi>a</mi><mo></mo><mi>s</mi>
-</mrow><mo></mo><mrow><mi>t</mi><mo></mo><mi>h</mi><mo></mo>
-<mi>e</mi></mrow><mo></mo><mrow><mi>w</mi><mo></mo><mi>e</mi><mo>
-</mo><mi>i</mi><mo></mo><mi>g</mi><mo></mo><mi>h</mi><mo></mo>
-<mi>t</mi></mrow><mo></mo><mrow><mi>a</mi><mo></mo><mi>n</mi><mo>
-</mo><mi>d</mi></mrow><mo></mo><mrow><mi>t</mi><mo></mo><mi>e</mi>
-<mo></mo><mi>n</mi><mo></mo><mi>s</mi><mo></mo><mi>i</mi>
-<mo></mo><mi>o</mi><mo></mo><mi>n</mi></mrow></mrow></math>
-\end{verbatim}
+A human can easily identify that this corresponds to text and that should be inserted into a proper "mbox" or "text" tag. In this case, the snippet produced the following MathML code:
+\small{\codefont <math><mrow><mi>φ</mi><mo></mo><mrow><mi>a</mi><mo></mo>
+<mi>r</mi><mo></mo><mi>e</mi></mrow><mo></mo><mrow><mi>s
+</mi><mo></mo><mi>h</mi><mo></mo><mi>o</mi><mo></mo><mi>
+w</mi><mo></mo><mi>n</mi></mrow><mo>,</mo><mrow><mi>a</m
+i><mo></mo><mi>s</mi></mrow><mo></mo><mrow><mi>w</mi><mo
+></mo><mi>e</mi><mo></mo><mi>l</mi><mo></mo><mi>l</mi></
+mrow><mo></mo><mrow><mi>a</mi><mo></mo><mi>s</mi></mrow>
+<mo></mo><mrow><mi>t</mi><mo></mo><mi>h</mi><mo></mo><mi
+>e</mi></mrow><mo></mo><mrow><mi>w</mi><mo></mo><mi>e</m
+i><mo></mo><mi>i</mi><mo></mo><mi>g</mi><mo></mo><mi>h</
+mi><mo></mo><mi>t</mi></mrow><mo></mo><mrow><mi>a</mi><m
+o></mo><mi>n</mi><mo></mo><mi>d</mi></mrow><mo></mo><mro
+w><mi>t</mi><mo></mo><mi>e</mi><mo></mo><mi>n</mi><mo></
+mo><mi>s</mi><mo></mo><mi>i</mi><mo></mo><mi>o</mi><mo><
+/mo><mi>n</mi></mrow></mrow></math>
+}
 

### 2014-02-19 docs/thesis/chap-evaluation.tex
Added aditional equations to document added gradient operator group

@@
 
-\begin{longtable}{|m{1cm}|>
-{\centering\arraybackslash}m{3cm}|>
-{\centering\arraybackslash}m{5cm}|>
+\begin{longtable}{|m{0.75cm}|>
+{\centering\arraybackslash}m{2.7cm}|>
+{\centering\arraybackslash}m{6.5cm}|>
 {\centering\arraybackslash}m{5cm}|
@@
 \textbf{MathML code} &
-\textbf{Visual Rendering}
+\textbf{Visual Form}
 
@@
 \hline
-Eq1 & Time-independent Schr\char"00F6dinger equation & \scriptsize {\codefont <math><mfenced close=")" open="("> <mrow> <mo>-</mo> <mfrac> <msup> <mi>ℏ</mi> <mn>2</mn> </msup> <mrow> <mn>2</mn> <msub> <mi>m</mi> <mi>e</mi> </msub> </mrow> </mfrac> <msup> <mo>∇</mo> <mn>2</mn> </msup> <mo>+</mo> <mi>V</mi> <mfenced close=")" open="("> <mi>r</mi> </mfenced> </mrow> </mfenced> <mi>ψ</mi> <mfenced close=")" open="("> <mi>r</mi> </mfenced> <mo>==</mo> <mi>E</mi> <mi>ψ</mi> <mfenced close=")" open="("> <mi>r</mi> </mfenced> </math>} & $\left (-\frac{\hbar^{2}}{2m_e}\nabla^{2} + V(\mathbf{r})\right )\psi(\mathbf{r}) = E\psi(\mathbf{r})$ \\ \hline
+Eq1 & \scriptsize{ Time-independent Schr\char"00F6dinger equation} & \scriptsize {\codefont <math><mfenced close=")" open="("> <mrow> <mo>-</mo> <mfrac> <msup> <mi>ℏ</mi> <mn>2</mn> </msup> <mrow> <mn>2</mn> <msub> <mi>m</mi> <mi>e</mi> </msub> </mrow> </mfrac> <msup> <mo>$\nabla$</mo> <mn>2</mn> </msup> <mo>+</mo> <mi>V</mi> <mfenced close=")" open="("> <mi>r</mi> </mfenced> </mrow> </mfenced> <mi>ψ</mi> <mfenced close=")" open="("> <mi>r</mi> </mfenced> <mo>=</mo> <mi>E</mi> <mi>ψ</mi> <mfenced close=")" open="("> <mi>r</mi> </mfenced> </math>} & \scriptsize{ $\left (-\frac{\hbar^{2}}{2m_e}\nabla^{2} + V(\mathbf{r})\right )\psi(\mathbf{r}) = E\psi(\mathbf{r})$ }\\ \hline
 
-\caption{Software used during evaluations}
+Eq2 & \scriptsize{Atomic mass in terms of number of proton and number of neutrons} & \scriptsize {\codefont <math> <mi>A</mi> <mo>=</mo> <mi>Z</mi> <mo>+</mo> <mi>N</mi> </math>} & \scriptsize{$A = Z + N$} \\ \hline
+
+Eq3 & \scriptsize{Radiation flux in term of the initial intensity, the absorption coefficient and the thickness of a substance} & \scriptsize {\codefont <math> <mi>I</mi> <mo>=</mo> <msub> <mi>I</mi> <mn>0</mn> </msub><msup> <mi>e</mi> <mrow> <mo>-</mo> <mi>μ</mi> <mi>x</mi> </mrow> </msup> </math>
+} & \scriptsize{$I = I_0e^{-\mu x}$ } \\ \hline
+
+Eq4 & \scriptsize{Higgs Boson decaying process into $W^+$ and $W^-$ bosons.
+This is not exactly a mathematical equation, but a physical process.
+However it is also expressed in LaTeX and to high energy physics experts, it makes sense to search them.} & \scriptsize {\codefont <math> <mi>H</mi> <mo>→</mo> <msup> <mi>W</mi> <mo>+</mo> </msup> <msup> <mi>W</mi> <mo>-</mo> </msup> </math>} & \scriptsize{$H\rightarrow W^+W^-$ } \\ \hline
+
+Eq5 & \scriptsize{Electron effective mass in solid state physics} & \scriptsize {\codefont <math > <msup> <msup> <mi>m</mi> <mo>*</mo> </msup> <mn>-1</mn> </msup> <mo>==</mo> <mfrac> <mn>1</mn> <msup> <mi>ℏ</mi> <mn>2</mn> </msup> </mfrac> <msub> <mo>$\nabla$</mo> <mi>k</mi> </msub> <msub> <mo>$\nabla$</mo> <mi>k</mi> </msub> <mi>E</mi> </math>
+ } & \scriptsize{${m^*}^{-1} = \frac{1}{\hbar^{2}} \nabla_k \nabla_k E$ } \\ \hline
+
+Eq6 & \scriptsize{Fermi Energy} & \scriptsize {\codefont <math> <msub> <mi>E</mi> <mi>F</mi> </msub> <mo>=</mo> <mfrac> <mrow> <msub> <mi>E</mi> <mi>C</mi> </msub> <mo>+</mo> <msub> <mi>E</mi> <mi>V</mi> </msub> </mrow> <mn>2</mn> </mfrac> <mo>+</mo> <mfrac> <mrow> <msub> <mi>κ</mi> <mi>B</mi> </msub> <mi>T</mi> </mrow> <mn>2</mn> </mfrac> <mi>ln</mi> <mfenced close=")" open="("> <mfrac> <msub> <mi>N</mi> <mi>V</mi> </msub> <msub> <mi>N</mi> <mi>C</mi> </msub> </mfrac> </mfenced> </math>} & \scriptsize{$E_F = \frac{E_C + E_V}{2} + \frac{\kappa_{B}T}{2} \ln \left(\frac{N_V}{N_C}\right)$ } \\ \hline
+
+\caption{Sample equations used during testing}
 \label{equations_table}
 \end{longtable}
+
+\section{Comparison against other systems}
+In this section we tried to compare our implementation of MASE(CDS) with the public available systems presented in the related work chapter.
+We judged if the fetched results of each system were relevant or not using the same criteria as for the previous section.
+The systems were tested using Firefox 26.0
+Table \ref{comparison_sw_table} presents the results of our test.
+
+\begin{figure}
+\includegraphics[height=15 cm]{figures/comparison_table.png}
+\label{comparison_sw_table}
+\caption{Results of comparison of available mathematical search systems}
+\end{figure}
+
+The results are a little disappointing since from the eight evaluated instances, only MIaS and Symbolab seem to be working properly.
 

### 2014-02-19 src/cern/ch/mathexplorer/lucene/query/MathQueryParser.java

@@ -142,7 +142,8 @@ public class MathQueryParser extends QParser {
 	}
 
 	public static void main(String[] args) throws Exception {
-		String query = Regex.cleanQuery(texToMathML("\\left (-\\frac{\\hbar^{2}}{2m_e}\\nabla^{2} + V(\\mathbf{r})\\right )\\psi(\\mathbf{r}) = E\\psi(\\mathbf{r})"));
+		String query = Regex.cleanQuery(texToMathML(""
+				+ "$E_F = \\frac{E_C + E_V}{2} + \\frac{\\kappa_{B}T}{2} \\ln \\left(\\frac{N_V}{N_C}\\right)$"));
 		MathQueryParser mqp = new MathQueryParser(query, null, null, null);
 		mqp.parse();
 	}

### 2014-02-19 src/cern/ch/mathexplorer/utils/Constants.java

@@ -200,7 +200,12 @@ public final class Constants implements Serializable {
 				"✕",
 				"✖",
 				"·")))
-		, ARROWS(new HashSet<>(Arrays.asList("←" //
+		,
+		GRADIENT(new HashSet<>(Arrays.asList(
+				"▽",		//WHITE DOWN-POINTING TRIANGLE
+				"∇")))		//NABLA
+		,
+		ARROWS(new HashSet<>(Arrays.asList("←" //
 				, "→" //
 				, "↑" //
 				, "↓" //

### 2014-02-19 docs/thesis/appendix-conf_files.tex
.

\chapter{Configuration files}

\section{Solr Schema}
The Solr schema file \verb|schema.xml| indicates which are the fields that are going to be used in this instance, and what type of analyzer is going to be used for each one. One can also define field types in case different fields want to have the same behaviour but conceptually having different meanings.

The following snippet add the fields declarations:

\begin{verbatim}
   <!-- Arthur Oviedo AO-->
   <!-- Fields declaration using the field types declared below-->
   <field name="math_notational_field" 
   		type="math_notational_type"/>
   <field name="math_structural_field" 
   		type="math_structural_type"/>
   <field name="math_normalized_notational_field" 
   		type="math_normalized_notational_type"/>
   <field name="math_full_normalized_notational_field" 
   		type="math_full_normalized_notational_type"/>
   <field name="filename" 
   		type="string" indexed="true" stored="true"/>
   <field name="number_occurences" 
   		type="int" indexed="true" stored="true"/>
\end{verbatim}

And the following one, defines the types and the configurations (Including the java class implementing the analyzer) for each one:

\begin{verbatim}
	<fieldType name="math_normalized_notational_type" 
		class="solr.TextField" 
		positionIncrementGap="1"
		indexed="true" 
		stored="true" 
		termVectors="true" 
		termPositions="true" >
		<analyzer class="cern.ch.mathexplorer.lucene.analysis.analyzers.
			SolrNormalizerNotationalAnalyzer"/>
	</fieldType>

	<!-- Field type for MathMl info 
	(Tokens that are extracted from the MathML representation)
	over the normalized/simplified string using Full simplification-->
	<fieldType name="math_full_normalized_notational_type" 
		class="solr.TextField" 
		positionIncrementGap="1"
		indexed="true" 
		stored="true" 
		termVectors="true" 
		termPositions="true" >
		<analyzer class="cern.ch.mathexplorer.lucene.analysis.analyzers.
			SolrFullNormalizerNotationalAnalyzer"/>
	</fieldType>

	<!-- Field type for  structural features extracted from the equation-->
	<fieldType name="math_structural_type" 
		class="solr.TextField" 
		positionIncrementGap="1"
		indexed="true" 
		stored="true" 
		termVectors="true" 
		termPositions="true" >
		<analyzer class="cern.ch.mathexplorer.lucene.analysis.analyzers.
			SolrStructuralAnalyzer"/>
	</fieldType>

\end{verbatim}

\section{Solr configuration file}
The \verb|solrconfig.xml| file specifies additional configuration parameters of the instance, including what handlers to use for each different type of request. One specific type of handler is \verb|queryParser|, and for using our specific query parser we include the following line of code:

\begin{verbatim}
  <queryParser name="mathqueryparser" 
  class="cern.ch.mathexplorer.lucene.query.MathQueryParserPlugin" />
\end{verbatim}

### 2014-02-19 src/cern/ch/mathexplorer/lucene/query/MathQueryParser.java

@@ -142,8 +142,7 @@ public class MathQueryParser extends QParser {
 	}
 
 	public static void main(String[] args) throws Exception {
-		String query = Regex.cleanQuery(texToMathML(""
-				+ "$E_F = \\frac{E_C + E_V}{2} + \\frac{\\kappa_{B}T}{2} \\ln \\left(\\frac{N_V}{N_C}\\right)$"));
+		String query = Regex.cleanQuery(texToMathML("\\left (-\\frac{\\hbar^{2}}{2m_e}\\nabla^{2} + V(\\mathbf{r})\\right )\\psi(\\mathbf{r}) = E\\psi(\\mathbf{r})"));
 		MathQueryParser mqp = new MathQueryParser(query, null, null, null);
 		mqp.parse();
 	}

### 2014-02-19 src/cern/ch/mathexplorer/utils/Constants.java

@@ -200,12 +200,7 @@ public final class Constants implements Serializable {
 				"✕",
 				"✖",
 				"·")))
-		,
-		GRADIENT(new HashSet<>(Arrays.asList(
-				"▽",		//WHITE DOWN-POINTING TRIANGLE
-				"∇")))		//NABLA
-		,
-		ARROWS(new HashSet<>(Arrays.asList("←" //
+		, ARROWS(new HashSet<>(Arrays.asList("←" //
 				, "→" //
 				, "↑" //
 				, "↓" //

### 2014-02-19 src/cern/ch/mathexplorer/lucene/analysis/analyzers/SolrFullNormalizerNotationalAnalyzer.java
.

@@ -1,0 +1,42 @@
+package cern.ch.mathexplorer.lucene.analysis.analyzers;
+import java.io.Reader;
+
+import org.apache.lucene.analysis.TokenStream;
+import org.apache.lucene.analysis.Tokenizer;
+import org.apache.lucene.util.Version;
+import org.apache.solr.analysis.SolrAnalyzer;
+
+import cern.ch.mathexplorer.lucene.analysis.filters.NumericalRoundingFilter;
+import cern.ch.mathexplorer.lucene.analysis.filters.SynonymExpandingFilter;
+import cern.ch.mathexplorer.lucene.analysis.filters.UnicodeNormalizingFilter;
+import cern.ch.mathexplorer.lucene.analysis.tokenizers.MultiplePatternTokenizer;
+import cern.ch.mathexplorer.mathematica.MathematicaConfig;
+import cern.ch.mathexplorer.utils.Regex;
+
+public final class SolrFullNormalizerNotationalAnalyzer extends SolrAnalyzer {
+  
+  private final Version matchVersion;
+  
+  /**
+   * Creates a new {@link SolrFullNormalizerNotationalAnalyzer}
+   * @param matchVersion Lucene version to match See {@link <a href="#version">above</a>}
+   * Provides the same functionality as {@link SolrNotationalAnalyzer}
+   * but over a normalized/simplified version of the original string 
+   */
+  public SolrFullNormalizerNotationalAnalyzer(Version matchVersion) {
+    this.matchVersion = matchVersion;
+  }
+  
+  @Override
+  protected TokenStreamComponents createComponents(final String fieldName,
+      final Reader reader) {
+	  Tokenizer source2 = new MultiplePatternTokenizer(reader, Regex.PATTERNS, Regex.GROUP,
+			  MathematicaConfig.NORMALIZATION_MODES.FULL_SIMPLIFICATION);
+	  TokenStream unicodeNormalizer = new UnicodeNormalizingFilter(source2);
+	  TokenStream numericRounder 	= new NumericalRoundingFilter(unicodeNormalizer);
+	  TokenStream relatedOperators 	= new SynonymExpandingFilter(numericRounder);
+	  
+	  
+	  return new TokenStreamComponents(source2, relatedOperators);
+  }
+}

### 2014-02-19 src/cern/ch/mathexplorer/lucene/query/MathQueryParser.java

@@ -111,7 +111,7 @@ public class MathQueryParser extends QParser {
 		addNotationalTokens(query, qstr, MATH_FIELD.MATH_NOTATIONAL_FIELD);
 		if (MathematicaConfig.USE_MATHEMATICA) {
 			String normalizedStr = MathematicaEngine.getInstance("QUERY")
-					.simplyExpressionWithTimeout(qstr);
+					.simplifyExpressionWithTimeout(qstr);
 			addStructuralPatterns(query, qstr);
 			addNotationalTokens(query, normalizedStr, MATH_FIELD.MATH_NORMALIZED_NOTATIONAL_FIELD);
 		}

### 2014-02-19 src/cern/ch/mathexplorer/mathematica/MathematicaEngine.java

@@ -149,11 +149,11 @@ public class MathematicaEngine {
 	
 	}
 
-	public String simplyExpressionWithTimeout(String mathMLExpression){
+	public String simplifyExpressionWithTimeout(String mathMLExpression){
 		if (MathematicaConfig.NORMALIZATION_MODE.equals(MathematicaConfig.NORMALIZATION_MODES.FULL_SIMPLIFICATION)) {
-			return simplyExpressionWithTimeout(mathMLExpression, true);
+			return simplifyExpressionWithTimeout(mathMLExpression, true);
 		} else {
-			return simplyExpressionWithTimeout(mathMLExpression, false);
+			return simplifyExpressionWithTimeout(mathMLExpression, false);
 		}
 	}
 
@@ -162,7 +162,7 @@ public class MathematicaEngine {
 	 * Calls the method for simplifyin a given string.
 	 * If the method takes more than the defined timeout, the original string is returned 
 	 */
-	public String simplyExpressionWithTimeout(String mathMLExpression, boolean full){
+	public String simplifyExpressionWithTimeout(String mathMLExpression, boolean full){
 		ExecutorService executor = Executors.newSingleThreadExecutor();
         Future future = executor.submit(new MathematicaTask(mathMLExpression, TASK.SIMPLIFY_EXPRESSION, full));
         try {
@@ -373,7 +373,7 @@ public class MathematicaEngine {
 		MathematicaEngine instance = getInstance("TESTING");
 		int count = 0;
 		while ((line = br.readLine()) != null) {
-			instance.simplyExpressionWithTimeout(line);
+			instance.simplifyExpressionWithTimeout(line);
 			instance.getPatternsWithTimeout(line);
 			//instance.getPatterns(line);
 			//instance.simplifyExpression(line, true);

### 2014-02-19 src/cern/ch/mathexplorer/lucene/analysis/tokenizers/MathTokenizer.java
fixed bug with renaming of simplify method

@@ -38,10 +38,10 @@ public abstract class MathTokenizer extends Tokenizer {
 			
 		}
 		if (normalizationMode.equals(MathematicaConfig.NORMALIZATION_MODES.STANDARD_SIMPLIFICATION)){
-			tmp = MathematicaEngine.getInstance("INDEXING").simplyExpressionWithTimeout(tmp, false);
+			tmp = MathematicaEngine.getInstance("INDEXING").simplifyExpressionWithTimeout(tmp, false);
 		}
 		if (normalizationMode.equals(MathematicaConfig.NORMALIZATION_MODES.FULL_SIMPLIFICATION)){
-			tmp = MathematicaEngine.getInstance("INDEXING").simplyExpressionWithTimeout(tmp, true);
+			tmp = MathematicaEngine.getInstance("INDEXING").simplifyExpressionWithTimeout(tmp, true);
 		}
 		str = new StringBuilder(Regex.cleanQuery(tmp));
 

### 2014-02-19 src/cern/ch/mathexplorer/lucene/query/MathQueryParser.java
added gradient synonyms

@@ -40,45 +40,46 @@ public class MathQueryParser extends QParser {
 
 	private static SnuggleEngine engine = new SnuggleEngine();
 
-	public void addNotationalTokens(BooleanQuery query, String mathML, MATH_FIELD field) {
+	public void addNotationalTokens(BooleanQuery query, String mathML,
+			MATH_FIELD field) {
 		Collection<String> tokenInQuery = Regex.extractElements(mathML);
 		for (String mathMLToken : tokenInQuery) {
-			query.add(new BooleanClause(new TermQuery(new Term(
-					field.getName(), mathMLToken)),
-					Occur.SHOULD));
+			query.add(new BooleanClause(new TermQuery(new Term(field.getName(),
+					mathMLToken)), Occur.SHOULD));
 			addSynonyms(mathMLToken, query, field);
 			Console.print(mathMLToken);
 		}
 	}
 
 	void addSynonyms(String mathMLToken, BooleanQuery query, MATH_FIELD field) {
-		if (mathMLToken.startsWith("<mo>") && mathMLToken.endsWith("</mo>")) { // OPERATOR CATEGORY TOKEN
-			String operator = mathMLToken.replace("<mo>", "").replace("</mo>", "");
+		if (mathMLToken.startsWith("<mo>") && mathMLToken.endsWith("</mo>")) { // OPERATOR
+																				// CATEGORY
+																				// TOKEN
+			String operator = mathMLToken.replace("<mo>", "").replace("</mo>",
+					"");
 			CHARACTER_CATEGORIES category = null;
 			if ((category = (Constants.CHARACTERS_TO_CATEGORY.get(operator))) != null) {
-				query.add(new BooleanClause(new TermQuery(new Term(
-						field.getName(), category.name())),
-						Occur.SHOULD));
+				query.add(new BooleanClause(new TermQuery(new Term(field
+						.getName(), category.name())), Occur.SHOULD));
 			}
 		}
 	}
 
-	void addStructuralPatterns(BooleanQuery query, String mathML){
+	void addStructuralPatterns(BooleanQuery query, String mathML) {
 		List<StructuralPattern> patterns = new ArrayList<>();
 		try {
 			patterns = MathematicaEngine.getInstance("QUERY")
 					.getPatternsWithTimeout(mathML);
[…]

### 2014-02-19 src/cern/ch/mathexplorer/utils/Constants.java

@@ -192,7 +192,16 @@ public final class Constants implements Serializable {
 				, "\u2A1B" // Integral with overbar
 				, "\u2A14" // Line integration not including pole
 				, "\u2A1C" // Integral with underbar
-		))), 
+		))),
+		GRADIENT(new HashSet<>(Arrays.asList(
+				"∇",	//NABLA	
+				"▽"	//WHITE DOWN POINTING TRIANGLE
+				))),
+		EQUALS(new HashSet<>(Arrays.asList(
+				"=",	
+				"==",
+				"≡"
+				))),
 		MULTIPLICATION(new HashSet<>(Arrays.asList(
 				"\u2062",	//Invisible times
 				//"*",		Needs to be considered in context

### 2014-02-19 docs/thesis/chap-evaluation.tex
added 5th equation

@@
 
-Eq5 & \scriptsize{Electron effective mass in solid state physics} & \scriptsize {\codefont <math > <msup> <msup> <mi>m</mi> <mo>*</mo> </msup> <mn>-1</mn> </msup> <mo>==</mo> <mfrac> <mn>1</mn> <msup> <mi>ℏ</mi> <mn>2</mn> </msup> </mfrac> <msub> <mo>$\nabla$</mo> <mi>k</mi> </msub> <msub> <mo>$\nabla$</mo> <mi>k</mi> </msub> <mi>E</mi> </math>
- } & \scriptsize{${m^*}^{-1} = \frac{1}{\hbar^{2}} \nabla_k \nabla_k E$ } \\ \hline
+Eq5 & \scriptsize{Einstein Field equation} & \scriptsize {\codefont <math><msub><mi>G</mi><mrow><mi>μ</mi><mi>ν</mi></mrow></msub><mo>=</mo><msub><mi>R</mi><mrow><mi>μ</mi><mi>ν</mi></mrow></msub><mo>-</mo><mfrac><mn>1</mn><mn>2</mn></mfrac><mi>R</mi><msub><mi>g</mi><mrow><mi>μ</mi><mi>ν</mi></mrow></msub><mo>=</mo><mfrac><mrow><mn>8</mn><mi>π</mi><mi>G</mi></mrow><msup><mi>c</mi><mn>4</mn></msup></mfrac><msub><mi>T</mi><mrow><mi>μ</mi><mi>ν</mi></mrow></msub></math>
+ </math>
+ } & \scriptsize{$G_{\mu\nu}\equiv R_{\mu\nu} - {\textstyle 1 \over 2}R\,g_{\mu\nu} = {8 \pi G \over c^4} T_{\mu\nu}$ } \\ \hline
 

### 2014-02-19 src/cern/ch/mathexplorer/lucene/query/MathQueryParser.java

@@ -169,7 +169,7 @@ public class MathQueryParser extends QParser {
 
 	public static void main(String[] args) throws Exception {
 		String query = Regex
-				.cleanQuery(texToMathML("\\left (-\\frac{\\hbar^{2}}{2m_e}\\nabla^{2} + V(\\mathbf{r})\\right )\\psi(\\mathbf{r}) = E\\psi(\\mathbf{r})"));
+				.cleanQuery(texToMathML("G_{\\mu\\nu}\\equiv R_{\\mu\\nu} - {\\textstyle 1 \\over 2}R\\,g_{\\mu\\nu} = {8 \\pi G \\over c^4} T_{\\mu\\nu}"));
 		MathQueryParser mqp = new MathQueryParser(query, null, null, null);
 		mqp.parse();
 	}

### 2014-02-19 src/cern/ch/mathexplorer/utils/Regex.java

@@ -81,6 +81,8 @@ public class Regex {
 		queryString = queryString.replaceAll("</mspace>", "");
 		queryString = queryString.replaceAll("<mo>.</mo></math>", "</math>");
 		queryString = queryString.replaceAll("<mo>,</mo></math>", "</math>");
+		queryString = queryString.replaceAll("> <", "><");
+
 		
 		//queryString = queryString.replaceAll("&theta;", "θ");
 		queryString = StringEscapeUtils.unescapeHtml4(queryString);

### 2014-02-19 docs/thesis/chap-evaluation.tex
added sample equations, indexing tests and quality of results

--- 2014-02-19 docs/thesis/chap-evaluation.tex
@@
 
-Eq5 & \scriptsize{Electron effective mass in solid state physics} & \scriptsize {\codefont <math > <msup> <msup> <mi>m</mi> <mo>*</mo> </msup> <mn>-1</mn> </msup> <mo>==</mo> <mfrac> <mn>1</mn> <msup> <mi>ℏ</mi> <mn>2</mn> </msup> </mfrac> <msub> <mo>$\nabla$</mo> <mi>k</mi> </msub> <msub> <mo>$\nabla$</mo> <mi>k</mi> </msub> <mi>E</mi> </math>
- } & \scriptsize{${m^*}^{-1} = \frac{1}{\hbar^{2}} \nabla_k \nabla_k E$ } \\ \hline
+Eq5 & \scriptsize{Einstein Field equation} & \scriptsize {\codefont <math> <msub> <mi>G</mi> <mrow> <mi>μ</mi> <mi>ν</mi> </mrow> </msub> <mo>=</mo> <msub> <mi>R</mi> <mrow> <mi>μ</mi> <mi>ν</mi> </mrow> </msub> <mo>-</mo> <mfrac> <mn>1</mn> <mn>2</mn> </mfrac> <mi>R</mi> <msub> <mi>g</mi> <mrow> <mi>μ</mi> <mi>ν</mi> </mrow> </msub> <mo>=</mo> <mfrac> <mrow> <mn>8</mn> <mi>π</mi> <mi>G</mi> </mrow> <msup> <mi>c</mi> <mn>4</mn> </msup> </mfrac> <msub> <mi>T</mi> <mrow> <mi>μ</mi> <mi>ν</mi> </mrow> </msub> </math>
+ </math>
+ } & \scriptsize{$G_{\mu\nu}\equiv R_{\mu\nu} - {\textstyle 1 \over 2}R\,g_{\mu\nu} = {8 \pi G \over c^4} T_{\mu\nu}$ } \\ \hline
 

### 2014-02-20 docs/thesis/chap-cern_math_explorer.tex
small additions to the document

@@
-\chapter{MASE(CDS)}
+\chapter{$5e^{x+y}$(CDS)}
 \label{chapter-cern_math_explorer}
-In this chapter we present our solution called MASE(CDS), Math Aware Search Engine (For CDS). We present the key points of our system, and how they are related to previous built systems.
+In this chapter we present our solution called $5e^{x+y}$(CDS). We present the key points of our system, and how they are related to previous built systems.
 
@@
 Our system was developed on top of the  the Apache Solr/Lucene framework.
-CDS already uses Solr as a search engine layer, so developing MASE using this technology supposed a reasonable choice.
+CDS already uses Solr as a search engine layer, so developing $5e^{x+y}$(CDS) using this technology supposed a reasonable choice.
 One of the main steps while building an IR tool, is understanding the data and what kind of features can be extracted from it: If the system is based on text, then tasks as stemming, handling of synonyms, misspelling and so on, such be taken into consideration; if the system being developed is based on images, then examples of features can be histograms of colors, geometrical features and so on.
@@
 
-\subsubsection{Non-formal mathematical variations}
+\subsubsection{Subscript/Superscript variations}
 This set of structures represent common operations that cat appear in a given expression, but its identification is based on notation factors.
@@
 We would like to assign a partial match to any other kind of this decomposition say $B = MRM^{-1}$.
-these types of structures live in-between the notational and structural categories but, as it will be discussed, we identify them using Mathematica and encompass them as structural features.
+these types of structures live in-between the notational and structural categories but since we identify them using Mathematica, we encompass them as structural features.
+For this type of structures, we identify simple operations between an element and some possible variations of the same element with some subscript/superscript.
 
@@
 Additionally, we identified patterns that are relevant and frequent in specific domains of the high energy physics.
+Some patterns can be as general as a derivative over time ($dx/dt$), or more specific ones like a particle decaying process ($originalParticle \rightarrow subparticle1, subparticle2, subparticle3$).
 

### 2014-02-20 docs/thesis/chap-evaluation.tex
small additions to the document

--- 2014-02-19 docs/thesis/chap-evaluation.tex
@@
 Table \ref{equations_table} presents the set of queries that were evaluated, and a simple explanation about it.
-
-\begin{longtable}{|m{0.75cm}|>
-{\centering\arraybackslash}m{2.7cm}|>
-{\centering\arraybackslash}m{6.5cm}|>
-{\centering\arraybackslash}m{5cm}|
-}
-\hline 
-\textbf{Id} & 
-\textbf{Description} &
-\textbf{MathML code} &
-\textbf{Visual Form}
-
-\\
-\hline
-Eq1 & \scriptsize{ Time-independent Schr\char"00F6dinger equation} & \scriptsize {\codefont <math><mfenced close=")" open="("> <mrow> <mo>-</mo> <mfrac> <msup> <mi>ℏ</mi> <mn>2</mn> </msup> <mrow> <mn>2</mn> <msub> <mi>m</mi> <mi>e</mi> </msub> </mrow> </mfrac> <msup> <mo>$\nabla$</mo> <mn>2</mn> </msup> <mo>+</mo> <mi>V</mi> <mfenced close=")" open="("> <mi>r</mi> </mfenced> </mrow> </mfenced> <mi>ψ</mi> <mfenced close=")" open="("> <mi>r</mi> </mfenced> <mo>=</mo> <mi>E</mi> <mi>ψ</mi> <mfenced close=")" open="("> <mi>r</mi> </mfenced> </math>} & \scriptsize{ $\left (-\frac{\hbar^{2}}{2m_e}\nabla^{2} + V(\mathbf{r})\right )\psi(\mathbf{r}) = E\psi(\mathbf{r})$ }\\ \hline
-
-Eq2 & \scriptsize{Atomic mass in terms of number of proton and number of neutrons} & \scriptsize {\codefont <math> <mi>A</mi> <mo>=</mo> <mi>Z</mi> <mo>+</mo> <mi>N</mi> </math>} & \scriptsize{$A = Z + N$} \\ \hline
-
-Eq3 & \scriptsize{Radiation flux in term of the initial intensity, the absorption coefficient and the thickness of a substance} & \scriptsize {\codefont <math> <mi>I</mi> <mo>=</mo> <msub> <mi>I</mi> <mn>0</mn> </msub><msup> <mi>e</mi> <mrow> <mo>-</mo> <mi>μ</mi> <mi>x</mi> </mrow> </msup> </math>
-} & \scriptsize{$I = I_0e^{-\mu x}$ } \\ \hline
-
-Eq4 & \scriptsize{Higgs Boson decaying process into $W^+$ and $W^-$ bosons.
-This is not exactly a mathematical equation, but a physical process.
-However it is also expressed in LaTeX and to high energy physics experts, it makes sense to search them.} & \scriptsize {\codefont <math> <mi>H</mi> <mo>→</mo> <msup> <mi>W</mi> <mo>+</mo> </msup> <msup> <mi>W</mi> <mo>-</mo> </msup> </math>} & \scriptsize{$H\rightarrow W^+W^-$ } \\ \hline
-
-Eq5 & \scriptsize{Electron effective mass in solid state physics} & \scriptsize {\codefont <math > <msup> <msup> <mi>m</mi> <mo>*</mo> </msup> <mn>-1</mn> </msup> <mo>==</mo> <mfrac> <mn>1</mn> <msup> <mi>ℏ</mi> <mn>2</mn> </msup> </mfrac> <msub> <mo>$\nabla$</mo> <mi>k</mi> </msub> <msub> <mo>$\nabla$</mo> <mi>k</mi> </msub> <mi>E</mi> </math>
- } & \scriptsize{${m^*}^{-1} = \frac{1}{\hbar^{2}} \nabla_k \nabla_k E$ } \\ \hline
-
-Eq6 & \scriptsize{Fermi Energy} & \scriptsize {\codefont <math> <msub> <mi>E</mi> <mi>F</mi> </msub> <mo>=</mo> <mfrac> <mrow> <msub> <mi>E</mi> <mi>C</mi> </msub> <mo>+</mo> <msub> <mi>E</mi> <mi>V</mi> </msub> </mrow> <mn>2</mn> </mfrac> <mo>+</mo> <mfrac> <mrow> <msub> <mi>κ</mi> <mi>B</mi> </msub> <mi>T</mi> </mrow> <mn>2</mn> </mfrac> <mi>ln</mi> <mfenced close=")" open="("> <mfrac> <msub> <mi>N</mi> <mi>V</mi> </msub> <msub> <mi>N</mi> <mi>C</mi> </msub> </mfrac> </mfenced> </math>} & \scriptsize{$E_F = \frac{E_C + E_V}{2} + \frac{\kappa_{B}T}{2} \ln \left(\frac{N_V}{N_C}\right)$ } \\ \hline
-
-\caption{Sample equations used during testing}
-\label{equations_table}
-\end{longtable}
 

### 2014-02-20 docs/thesis/chap-introduction.tex
small additions to the document

\chapter{Introduction}

\section{CERN Document Server}

\section{Invenio}

### 2014-02-20 docs/thesis/chap-evaluation.tex
added again literature

@@
 In this section we are interested in evaluating the quality of the results provided by our system.
-The type of queries that MASE was designed for, are typical equations that can be found in a scientific publication. 
+The type of queries that $5e^{x+y}$ was designed for, are typical equations that can be found in a physics scientific publication. 
 Out main user case is that a user of CDS is interested in finding documents inside the collection whose equations are related to the one that is provided.
@@
 Table \ref{equations_table} presents the set of queries that were evaluated, and a simple explanation about it. 
+Each of the users evaluated the results only for the equations he/she provided.
+For each of the presented result, the user ranked it as "Completely Relevant", "Partially Relevant" and "Completely Irrelevant".
+As all evaluations including human interaction, this scoring is at some level subjective.
+
+We present results for three metrics: Partial precision (Document either partially relevant or completely relevant) $P_{partial} = \frac{|Partially Relevant Results \cup Strictly Relevant Results | }{K}$, $P_{strict} = \frac{Strictly Relevant Results | }{K}$ and discounted cumulative gain.
 

### 2014-02-20 docs/thesis/chap-theoretical_background.tex
small additions to the document
added again literature

@@
 The scoring of a document for a given query is computed as the cosine of the angle between both vectors which can be expressed as: 
-$$score(d, q) = cos\theta = \frac{d \cdot q}{\parallel d \parallel \parallel q \parallel}  = \frac{\sum_{i=1}^{n}weight(d_i, d)*weight(q_i, q)}{\sqrt{\sum_{i=1}^{n}weight^2(d_i, d)}\sqrt{\sum_{i=1}^{n}weight^2(q_i, q)}} $$
+$$score(d, q) = cos\theta(d, q) = \frac{d \cdot q}{\parallel d \parallel \parallel q \parallel}  = \frac{\sum_{i=1}^{n}weight(d_i, d)*weight(q_i, q)}{\sqrt{\sum_{i=1}^{n}weight^2(d_i, d)}\sqrt{\sum_{i=1}^{n}weight^2(q_i, q)}} $$
 
@@
 
+\section{Latent Semantic Indexing}
+
 \section{Tree Edit Distance}

### 2014-02-20 src/cern/ch/mathexplorer/mathematica/Patterns.java

@@ -123,6 +123,8 @@ public class Patterns {
 				String.format("Superscript[X_,%s]",secondArg), 
 				String.format("Superscript[X_,%s]",secondArg),
 				String.format("Power[X_,%s]",secondArg),
+				String.format("Overscript[X_, %s]",secondArg), 
+				String.format("Underscript[X_,%s]",secondArg));
 				//"SubPlus[X_]", 
 				//"SubMinus[X_]", 
 				//"SubStar[X_]", 
@@ -130,8 +132,6 @@ public class Patterns {
 				//"SuperMinus[X_]", 
 				//"SuperStar[X_]", 
 				//"SuperDagger[X_]", 
-				String.format("Overscript[X_, %s]",secondArg), 
-				String.format("Underscript[X_,%s]",secondArg));
 				//"OverBar[X_]", 
 				//"OverVector[X_]", 
 				//"OverHat[X_]", 

### 2014-02-20 docs/thesis/chap-technical_considerations.tex
started to work on math representation section

@@
 \section{Digital Representations of Mathematics}
-\subsection{MathML}
-\subsection{OpenMath}
-\subsection{LaTeX}
+When building any kind of information retrieval system, selecting the right representations of the data can affect the type of algorithms that one can use, the amount of storage, the quality of the data among other factors.
+Mathematical content is not an exception, and there are available different formats to encode a mathematical expression.
+One of the most common ways to represent mathematics in scientific documents, which suits CDS's domain, is \LaTeX.
+Another  important standard for the representation of mathematics is MathML, which was first proposed by the World Wide Web Consortium in 1998 as the recommended language to be used in web documents.
+One of the advantages of MathML over LaTeX, is the fact that it is an application of XML, which makes it very easy process algorithmically.
+There two different variations of MathML, presentation and content.
+The first one is oriented to the visual representation of the expression and the second one is more oriented to the semantics of the expression.
+OpenMath is another markup language to represent mathematics and can be used to compliment presentation MathML to add more semantic information.
+
+Table \ref{math_languages} presents a comparison on how different languages can express the expression $x^2 + y^2 = z^2$
+
+\begin{longtable}{|m{3.5cm}|>
+{\centering\arraybackslash}m{3cm}|>
+{\centering\arraybackslash}m{3cm}|>
+{\centering\arraybackslash}m{3cm}|
+}
+\hline 
+\textbf{\LaTeX} & 
+\textbf{Presentation MathML} & 
+\textbf{Content MathML} & 
+\textbf{OpenMath}  \\ \hline
+
+\verb|$x^2 + y^2 = z^2$|&&&
+\\
+\hline
+
+\caption{Comparison of the different languages for expressing mathematical content} 
+\label{math_languages}
+\end{longtable}
+
+Because
 

### 2014-02-21 docs/thesis/appendix-conf_files.tex
work on document: added graphics

@@
    		type="math_normalized_notational_type"/>
-   <field name="math_full_normalized_notational_field" 
-   		type="math_full_normalized_notational_type"/>
    <field name="filename" 
    		type="string" indexed="true" stored="true"/>
-   <field name="number_occurences" 
+   <field name="number_occurrences" 
    		type="int" indexed="true" stored="true"/>

### 2014-02-21 docs/thesis/appendix-system_design.tex
work on document: added graphics

\chapter{Test equations}

\begin{longtable}{|m{0.75cm}|>
{\centering\arraybackslash}m{2.7cm}|>
{\centering\arraybackslash}m{6.5cm}|>
{\centering\arraybackslash}m{5cm}|
}
\hline 
\textbf{Id} & 
\textbf{Description} &
\textbf{MathML code} &
\textbf{Visual Form}

\\
\hline
Eq1 & \scriptsize{ Time-independent Schr\char"00F6dinger equation} & \scriptsize {\codefont <math><mfenced close=")" open="("> <mrow> <mo>-</mo> <mfrac> <msup> <mi>ℏ</mi> <mn>2</mn> </msup> <mrow> <mn>2</mn> <msub> <mi>m</mi> <mi>e</mi> </msub> </mrow> </mfrac> <msup> <mo>$\nabla$</mo> <mn>2</mn> </msup> <mo>+</mo> <mi>V</mi> <mfenced close=")" open="("> <mi>r</mi> </mfenced> </mrow> </mfenced> <mi>ψ</mi> <mfenced close=")" open="("> <mi>r</mi> </mfenced> <mo>=</mo> <mi>E</mi> <mi>ψ</mi> <mfenced close=")" open="("> <mi>r</mi> </mfenced> </math>} & \scriptsize{ $\left (-\frac{\hbar^{2}}{2m_e}\nabla^{2} + V(\mathbf{r})\right )\psi(\mathbf{r}) = E\psi(\mathbf{r})$ }\\ \hline

Eq2 & \scriptsize{Atomic mass in terms of number of proton and number of neutrons} & \scriptsize {\codefont <math> <mi>A</mi> <mo>=</mo> <mi>Z</mi> <mo>+</mo> <mi>N</mi> </math>} & \scriptsize{$A = Z + N$} \\ \hline

Eq3 & \scriptsize{Radiation flux in term of the initial intensity, the absorption coefficient and the thickness of a substance} & \scriptsize {\codefont <math> <mi>I</mi> <mo>=</mo> <msub> <mi>I</mi> <mn>0</mn> </msub><msup> <mi>e</mi> <mrow> <mo>-</mo> <mi>μ</mi> <mi>x</mi> </mrow> </msup> </math>
} & \scriptsize{$I = I_0e^{-\mu x}$ } \\ \hline

Eq4 & \scriptsize{Higgs Boson decaying process into $W^+$ and $W^-$ bosons. This is not exactly a mathematical equation, but a physical process. However it is also expressed in LaTeX and to high energy physics experts, it makes sense to search them.} & \scriptsize {\codefont <math> <mi>H</mi> <mo>→</mo> <msup> <mi>W</mi> <mo>+</mo> </msup> <msup> <mi>W</mi> <mo>-</mo> </msup> </math>} & \scriptsize{$H\rightarrow W^+W^-$ } \\ \hline

Eq5 & \scriptsize{Einstein Field equation} & \scriptsize {\codefont <math> <msub> <mi>G</mi> <mrow> <mi>μ</mi> <mi>ν</mi> </mrow> </msub> <mo>=</mo> <msub> <mi>R</mi> <mrow> <mi>μ</mi> <mi>ν</mi> </mrow> </msub> <mo>-</mo> <mfrac> <mn>1</mn> <mn>2</mn> </mfrac> <mi>R</mi> <msub> <mi>g</mi> <mrow> <mi>μ</mi> <mi>ν</mi> </mrow> </msub> <mo>=</mo> <mfrac> <mrow> <mn>8</mn> <mi>π</mi> <mi>G</mi> </mrow> <msup> <mi>c</mi> <mn>4</mn> </msup> </mfrac> <msub> <mi>T</mi> <mrow> <mi>μ</mi> <mi>ν</mi> </mrow> </msub> </math>
 </math>
 } & \scriptsize{$G_{\mu\nu}\equiv R_{\mu\nu} - {\textstyle 1 \over 2}R\,g_{\mu\nu} = {8 \pi G \over c^4} T_{\mu\nu}$ } \\ \hline

Eq6 & \scriptsize{Fermi Energy} & \scriptsize {\codefont <math> <msub> <mi>E</mi> <mi>F</mi> </msub> <mo>=</mo> <mfrac> <mrow> <msub> <mi>E</mi> <mi>C</mi> </msub> <mo>+</mo> <msub> <mi>E</mi> <mi>V</mi> </msub> </mrow> <mn>2</mn> </mfrac> <mo>+</mo> <mfrac> <mrow> <msub> <mi>κ</mi> <mi>B</mi> </msub> <mi>T</mi> </mrow> <mn>2</mn> </mfrac> <mi>ln</mi> <mfenced close=")" open="("> <mfrac> <msub> <mi>N</mi> <mi>V</mi> </msub> <msub> <mi>N</mi> <mi>C</mi> </msub> </mfrac> </mfenced> </math>} & \scriptsize{$E_F = \frac{E_C + E_V}{2} + \frac{\kappa_{B}T}{2} \ln \left(\frac{N_V}{N_C}\right)$ } \\ \hline

\caption{Sample equations used during testing}
\label{equations_table}
\end{longtable}

### 2014-02-21 docs/thesis/appendix-uml.tex
work on document: added graphics

\chapter{Detailed system architecture diagrams}

\section{Analyzers}
\begin{figure}
	\centering
	\includegraphics[height=4 cm]{visio_drawings/analyzers.png}
	\caption{Overview of {\small{\codefont cern.ch.mathexplorer.lucene.analysis.analyzers}} package}
	\label{uml_analyzers}
\end{figure}

\section{Tokenizers}
\begin{figure}
	\centering
	\includegraphics[height=4 cm]{visio_drawings/tokenizers.png}
	\caption{Overview of {\small{\codefont cern.ch.mathexplorer.lucene.analysis.tokenizers}} package}
	\label{uml_tokenizers}
\end{figure}

\section{Filters}
\begin{figure}
	\centering
	\includegraphics[height=4 cm]{visio_drawings/filters.png}
	\caption{Overview of {\small{\codefont cern.ch.mathexplorer.lucene.analysis.filters}} package}
	\label{uml_filters}
\end{figure}

### 2014-02-21 docs/thesis/chap-cern_math_explorer.tex
work on document: added graphics

@@
 
-After examining a set of relevant documents from our dataset, we identified some heuristics that could be applied to improve the recall of our system:
+After examining a set of documents from our dataset, we identified some heuristics that could be applied to improve the recall of our system:
 
@@
 \subsection{Structural Features}
+The structure of a mathematical equations is one of the most important features that can be extracted.
 
@@
 The drawback of our solution is the need to manually select representative and useful patterns.
-This selection was done based on standard based tables of integrals similar to the ones that Computational Algebraic Systems employ to compute them.
+This selection was done based on standard based tables of integrals similar to the ones that CASs employ to compute them.
 
@@
 \subsection{Development with Lucene/Solr}
-This section explains how the described features were implemented in the {\codefont Apache Solr/Lucene} framework.
+This section explains how the described components were implemented in the {\codefont Apache Solr/Lucene} framework.
+One focus of our work was to develop a modular system that allowed easily to deploy new heuristics as they were identified.
+
+Lucene framework defines some key concepts which ultimately are mapped into concrete classes.
+A {\codefont Document} is the minimum retrieval unit.
+For $5e^{x+y}$ we could either use a complete article as a document or a single equation.
+We choose the latter because it makes easier to focus on extracting features from a single equation.
+A document contains a set of {\codefont fields} which represent different types of information that it can store.
+Each field has different options such as whether it would be indexed and/or stored.
+A field can also indicate whether it will be a {\codefont Term Vector}.
+Our fields are as follow:
+\begin{itemize}
+\item math\_notational\_field: This field stores the notational features as a Term Vector. 
+\item math\_structural\_field: This field stores the structural features as a Term Vector. 
+\item math\_normalized\_notational\_field: This field stores the notational features of the normalized expression as a Term Vector. 
+\item filename: This is an auxiliary field which stores the CDS record / article name where the equation was found.
+\item number\_occurrences: Another auxiliary field that is used to score final results.
+\end{itemize}
+
+Each field is associated to a particular {\codefont Analyzer}.
+An analyzer is a specific class that handles an element from a field and groups all the operations that are to be performed.
+For this purpose we wrote {\codefont SolrNotationalAnalyzer}, {\codefont SolrStructuralAnalyzer} and {\codefont SolrNormalizedNotationalAnalyzer}.
+The Solr prefix is added to make clear the fact that the class extends a {\codefont SolrAnalyzer} which extends a normal lucene {\codefont Analyzer}.
+
+An analyzer consists of a sequence of {\codefont TokenStrem} elements.
+Normally an analyzer contains one {\codefont Tokenizer} element (which extends a {\codefont TokenStrem}) that is in charge of creating the Terms that will be stored in the field, and one or more {\codefont TokenFilter} elements which perform operations on the single tokens that were created previously.
+For the specific cases of SolrNotationalAnalyzer and SolrNormalizedNotationalAnalyzer we created the following classes:
+
+\begin{itemize}
+\item {\codefont MultiplePatternTokenizer}: This class is in charge of applying a set of regular expressions over the given expression in order to extract the single elements that were presented.
+Lucene incorporates the class {\codefont PatternTokenizer} but it only accepts one regular expression.
+\item {\codefont UnicodeNormalizingFilter}: This class receives single tokens and verifies if the token is in Unicode NFKD. In negative case, it emits an additional token in the normalized form.
+\item {\codefont SynonymExpandingFilter}: This class verifies if the received token belongs to a predefined category of elements and emits an additional token with it.
+\item {\codefont NumericalRoundingFilter}: This class process {\codefont <mn>} tokens.
+When a number contains a decimal part, it applies the standard rounding mode iteratively and for each one, it emits a token for each step.
+\end{itemize}
+
+{\codefont SolrStructuralAnalyzer } is simpler in its workflow: It consits of a {\codefont StructuralPatternsTokenizer} that tries to find occurrences of the predefined patterns in the expression.
+For each match, it emits a token with the pattern that was found.
 \subsection{Integration with Mathematica}
-This section describes some aspects that should be had to be considered while implementing the integration with the Mathematica CAS.
-Our system uses the provided {\codefont JLink} library to create a connection with the underlying process {\codefont MathKernel}.
+This section describes some aspects that had to be considered while implementing the integration with Mathematica.
+Our system uses the {\codefont JLink} library to create a connection with the underlying process {\codefont MathKernel}.
 The main class for communicating java code and {\codefont Mathematica} is {\codefont KernelLink} and the main used method was {\codefont evaluateToOutputForm(String expr, int pageWidth)} where {\codefont expr} is the expression to be evaluated and {\codefont pageWidth} affects the formatting of the result.
@@
 \subsection{Integration with CDS}
+Currently the Invenio code-base is being under a deep refactoring and rewriting.
+CDS currently runs in the stable branch {\codefont master} while the new developments are preferred to be implemented in the new branch {\codefont pu}.
+A demo interface over the new branch was developed to showcase the system, however to have a complete integration with CDS, a more deep work is required. 
+Our system is deployed as a standalone jar which should be incorporated into a Solr instance.
+Also, some extra configurations should be added.
+Details on this can be found in appendix \ref{appendix-conf_files.}
+The communication between Solr and Invenio was through the library {\codefont solrpy}.

### 2014-02-21 docs/thesis/chap-evaluation.tex
work on document: added graphics

--- 2014-02-20 docs/thesis/chap-evaluation.tex
@@
 Table \ref{equations_table} presents the set of queries that were evaluated, and a simple explanation about it. 
+Each of the users evaluated the results only for the equations he/she provided.
+For each of the presented result, the user ranked it as "Strictly Relevant", "Partially Relevant" and "Completely Irrelevant".
+As all evaluations including human interaction, this scoring is at some level subjective.
+
+We present results for three metrics: Partial precision (Document either partially relevant or completely relevant) strict precision and discounted cumulative gain.
 

### 2014-02-21 docs/thesis/chap-technical_considerations.tex
work on document: added graphics

@@
 One of the most common ways to represent mathematics in scientific documents, which suits CDS's domain, is \LaTeX.
+
 Another  important standard for the representation of mathematics is MathML, which was first proposed by the World Wide Web Consortium in 1998 as the recommended language to be used in web documents.
@@
 The first one is oriented to the visual representation of the expression and the second one is more oriented to the semantics of the expression.
-OpenMath is another markup language to represent mathematics and can be used to compliment presentation MathML to add more semantic information.
+Its main component is the <apply> tag which represents the function application .
 
-Table \ref{math_languages} presents a comparison on how different languages can express the expression $x^2 + y^2 = z^2$
+OpenMath is yet another markup language to represent mathematics and can be used to compliment presentation MathML to add more semantic information.
+It is mainly used now for defining mathematical concepts into standard content dictionaries which can be imported.
+MathML is compatible with this dictionaries.
+
+Table \ref{math_languages} presents a comparison on how different languages can express the quadratic equation $x = \frac{-b \pm \sqrt{b^2 - 4ac}}{2a} $
 
@@
 {\centering\arraybackslash}m{3cm}|>
-{\centering\arraybackslash}m{3cm}|
+{\centering\arraybackslash}m{5cm}|
 }
@@
 \textbf{Presentation MathML} & 
-\textbf{Content MathML} & 
+\textbf{Content MathML + Presentation Markups} & 
 \textbf{OpenMath}  \\ \hline
 
-\verb|$x^2 + y^2 = z^2$|&&&
+\scriptsize{\lstinline|$x = \frac{-b \pm \sqrt{b^2 - 4ac}}{2a} $|}
+& \scriptsize{\codefont <math display="block"> <mrow>   <mi>x</mi>  <mo>=</mo>  <mfrac> <mrow> <mo>-</mo> <mi>b</mi> <mo>
+{\unicodefont \char"00B1} </mo> <msqrt> <msup> <mi>b</mi> <mn>2</mn> </msup> <mo>-</mo> <mn>4</mn> <mo></mo> <mi>a</mi> <mo></mo> <mi>c</mi> </msqrt> </mrow> <mrow> <mn>2</mn> <mo></mo> <mi>a</mi> </mrow> </mfrac> </mrow> </math>}
+&
+\scriptsize{\codefont <math> <apply> <eq/> <ci>x</ci> <csymbol> <mfrac> <apply> <minus/> <mi>b</mi> {\unicodefont \char"00B1} <mroot> <apply> <minus/> <csymbol> <msup> <mi>b</mi> <mn>2</mn> </msup> </csymbol> <csymbol> <mn>4</mn> <mo>\&times;</mo> <mi>a</mi> <mo>\&times;</mo> <mi>c</mi> </csymbol> </apply> <mrow></mrow> </mroot> </apply> <apply> <times/> <cn>2</cn> <ci>a</ci> </apply> </mfrac> </csymbol> </apply> </math> }
+&
+\scriptsize{\codefont 
+<OMOBJ> <OMA> <OMS cd = "relation1" name="eq"/> <OMV name="x"/>
+    <OMA> <OMS cd="arith1" name="divide"/> <OMA> <OMS cd = "arith1" name="minus"/><OMA> <OMS cd = "arith1" name="times"/>
+          <OMA> <OMS cd = "arith1" name="times"/> <OMV name="b"/> <OMV name="+ALE-"/> </OMA> <OMA> <OMS cd="arith1" name="root"/> <OMA> <OMS cd = "arith1" name="minus"/> <OMA> <OMS cd="arith1" name="power"/> <OMV name="b"/> <OMI>2</OMI> </OMA> <OMA> <OMS cd = "arith1" name="times"/> <OMA> <OMS cd = "arith1" name="times"/> <OMI>4</OMI> <OMV name="a"/> </OMA> <OMV name="c"/> </OMA> </OMA> <OMA> <OMI> 2 </OMI> </OMA> </OMA> </OMA> <OMA> <OMS cd = "arith1" name="times"/> <OMI>2</OMI> <OMV name="a"/> </OMA> </OMA> </OMA> </OMOBJ>}
 \\
@@
 
-Because
+\LaTeX allows the most compact representations of the equations and it is the closest language to the community.
+However, its processing is not straightforward because a given equation can include multiple commands from different packages.
+Also there are several ways to represent the same set of symbols, either using its Unicode code-point or through embedded commands.
+Another difficulty are custom commands that users can define in the preamble of the document.
+In overall, the interpretation and processing of a mathematical expression in this language would require writing a complete compiler which is not the purpose of this work.
+MathML offers a better compromise between the length of the representation and the easiness to be processed.
 

### 2014-02-21 docs/thesis/chap-conclusions.tex
added section of dlmf

\chapter{Conclusions}
\label{chapter-conclusions}

### 2014-02-21 docs/thesis/chap-related_work.tex
added section of dlmf

@@
 \subsection{DLMFSearch}
+The Digital Library for Mathematical Funtions \cite{dlmf} is a project launched by the National Institute of Standards and Technology, in 2010, as an online version of the  Handbook of Mathematical Functions with Formulas, Graphs and Mathematical Tables\cite{handbook}.
+DLMF's main goal is to compile the mathematical knowledge in the form of equations, functions, tables and make this information useful for researchers and public in general.
+The system contains a search functionality that allows to input a combination of full text and \LaTeX snippets.
+The system tries to perform an exact match, and if no results are found, it relaxes the query.
+DLMF also perfoms some normalization of the equation and some cleaning of some characters, but no further details are provided.
+The content indexed by this project is highly curated, which differentiates it from the other projects.
+In the report published in 2013 \cite{dlmf2}, it is reported to have indexed around 38000 equations.
+
 \subsection{MathWebSearch}
@@
 The system implements and idea proposed by Peter Graf in \cite{substitution_tree_indexing} called substitution tree indexing.
-This idea can be viewed as a generalization of the variable and constant unification employed by MIaS
+This idea can be viewed as a generalization of the variable and constant unification.
+It represents the equations as a tree an recursively generalizes each sub-expression.
 

### 2014-02-24 docs/thesis/chap-evaluation.tex
added section of experiment comparing metrics

@@
 \end{longtable}
+
+\section{Alternative Metrics}
+According to some experimental evaluations presented in \cite{tree_comparison}, Tree Edit Distance provides an interesting alternative metric to the standard vector space model using angular distance.
+In this work, authors present an improvement in the quality of retrieved results compared to the classic approach of indexing the single leaves of the tree and a subset of the possible sub-trees.
+For evaluating the feasibility of this approach we compared a set of equations using both metrics: Tree edit distance (Using Zheng and Shasha's algorithm implemented in python \cite{tree_distance_python}.) and a standard angular distance that was not heavily optimized.
+We compared elapsed times for expressions of different length.
+
+\begin{longtable}{|c|c|c|}
+\hline 
+Expression Length & Angular Distance Time (msec) & Tree Edit Distance Time(msec) \\ \hline 
+70 & 0.01195 & 2.65  \\ \hline
+145 & 0.0142 & 9.97  \\ \hline
+155 & 0.0129 & 9.165  \\ \hline
+185 & 0.0173 & 8.925  \\ \hline
+267 & 0.0194 & 15.15  \\ \hline
+405 & 0.0201 & 29.5  \\ \hline
+406 & 0.0245 & 27.75  \\ \hline
+442 & 0.0236 & 30.95  \\ \hline
+522 & 0.0264 & 32.4  \\ \hline
+719 & 0.02502 & 32.1 \\ \hline
+
+\caption{Distance computation using two different metrics}
+\label{comparison_tree_times}
+\end{longtable}
+
+This result show that for shorter expressions, using tree edit distance represent an increase in time in more than 200x, and a factor of around 1200x for the longer expressions, making it impractical for implementing a system that needs to be responsive.
+Even though there are algorithms which provide a better asymptotic guarantees and better actual running times like RTED\cite{rted} with respect to Zheng ans Shasha's algorithm, the best improvements represent a decrease in processing time of 50\% to 80\% in trees with around 1000 nodes, while the standard tested equations which are representative of our dataset, contain less than 100 nodes.

### 2014-02-24 docs/thesis/appendix-test_equations.tex
more diagrams: main packages, query

--- 2014-02-21 docs/thesis/appendix-system_design.tex
@@
 
-Eq6 & \scriptsize{Fermi Energy} & \scriptsize {\codefont <math> <msub> <mi>E</mi> <mi>F</mi> </msub> <mo>=</mo> <mfrac> <mrow> <msub> <mi>E</mi> <mi>C</mi> </msub> <mo>+</mo> <msub> <mi>E</mi> <mi>V</mi> </msub> </mrow> <mn>2</mn> </mfrac> <mo>+</mo> <mfrac> <mrow> <msub> <mi>κ</mi> <mi>B</mi> </msub> <mi>T</mi> </mrow> <mn>2</mn> </mfrac> <mi>ln</mi> <mfenced close=")" open="("> <mfrac> <msub> <mi>N</mi> <mi>V</mi> </msub> <msub> <mi>N</mi> <mi>C</mi> </msub> </mfrac> </mfenced> </math>} & \scriptsize{$E_F = \frac{E_C + E_V}{2} + \frac{\kappa_{B}T}{2} \ln \left(\frac{N_V}{N_C}\right)$ } \\ \hline
+Eq6 & \scriptsize{Dirac Equation} & \scriptsize {\codefont <math> <mfenced close=")" open="("> <mrow> <mi>β</mi> <mi>m</mi> <msup> <mi>c</mi> <mn>2</mn> </msup> <mo>+</mo> <mi>c</mi> <mfenced close=")" open="("> <mrow> <msub> <mi>α</mi> <mn>1</mn> </msub> <msub> <mi>p</mi> <mn>1</mn> </msub> <mo>+</mo> <msub> <mi>α</mi> <mn>2</mn> </msub> <msub> <mi>p</mi> <mn>2</mn> </msub> <mo>+</mo> <msub> <mi>α</mi> <mn>3</mn> </msub> <msub> <mi>p</mi> <mn>3</mn> </msub> </mrow> </mfenced> </mrow> </mfenced> <mi>ψ</mi> <mfenced close=")" open="("> <mi>x</mi> <mi>t</mi> </mfenced> <mo>==</mo> <mi>i</mi> <mi>ℏ</mi> <mfrac> <mrow> <mo>∂</mo> <mi>ψ</mi> <mfenced close=")" open="("> <mi>x</mi> <mi>t</mi> </mfenced> </mrow> <mrow> <mo>∂</mo> <mi>t</mi> </mrow> </mfrac> </math>
+} & \tiny{$\left(\beta mc^2 + c(\alpha_1 p_1 +  \alpha_2 p_2 + \alpha_3 p_3)\right) \psi (x,t) = i \hbar \frac{\partial\psi(x,t) }{\partial t}$ } \\ \hline
 

### 2014-02-24 docs/thesis/chap-evaluation.tex
more diagrams: main packages, query

@@
 \hline 
-Expression Length & Angular Distance Time (msec) & Tree Edit Distance Time(msec) \\ \hline 
-70 & 0.01195 & 2.65  \\ \hline
-145 & 0.0142 & 9.97  \\ \hline
-155 & 0.0129 & 9.165  \\ \hline
-185 & 0.0173 & 8.925  \\ \hline
-267 & 0.0194 & 15.15  \\ \hline
-405 & 0.0201 & 29.5  \\ \hline
-406 & 0.0245 & 27.75  \\ \hline
-442 & 0.0236 & 30.95  \\ \hline
-522 & 0.0264 & 32.4  \\ \hline
-719 & 0.02502 & 32.1 \\ \hline
+Expression Length (Number of leaf nodes)& Angular Distance Time (msec) & Tree Edit Distance Time(msec) \\ \hline 
+3 & 0.01195 & 2.65  \\ \hline
+8 & 0.0142 & 9.97  \\ \hline
+7 & 0.0129 & 9.165  \\ \hline
+12 & 0.0194 & 15.15  \\ \hline
+18 & 0.0201 & 29.5  \\ \hline
+20 & 0.0245 & 27.75  \\ \hline
+22 & 0.0264 & 32.4  \\ \hline
+24 & 0.02502 & 32.1 \\ \hline
 

### 2014-02-24 docs/thesis/chap-technical_considerations.tex
more diagrams: main packages, query

@@
 \hline
-TeX4ht\cite{tex4ht1}\cite{tex4ht2} & Standalone Executable & 2009-01-31-07 & \LaTeX & XML + MathML & Open Source & 11 Jun 2009  \\
+TeX4ht\cite{tex4ht2} & Standalone Executable & 2009-01-31-07 & \LaTeX & XML + MathML & Open Source & 11 Jun 2009  \\
+\hline
+SnuggleTex\cite{snuggletex} & Java Library & 1.2.2 & \LaTeX (Small fragments) & MathML & Open Source & 24 May 2010  \\
 \hline

### 2014-02-24 src/cern/ch/mathexplorer/lucene/query/MathQueryParser.java

@@ -169,7 +169,7 @@ public class MathQueryParser extends QParser {
 
 	public static void main(String[] args) throws Exception {
 		String query = Regex
-				.cleanQuery(texToMathML("G_{\\mu\\nu}\\equiv R_{\\mu\\nu} - {\\textstyle 1 \\over 2}R\\,g_{\\mu\\nu} = {8 \\pi G \\over c^4} T_{\\mu\\nu}"));
+				.cleanQuery(texToMathML("\\left(\\beta mc^2 + c(\\alpha_1 p_1 + \\alpha_2 p_2 + \\alpha_3 p_3)\\right) \\psi (x,t) = i \\hbar \\frac{\\partial\\psi(x,t) }{\\partial t}"));
 		MathQueryParser mqp = new MathQueryParser(query, null, null, null);
 		mqp.parse();
 	}

### 2014-02-24 docs/thesis/appendix-test_equations.tex
refactored project. moved libraries

--- 2014-02-21 docs/thesis/appendix-system_design.tex
@@
 
-Eq6 & \scriptsize{Fermi Energy} & \scriptsize {\codefont <math> <msub> <mi>E</mi> <mi>F</mi> </msub> <mo>=</mo> <mfrac> <mrow> <msub> <mi>E</mi> <mi>C</mi> </msub> <mo>+</mo> <msub> <mi>E</mi> <mi>V</mi> </msub> </mrow> <mn>2</mn> </mfrac> <mo>+</mo> <mfrac> <mrow> <msub> <mi>κ</mi> <mi>B</mi> </msub> <mi>T</mi> </mrow> <mn>2</mn> </mfrac> <mi>ln</mi> <mfenced close=")" open="("> <mfrac> <msub> <mi>N</mi> <mi>V</mi> </msub> <msub> <mi>N</mi> <mi>C</mi> </msub> </mfrac> </mfenced> </math>} & \scriptsize{$E_F = \frac{E_C + E_V}{2} + \frac{\kappa_{B}T}{2} \ln \left(\frac{N_V}{N_C}\right)$ } \\ \hline
+Eq6 & \scriptsize{Luminosity of a star in terms of its temperature and radius} & \scriptsize {\codefont <math><mi>L</mi><mo>=</mo><mn>4</mn><mi>π</mi><msup><mi>R</mi><mn>2</mn></msup><mi>σ</mi><msubsup><mi>T</mi><mrow><mi>e</mi><mi>f</mi><mi>f</mi></mrow><mn>4</mn></msubsup></math>
+} & \scriptsize{$ L = 4\piR^2\sigma T^4_{eff} $ } \\ \hline
 

### 2014-02-24 src/cern/ch/mathexplorer/lucene/query/MathQueryParser.java

@@ -151,7 +151,12 @@ public class MathQueryParser extends QParser {
 
 	public static String texToMathML(String texText) throws IOException {
 		texText = texText.trim();
-		texText.replaceAll("\\$\\$", "$");
+		if (texText.startsWith("$$")){
+			texText.replace("$$", "$");
+		}
+		if (texText.endsWith("$$")){
+			texText.replace("$$", "$");
+		}
 		if (!texText.endsWith("$")) {
 			texText += "$";
 		}
@@ -168,8 +173,7 @@ public class MathQueryParser extends QParser {
 	}
 
 	public static void main(String[] args) throws Exception {
-		String query = Regex
-				.cleanQuery(texToMathML("\\left(\\beta mc^2 + c(\\alpha_1 p_1 + \\alpha_2 p_2 + \\alpha_3 p_3)\\right) \\psi (x,t) = i \\hbar \\frac{\\partial\\psi(x,t) }{\\partial t}"));
+		String query = Regex.cleanQuery(texToMathML("$$ A+B $$"));
 		MathQueryParser mqp = new MathQueryParser(query, null, null, null);
 		mqp.parse();
 	}

### 2014-02-25 docs/thesis/chap-cern_math_explorer.tex
work on thesis

@@
 
-\subsubsection{Synonym Expansion}
+\subsubsection{Operator grouping}
 Even though the Unicode normalization step work for a big part of the cases presented in table \ref{unicode_characters}, there are still some groups of characters which would not be matched (Even partially), such as some types of integrals.
-For addressing these groups, a precomputed table was created for some general groups of characters which have some similar meaning.
+For addressing these groups, a precomputed table was created for some general groups of operators which have some similar meaning.
 For each token that belongs to some of this predefined groups, a second token is created identifying the group.
@@
 \subsection{Structural Features}
-The structure of a mathematical equations is one of the most important features that can be extracted.
+The structure of a mathematical expression compliments the information that an be obtained over generic substructures where the naming of the variables is irrelevant.
 
@@
 Additionally, we identified patterns that are relevant and frequent in specific domains of the high energy physics.
-Some patterns can be as general as a derivative over time ($dx/dt$), or more specific ones like a particle decaying process ($originalParticle \rightarrow subparticle1, subparticle2, subparticle3$).
+Some patterns can be as general as a derivative over time ($dx/dt$), or more specific ones like a particle decaying process ($originalParticle \rightarrow subparticle1, subparticle2, subparticle3$) and some in the middle like the general structure of a given action: $S = \int^{t2}_{t1} \mathcal{L} dt$.
+The main drawback of this approach is the need to manually detect, implement and maintain long lists of patterns.
 
@@
 CDS currently runs in the stable branch {\codefont master} while the new developments are preferred to be implemented in the new branch {\codefont pu}.
-A demo interface over the new branch was developed to showcase the system, however to have a complete integration with CDS, a more deep work is required. 
 Our system is deployed as a standalone jar which should be incorporated into a Solr instance.
 Also, some extra configurations should be added.
-Details on this can be found in appendix \ref{appendix-conf_files.}
+Details on this can be found in appendix \ref{appendix-conf_files}
 The communication between Solr and Invenio was through the library {\codefont solrpy}. 
+A demo interface over the new branch was developed to showcase the system, however to have a complete integration with CDS, a more deep work is required.
+
+\begin{figure}
+\includegraphics[height=8 cm]{figures/input_interface.png}
+\label{comparison_sw_table}
+\caption{Web interface of $5e^{x+y}$: Query input screen}
+\end{figure}
+
+\begin{figure}
+\includegraphics[height=8 cm]{figures/results_interface.png}
+\label{comparison_sw_table}
+\caption{Web interface of $5e^{x+y}$: Results screen}
+\end{figure}

### 2014-02-25 docs/thesis/appendix-test_equations.tex
work on thesis: finished sample equations

@@
 \hline
-Eq1 & \scriptsize{ Time-independent Schr\char"00F6dinger equation} & \scriptsize {\codefont <math><mfenced close=")" open="("> <mrow> <mo>-</mo> <mfrac> <msup> <mi>ℏ</mi> <mn>2</mn> </msup> <mrow> <mn>2</mn> <msub> <mi>m</mi> <mi>e</mi> </msub> </mrow> </mfrac> <msup> <mo>$\nabla$</mo> <mn>2</mn> </msup> <mo>+</mo> <mi>V</mi> <mfenced close=")" open="("> <mi>r</mi> </mfenced> </mrow> </mfenced> <mi>ψ</mi> <mfenced close=")" open="("> <mi>r</mi> </mfenced> <mo>=</mo> <mi>E</mi> <mi>ψ</mi> <mfenced close=")" open="("> <mi>r</mi> </mfenced> </math>} & \scriptsize{ $\left (-\frac{\hbar^{2}}{2m_e}\nabla^{2} + V(\mathbf{r})\right )\psi(\mathbf{r}) = E\psi(\mathbf{r})$ }\\ \hline
+Eq1 & \scriptsize{ Time-independent Schr\char"00F6dinger equation} & \scriptsize {\codefont <math><mfenced close=")" open="("> <mrow> <mo>-</mo> <mfrac> <msup> <mi>ℏ</mi> <mn>2</mn> </msup> <mrow> <mn>2</mn> <msub> <mi>m</mi> <mi>e</mi> </msub> </mrow> </mfrac> <msup> <mo>$\nabla$</mo> <mn>2</mn> </msup> <mo>+</mo> <mi>V</mi> <mfenced close=")" open="("> <mi>r</mi> </mfenced> </mrow> </mfenced> <mi>ψ</mi> <mfenced close=")" open="("> <mi>r</mi> </mfenced> <mo>=</mo> <mi>E</mi> <mi>ψ</mi> <mfenced close=")" open="("> <mi>r</mi> </mfenced> </math>} & \small{ $\left (-\frac{\hbar^{2}}{2m_e}\nabla^{2} + V(\mathbf{r})\right )\psi(\mathbf{r}) = E\psi(\mathbf{r})$ }\\ \hline
 
-Eq2 & \scriptsize{Atomic mass in terms of number of proton and number of neutrons} & \scriptsize {\codefont <math> <mi>A</mi> <mo>=</mo> <mi>Z</mi> <mo>+</mo> <mi>N</mi> </math>} & \scriptsize{$A = Z + N$} \\ \hline
+Eq2 & \scriptsize{Atomic mass in terms of number of proton and number of neutrons} & \scriptsize {\codefont <math> <mi>A</mi> <mo>=</mo> <mi>Z</mi> <mo>+</mo> <mi>N</mi> </math>} & \small{$A = Z + N$} \\ \hline
 
 Eq3 & \scriptsize{Radiation flux in term of the initial intensity, the absorption coefficient and the thickness of a substance} & \scriptsize {\codefont <math> <mi>I</mi> <mo>=</mo> <msub> <mi>I</mi> <mn>0</mn> </msub><msup> <mi>e</mi> <mrow> <mo>-</mo> <mi>μ</mi> <mi>x</mi> </mrow> </msup> </math>
-} & \scriptsize{$I = I_0e^{-\mu x}$ } \\ \hline
+} & \small{$I = I_0e^{-\mu x}$ } \\ \hline
 
@@
 This is not exactly a mathematical equation, but a physical process.
-However it is also expressed in LaTeX and to high energy physics experts, it makes sense to search them.} & \scriptsize {\codefont <math> <mi>H</mi> <mo>→</mo> <msup> <mi>W</mi> <mo>+</mo> </msup> <msup> <mi>W</mi> <mo>-</mo> </msup> </math>} & \scriptsize{$H\rightarrow W^+W^-$ } \\ \hline
+However it is also expressed in LaTeX and to high energy physics experts, it makes sense to search them.} & \scriptsize {\codefont <math> <mi>H</mi> <mo>→</mo> <msup> <mi>W</mi> <mo>+</mo> </msup> <msup> <mi>W</mi> <mo>-</mo> </msup> </math>} & \small{$H\rightarrow W^+W^-$ } \\ \hline
 
@@
  </math>
- } & \scriptsize{$G_{\mu\nu}\equiv R_{\mu\nu} - {\textstyle 1 \over 2}R\,g_{\mu\nu} = {8 \pi G \over c^4} T_{\mu\nu}$ } \\ \hline
+ } & \footnotesize{$G_{\mu\nu} = R_{\mu\nu} - {\textstyle 1 \over 2}R\,g_{\mu\nu} = {8 \pi G \over c^4} T_{\mu\nu}$ } \\ \hline
 
-Eq6 & \scriptsize{Luminosity of a star in terms of its temperature and radius} & \scriptsize {\codefont <math><mi>L</mi><mo>=</mo><mn>4</mn><mi>π</mi><msup><mi>R</mi><mn>2</mn></msup><mi>σ</mi><msubsup><mi>T</mi><mrow><mi>e</mi><mi>f</mi><mi>f</mi></mrow><mn>4</mn></msubsup></math>
-} & \scriptsize{$ L = 4\piR^2\sigma T^4_{eff} $ } \\ \hline
+Eq6 & \scriptsize{Luminosity of a star in terms of its temperature and radius} & \scriptsize {\codefont <math> <mi>L</mi> <mo>=</mo> <mn>4</mn> <mi>π</mi> <msup> <mi>R</mi> <mn>2</mn> </msup> <mi>σ</mi> <msubsup> <mi>T</mi> <mrow> <mi>e</mi> <mi>f</mi> <mi>f</mi> </mrow> <mn>4</mn> </msubsup> </math>
+} & \small{$ L = 4 \pi R^2 \sigma T^4_{eff} $ } \\ \hline
+
+Eq7 & \scriptsize{Free-cyclotron motion of an electron in terms of its charge, mass and the magnetic field} & \scriptsize {\codefont <math> <msub> <mi>ω</mi> <mi>c</mi> </msub> <mo>=</mo> <mo>|</mo> <mi>q</mi> <mover accent="true"> <mi>B</mi> <mo>→</mo> </mover> <mo>|</mo> <mo>/</mo> <mi>m</mi> </math>
+} & \small{$ \omega_c = |q\vec{B}|/m $ } \\ \hline
+
+Eq8 & \scriptsize{Spin energy of a particle in presence of an external magnetic field} & \scriptsize{\codefont <math> <mi>E</mi> <mo>=</mo> <mo>-</mo> <mover accent="true"> <mi>μ</mi> <mo>→</mo> </mover> <mo>⋅</mo> <mover accent="true"> <mi>B</mi> <mo>→</mo> </mover> </math>
+} & \small { $E = -\vec{\mu} \cdot \vec{B}$ } \\ \hline
+
+Eq9 & \scriptsize{Quantum electrodynamics Lagrangian modelling the interaction of the -1/2 spin field with the electromagnetic field} & \scriptsize{\codefont <math > <msub> <mi mathvariant="script">L</mi> <mstyle mathvariant="normal"> <mi>Q</mi> <mi>E</mi> <mi>D</mi> </mstyle> </msub> <mo>=</mo> <msub> <mover accent="true"> <mi>ψ</mi> <mo>̄</mo> </mover> <mi>i</mi> </msub> <mi>i</mi> <mfenced close=")" open="("> <mrow> <msub> <mfenced close=")" open="("> <mrow> <msup> <mi>γ</mi> <mi>μ</mi> </msup> <msub> <mi>D</mi> <mi>μ</mi> </msub> </mrow> </mfenced> <mrow> <mi>i</mi> <mi>j</mi> </mrow> </msub> <mo>-</mo> <mi>m</mi> <msub> <mi>δ</mi> <mrow> <mi>i</mi> <mi>j</mi> </mrow> </msub> </mrow> </mfenced> <msub> <mi>ψ</mi> <mi>j</mi> </msub> <mo>-</mo> <mfrac> <mn>1</mn> <mn>4</mn> </mfrac> <msub> <mi>F</mi> <mrow> <mi>μ</mi> <mi>ν</mi> </mrow> </msub> <msup> <mi>F</mi> <mrow> <mi>μ</mi> <mi>ν</mi> </mrow> </msup> </math>
+} & \small { $\mathcal{L}_\mathrm{QED} 
+= \bar{\psi}_i i \left( (\gamma^\mu D_\mu)_{ij} - m\, \delta_{ij}\right) \psi_j - \frac{1}{4}F_{\mu \nu} F^{\mu \nu}  $ } \\ \hline
+
+Eq10 & \scriptsize{Einstein-Hilbert action} & \scriptsize{\codefont <math> <mi>S</mi> <mo>=</mo> <mfrac> <mn>1</mn> <mrow> <mn>2</mn> <mi>κ</mi> </mrow> </mfrac> <mo>∫</mo> <mi>R</mi> <msqrt> <mrow> <mo>-</mo> <mi>g</mi> </mrow> </msqrt> <msup> <mi>d</mi> <mn>4</mn> </msup> <mi>x</mi> </math>} & \small { $
+    S = {1 \over 2\kappa} \int R \sqrt{-g} \, \mathrm{d}^4x	$ } \\ \hline
 

### 2014-02-25 docs/thesis/chap-cern_math_explorer.tex
work on thesis: finished sample equations

@@
 \subsubsection{Specific domain structures}
-Additionally, we identified patterns that are relevant and frequent in specific domains of the high energy physics.
-Some patterns can be as general as a derivative over time ($dx/dt$), or more specific ones like a particle decaying process ($originalParticle \rightarrow subparticle1, subparticle2, subparticle3$) and some in the middle like the general structure of a given action: $S = \int^{t2}_{t1} \mathcal{L} dt$.
-The main drawback of this approach is the need to manually detect, implement and maintain long lists of patterns.
+
+Additionally, there are common patterns to specific domains which can improve the quality of the retrieved results.
+Some specific patterns we identified include: $originalParticle \rightarrow subparticle1, subparticle2, subparticle3$ (For representing particle decaying processes) $S = \int^{t2}_{t1} \mathcal{L} dt$ (For an action in terms of its Lagrangian) and $SU(n)$ (For describing special unitary groups).
+The main drawback of this approach is the need to manually detect, implement and maintain long lists of patterns and for this reason we did not tried to do an exhaustive list of them.
 

### 2014-02-25 docs/thesis/appendix-test_equations.tex
pics from the queries

@@
 
-Eq4 & \scriptsize{Higgs Boson decaying process into $W^+$ and $W^-$ bosons.
-This is not exactly a mathematical equation, but a physical process.
-However it is also expressed in LaTeX and to high energy physics experts, it makes sense to search them.} & \scriptsize {\codefont <math> <mi>H</mi> <mo>→</mo> <msup> <mi>W</mi> <mo>+</mo> </msup> <msup> <mi>W</mi> <mo>-</mo> </msup> </math>} & \small{$H\rightarrow W^+W^-$ } \\ \hline
+Eq4 & \scriptsize{Higgs Boson decaying process into $W^+$ and $W^-$ bosons.} & \scriptsize {\codefont <math> <mi>H</mi> <mo>→</mo> <msup> <mi>W</mi> <mo>+</mo> </msup> <msup> <mi>W</mi> <mo>-</mo> </msup> </math>} & \small{$H\rightarrow W^+W^-$ } \\ \hline
 
 Eq5 & \scriptsize{Einstein Field equation} & \scriptsize {\codefont <math> <msub> <mi>G</mi> <mrow> <mi>μ</mi> <mi>ν</mi> </mrow> </msub> <mo>=</mo> <msub> <mi>R</mi> <mrow> <mi>μ</mi> <mi>ν</mi> </mrow> </msub> <mo>-</mo> <mfrac> <mn>1</mn> <mn>2</mn> </mfrac> <mi>R</mi> <msub> <mi>g</mi> <mrow> <mi>μ</mi> <mi>ν</mi> </mrow> </msub> <mo>=</mo> <mfrac> <mrow> <mn>8</mn> <mi>π</mi> <mi>G</mi> </mrow> <msup> <mi>c</mi> <mn>4</mn> </msup> </mfrac> <msub> <mi>T</mi> <mrow> <mi>μ</mi> <mi>ν</mi> </mrow> </msub> </math>
- </math>
  } & \footnotesize{$G_{\mu\nu} = R_{\mu\nu} - {\textstyle 1 \over 2}R\,g_{\mu\nu} = {8 \pi G \over c^4} T_{\mu\nu}$ } \\ \hline

### 2014-02-25 docs/thesis/chap-evaluation.tex
work on thesis
cleaned useless docs

@@
 \section{Comparison against other systems}
-In this section we tried to compare our implementation of MASE(CDS) with the public available systems presented in the related work chapter.
+In this section we compared our implementation of MASE(CDS) with the public available systems presented in the related work chapter.
 We judged if the fetched results of each system were relevant or not using the same criteria as for the previous section.
@@
 
-The results are a little disappointing since from the eight evaluated instances, only MIaS and Symbolab seem to be working properly.
+The first result about this evaluation is that only two different instances developed and running. The other ones seems to have been abandoned.
 
@@
 
-\begin{longtable}{|c|c|c|}
+%%
+%\begin{longtable}{|m{3.5cm}|>
+%{\centering\arraybackslash}m{3cm}|>
+%{\centering\arraybackslash}m{3cm}|>
+%{\centering\arraybackslash}m{5cm}|
+%}
+%\hline 
+%\textbf{\LaTeX} & 
+%\textbf{Presentation MathML} & 
+%\textbf{Content MathML + Presentation Markups} & 
+%\textbf{OpenMath}  \\ \hline
+%%%
+
+\begin{longtable}{|>{\centering\arraybackslash}m{3.5cm}|>
+{\centering\arraybackslash}m{3cm}|>
+{\centering\arraybackslash}m{3cm}|
+}
 \hline 

### 2014-02-27 docs/thesis/chap-cern_math_explorer.tex
Added more characters/categories. Work on document: some drawings, graphics, and added comparison on simplification methods.

@@
 
+Figures \ref{integrals} and \ref{less_greater} present lists related of characters for two different categories.
+
+\begin{figure}[h!]
+	\centering
+	\includegraphics[height=2 cm]{figures/integrals.png}
+	\caption{List of different types of integral related characters in Unicode}
+	\label{integrals}
+\end{figure}
+
+\begin{figure}[h!]
+	\centering
+	\includegraphics[height=2 cm]{figures/greater_less.png}
+	\caption{List of different types of grater/less than related characters in Unicode}
+	\label{less_greater}
+\end{figure}
+
 \subsubsection{Numeric Approximation} 
@@
 
-\subsection{Development with Lucene/Solr}
+\section{Development with Lucene/Solr}
 This section explains how the described components were implemented in the {\codefont Apache Solr/Lucene} framework.
@@
 For each match, it emits a token with the pattern that was found.
-\subsection{Integration with Mathematica}
+
+\section{Integration with Mathematica}
 This section describes some aspects that had to be considered while implementing the integration with Mathematica.
@@
 \subsubsection{Pattern Extraction}
+
+\subsubsection{Expression simplification}
+The second feature that we are interested in is automatic expression simplification.
+Mathematica includes different transformations of expressions.
+These include: {\codefont Simplify} which tries to transform a given equation in an equivalent one but in a reduced form, {\codefont FullSimplify} which is similar to the previous one but tries a higher number of heuristics to apply that can simplify expressions further at the expense of more processing time, {\codefont Factor} to factorize polynomials, {\codefont Refine} which simplifies expressions given certain assumptions about the variables, {\codefont TrigReduce} that tries to apply trigonometric identities to simplify the expression, {\codefont FunctionExpand} that tries to expand special functions in terms of sums and products of other elementary functions.
+
+The two functions that are more relevant for our work are {\codefont Simplify} and {\codefont FullySimplify} since they apply most of the other combined methods and do not require additional information.
+
+Table \ref{table_simplifications} presents some sample equations found in some the documents in CDS and the different forms of simplification.
+
+\begin{tabular}{|>{\centering\arraybackslash}m{4cm}|>
+{\centering\arraybackslash}m{4cm}|>
+{\centering\arraybackslash}m{4cm}|}
+\hline
+Original Form & {\codefont Simplify} & {\codefont FullSimplify} \\
+\hline
+\scriptsize{\codefont <math> <mrow> <mrow> <mfrac> <msup> <mi>Φ</mi> <mo>′</mo> </msup> <mrow> <mn>2</mn> <mo>⁢</mo> <mrow> <mo>(</mo> <mrow> <mn>1</mn> <mo>+</mo> <mi>Φ</mi> </mrow> <mo>)</mo> </mrow> </mrow> </mfrac> <mo>+</mo> <mfrac> <mn>1</mn> <mi>r</mi> </mfrac> </mrow> <mo>=</mo> <mn>0</mn> </mrow> </math> }      & \scriptsize{\codefont <math> <mrow> <mrow> <mfrac> <mn>1</mn> <mi>r</mi> </mfrac> <mo>+</mo> <mfrac> <msup> <mi>Φ</mi> <mo>′</mo> </msup> <mrow> <mrow> <mn>2</mn> <mo>⁢</mo> <mi>Φ</mi> </mrow> <mo>+</mo> <mn>2</mn> </mrow> </mfrac> </mrow> <mo></mo> <mn>0</mn> </mrow> </math>}    & \scriptsize{\codefont <math> <mrow> <mrow> <mfrac> <mn>2</mn> <mi>r</mi> </mfrac> <mo>+</mo> <mfrac> <msup> <mi>Φ</mi> <mo>′</mo> </msup> <mrow> <mi>Φ</mi> <mo>+</mo> <mn>1</mn> </mrow> </mfrac> </mrow> <mo></mo> <mn>0</mn> </mrow> </math>}     \\
+$\frac{\Phi '}{2 (1+\Phi )}+\frac{1}{r}=0$          & $\frac{1}{r}+\frac{\Phi '}{2 \Phi +2}=0$ & $\frac{2}{r}+\frac{\Phi '}{\Phi +1}=0$       \\
+
+\hline
+\end{tabular}
 
@@
 
-\subsection{Integration with CDS}
+\section{Integration with CDS}
 Currently the Invenio code-base is being under a deep refactoring and rewriting.
 CDS currently runs in the stable branch {\codefont master} while the new developments are preferred to be implemented in the new branch {\codefont pu}.
-Our system is deployed as a standalone jar which should be incorporated into a Solr instance.
+Our system is deployed as a standalone {\codefont jar} which is added to a Solr instance.
 Also, some extra configurations should be added.
@@
 The communication between Solr and Invenio was through the library {\codefont solrpy}. 
-A demo interface over the new branch was developed to showcase the system, however to have a complete integration with CDS, a more deep work is required.
+Figure \ref{system_arch} presents the main components of our deployment.
+
+\begin{figure}
+\includegraphics[height=4.2 cm]{visio_drawings/architecture.png}
+\label{comparison_sw_table}
+\caption{High level deployment architecture}
+\end{figure}
+
+A demo interface over the {\codefont pu} branch was developed to showcase the system, however to have a complete integration with CDS, a more deep work is required.
+The demo setup employs the same dataset as used for experimentation.
 

### 2014-02-27 src/cern/ch/mathexplorer/lucene/analysis/analyzers/SolrFullNormalizerNotationalAnalyzer.java

@@ -7,7 +7,7 @@ import org.apache.lucene.util.Version;
 import org.apache.solr.analysis.SolrAnalyzer;
 
 import cern.ch.mathexplorer.lucene.analysis.filters.NumericalRoundingFilter;
-import cern.ch.mathexplorer.lucene.analysis.filters.SynonymExpandingFilter;
+import cern.ch.mathexplorer.lucene.analysis.filters.OperatorGroupingFilter;
 import cern.ch.mathexplorer.lucene.analysis.filters.UnicodeNormalizingFilter;
 import cern.ch.mathexplorer.lucene.analysis.tokenizers.MultiplePatternTokenizer;
 import cern.ch.mathexplorer.mathematica.MathematicaConfig;
@@ -34,7 +34,7 @@ public final class SolrFullNormalizerNotationalAnalyzer extends SolrAnalyzer {
 			  MathematicaConfig.NORMALIZATION_MODES.FULL_SIMPLIFICATION);
 	  TokenStream unicodeNormalizer = new UnicodeNormalizingFilter(source2);
 	  TokenStream numericRounder 	= new NumericalRoundingFilter(unicodeNormalizer);
-	  TokenStream relatedOperators 	= new SynonymExpandingFilter(numericRounder);
+	  TokenStream relatedOperators 	= new OperatorGroupingFilter(numericRounder);
 	  
 	  
 	  return new TokenStreamComponents(source2, relatedOperators);

### 2014-02-27 src/cern/ch/mathexplorer/lucene/analysis/analyzers/SolrNormalizerNotationalAnalyzer.java

@@ -7,7 +7,7 @@ import org.apache.lucene.util.Version;
 import org.apache.solr.analysis.SolrAnalyzer;
 
 import cern.ch.mathexplorer.lucene.analysis.filters.NumericalRoundingFilter;
-import cern.ch.mathexplorer.lucene.analysis.filters.SynonymExpandingFilter;
+import cern.ch.mathexplorer.lucene.analysis.filters.OperatorGroupingFilter;
 import cern.ch.mathexplorer.lucene.analysis.filters.UnicodeNormalizingFilter;
 import cern.ch.mathexplorer.lucene.analysis.tokenizers.MultiplePatternTokenizer;
 import cern.ch.mathexplorer.mathematica.MathematicaConfig;
@@ -34,7 +34,7 @@ public final class SolrNormalizerNotationalAnalyzer extends SolrAnalyzer {
 			  MathematicaConfig.NORMALIZATION_MODE);
 	  TokenStream unicodeNormalizer = new UnicodeNormalizingFilter(source2);
 	  TokenStream numericRounder 	= new NumericalRoundingFilter(unicodeNormalizer);
-	  TokenStream relatedOperators 	= new SynonymExpandingFilter(numericRounder);
+	  TokenStream relatedOperators 	= new OperatorGroupingFilter(numericRounder);
 	  
 	  
 	  return new TokenStreamComponents(source2, relatedOperators);

### 2014-02-27 src/cern/ch/mathexplorer/lucene/analysis/analyzers/SolrNotationalAnalyzer.java

@@ -7,7 +7,7 @@ import org.apache.lucene.util.Version;
 import org.apache.solr.analysis.SolrAnalyzer;
 
 import cern.ch.mathexplorer.lucene.analysis.filters.NumericalRoundingFilter;
-import cern.ch.mathexplorer.lucene.analysis.filters.SynonymExpandingFilter;
+import cern.ch.mathexplorer.lucene.analysis.filters.OperatorGroupingFilter;
 import cern.ch.mathexplorer.lucene.analysis.filters.UnicodeNormalizingFilter;
 import cern.ch.mathexplorer.lucene.analysis.tokenizers.MultiplePatternTokenizer;
 import cern.ch.mathexplorer.utils.Regex;
@@ -30,7 +30,7 @@ public final class SolrNotationalAnalyzer extends SolrAnalyzer {
 	  Tokenizer source2 = new MultiplePatternTokenizer(reader, Regex.PATTERNS, Regex.GROUP);
 	  TokenStream unicodeNormalizer = new UnicodeNormalizingFilter(source2);
 	  TokenStream numericRounder 	= new NumericalRoundingFilter(unicodeNormalizer);
-	  TokenStream relatedOperators 	= new SynonymExpandingFilter(numericRounder);
+	  TokenStream relatedOperators 	= new OperatorGroupingFilter(numericRounder);
 	  
 	  
 	  return new TokenStreamComponents(source2, relatedOperators);

### 2014-02-27 src/cern/ch/mathexplorer/lucene/analysis/filters/OperatorGroupingFilter.java

@@ -39,11 +39,11 @@ import cern.ch.mathexplorer.utils.Constants.CHARACTER_CATEGORIES;
  * Integrals, Set theory.
  * http://symbolcodes.tlt.psu.edu/bylanguage/mathchart.html#fractions
  */
-public final class SynonymExpandingFilter extends TokenFilter {
+public final class OperatorGroupingFilter extends TokenFilter {
 
 	private final CharTermAttribute termAtt = addAttribute(CharTermAttribute.class);
 
-	public SynonymExpandingFilter(TokenStream input) {
+	public OperatorGroupingFilter(TokenStream input) {
 		super(input);
 	}
 		

### 2014-02-27 src/cern/ch/mathexplorer/mathematica/MathematicaEngine.java

@@ -163,9 +163,9 @@ public class MathematicaEngine {
 	 * If the method takes more than the defined timeout, the original string is returned 
 	 */
 	public String simplifyExpressionWithTimeout(String mathMLExpression, boolean full){
-		ExecutorService executor = Executors.newSingleThreadExecutor();
-        Future future = executor.submit(new MathematicaTask(mathMLExpression, TASK.SIMPLIFY_EXPRESSION, full));
         try {
+        	ExecutorService executor = Executors.newSingleThreadExecutor();
+        	Future future = executor.submit(new MathematicaTask(mathMLExpression, TASK.SIMPLIFY_EXPRESSION, full));
         	return (String) future.get(MathematicaConfig.TIMEOUT_TIME, MathematicaConfig.TIMEOUT_TIMEUNIT);
         } catch (TimeoutException te) {
         	ml.abortEvaluation();
@@ -352,9 +352,9 @@ public class MathematicaEngine {
 	}
 
 	public static void main(String[] args) throws Exception {
-		test();
+		testSimplifications();
 		
-		MathematicaEngine mi = getInstance("TESTING");
+		/**MathematicaEngine mi = getInstance("TESTING");
 		String expression = Constants.SAMPLE_EQ_5;
 		Console.print(expression);
 		List<StructuralPattern> features = mi.getPatterns(expression);
@@ -363,24 +363,31 @@ public class MathematicaEngine {
 		}
 		Console.print(mi.simplifyExpression(expression, false));
 		Console.print(mi.simplifyExpression(expression, true));
-
+		*/
+	}
+	
+	public static void testSimplifications() throws Exception {
+		File dataDir = new File("./data/arxiv_cds");
+		for (File f : dataDir.listFiles() ) {
+			BufferedReader br = new BufferedReader(new FileReader(f));
+			String line = "";
+			MathematicaEngine instance = getInstance("TESTING");
+			while ((line = br.readLine()) != null) {
+				String result1 = instance.simplifyExpressionWithTimeout(line, false);
+				String result2 = instance.simplifyExpressionWithTimeout(line, true);
+				if (!result1.equals(result2)) {
+					System.out.println(line);
+					System.out.println(result1);
+					System.out.println(result2);
+				}
+			}
+			System.out.println("checked file: " + f);
+			br.close();
+		}
 	}
 	
 	public static void test() throws Exception {
[…]

### 2014-02-27 src/cern/ch/mathexplorer/utils/Console.java

@@ -1,7 +1,7 @@
 package cern.ch.mathexplorer.utils;
 
 public class Console {
-	static boolean enabled = true;
+	static boolean enabled = false;
 	public static void print(Object o) {
 		if (enabled) {
 			System.out.println(o);

### 2014-02-27 src/cern/ch/mathexplorer/utils/Constants.java

@@ -203,13 +203,21 @@ public final class Constants implements Serializable {
 		EQUALS(new HashSet<>(Arrays.asList(
 				"=",	
 				"==",
-				"≡"
+				"≡",
+				"≠",
+				"≢",
+				"≞",	//Measured
+				"≝"	//Definition
+				
 				))),
+				
 		GREATER_THAN(new HashSet<>(Arrays.asList(
+				"≥",
 				">",	
 				"&gt;"
 				))),
 		SMALLER_THAN(new HashSet<>(Arrays.asList(
+				"≤",
 				"<",	
 				"&lt;"
 				))),		

### 2014-02-28 docs/thesis/chap-advanced_techniques.tex
added screenshots

\chapter{Advanced Techniques}
\label{chap-advances_techniques}

\section{Latent Semantic Indexing with Semantic Vectors}

\section{Latent Dirichlet Allocation with Apache Mahout}

### 2014-03-04 docs/thesis/chap-cern_math_explorer.tex
Work on thesis doc: Added intro section and status of MIR.

@@
 
-The two functions that are more relevant for our work are {\codefont Simplify} and {\codefont FullySimplify} since they apply most of the other combined methods and do not require additional information.
+The two functions that are more relevant for our work are {\codefont Simplify} and {\codefont FullySimplify} since they apply a combination of the other methods and do not require additional information.
 
-Table \ref{table_simplifications} presents some sample equations found in some the documents in CDS and the different forms of simplification.
+Table \ref{comparison_simplification} presents some sample equations found in some the documents in CDS and the different forms of simplification.
 
-\begin{tabular}{|>{\centering\arraybackslash}m{4cm}|>
-{\centering\arraybackslash}m{4cm}|>
-{\centering\arraybackslash}m{4cm}|}
+\begin{tabular}{|>{\centering\arraybackslash}m{4.5cm}|>
+{\centering\arraybackslash}m{4.5cm}|>
+{\centering\arraybackslash}m{4.5cm}|}
 \hline
@@
 \hline
+
+\scriptsize{\codefont <math> <mrow> <mrow> <mfrac> <mn>1</mn> <mn>2</mn> </mfrac> <mo>⁢</mo> <msup> <mi>x</mi> <mn>2</mn> </msup> <mo>⁢</mo> <mrow> <mi>log</mi> <mo>⁡</mo> <mrow> <mo>(</mo> <mrow> <mn>1</mn> <mo>-</mo> <msup> <mi>e</mi> <mrow> <mo>-</mo> <mrow> <mn>2</mn> <mo>⁢</mo> <mi>x</mi> </mrow> </mrow> </msup> </mrow> <mo>)</mo> </mrow> </mrow> </mrow> <mo>-</mo> <mrow> <mfrac> <mn>1</mn> <mn>2</mn> </mfrac> <mo>⁢</mo> <mi>x</mi> <mo>⁢</mo> <mi>L</mi> <mo>⁢</mo> <msub> <mi>i</mi> <mn>2</mn> </msub> <mo>⁢</mo> <mrow> <mo>(</mo> <msup> <mi>e</mi> <mrow> <mo>-</mo> <mrow> <mn>2</mn> <mo>⁢</mo> <mi>x</mi> </mrow> </mrow> </msup> <mo>)</mo> </mrow> </mrow> <mo>-</mo> <mrow> <mfrac> <mn>1</mn> <mn>4</mn> </mfrac> <mo>⁢</mo> <mi>L</mi> <mo>⁢</mo> <msub> <mi>i</mi> <mn>3</mn> </msub> <mo>⁢</mo> <mrow> <mo>(</mo> <msup> <mi>e</mi> <mrow> <mo>-</mo> <mrow> <mn>2</mn> <mo>⁢</mo> <mi>x</mi> </mrow> </mrow> </msup> <mo>)</mo> </mrow> </mrow> </mrow> </math> }      & \scriptsize{\codefont <math> <mrow> <mfrac> <mn>1</mn> <mn>4</mn> </mfrac> <mo>⁢</mo> <msup> <mi>e</mi> <mrow> <mrow> <mo>-</mo> <mn>2</mn> </mrow> <mo>⁢</mo> <mi>x</mi> </mrow> </msup> <mo>⁢</mo> <mrow> <mo>(</mo> <mrow> <mrow> <mn>2</mn> <mo>⁢</mo> <msup> <mi>x</mi> <mn>2</mn> </msup> <mo>⁢</mo> <msup> <mi>e</mi> <mrow> <mn>2</mn> <mo>⁢</mo> <mi>x</mi> </mrow> </msup> <mo>⁢</mo> <mrow> <mi>log</mi> <mo>⁡</mo> <mo>(</mo> <mrow> <mn>1</mn> <mo>-</mo> <msup> <mi>e</mi> <mrow> <mrow> <mo>-</mo> <mn>2</mn> </mrow> <mo>⁢</mo> <mi>x</mi> </mrow> </msup> </mrow> <mo>)</mo> </mrow> </mrow> <mo>-</mo> <mrow> <mn>2</mn> <mo>⁢</mo> <msub> <mi>i</mi> <mn>2</mn> </msub> <mo>⁢</mo> <mi>L</mi> <mo>⁢</mo> <mi>x</mi> </mrow> <mo>-</mo> <mrow> <msub> <mi>i</mi> <mn>3</mn> </msub> <mo>⁢</mo> <mi>L</mi> </mrow> </mrow> <mo>)</mo> </mrow> </mrow> </math> }    & \scriptsize{\codefont <math> <mrow> <mrow> <mfrac> <mn>1</mn> <mn>2</mn> </mfrac> <mo>⁢</mo> <msup> <mi>x</mi> <mn>2</mn> </msup> <mo>⁢</mo> <mrow> <mi>log</mi> <mo>⁡</mo> <mo>(</mo> <mrow> <mn>1</mn> <mo>-</mo> <msup> <mi>e</mi> <mrow> <mrow> <mo>-</mo> <mn>2</mn> </mrow> <mo>⁢</mo> <mi>x</mi> </mrow> </msup> </mrow> <mo>)</mo> </mrow> </mrow> <mo>-</mo> <mrow> <mfrac> <mn>1</mn> <mn>4</mn> </mfrac> <mo>⁢</mo> <mi>L</mi> <mo>⁢</mo> <msup> <mi>e</mi> <mrow> <mrow> <mo>-</mo> <mn>2</mn> </mrow> <mo>⁢</mo> <mi>x</mi> </mrow> </msup> <mo>⁢</mo> <mrow> <mo>(</mo> <mrow> <mrow> <mn>2</mn> <mo>⁢</mo> <msub> <mi>i</mi> <mn>2</mn> </msub> <mo>⁢</mo> <mi>x</mi> </mrow> <mo>+</mo> <msub> <mi>i</mi> <mn>3</mn> </msub> </mrow> <mo>)</mo> </mrow> </mrow> </mrow> </math>}     \\
+\scriptsize{ $\frac{1}{2} x^2 \log \left(1-e^{-2 x}\right) - \frac{1}{2} x L i_ 2 \left(e^{-2 x}\right)-\frac{1}{4} L i_ 3 \left(e^{-2 x}\right)$ }          & \scriptsize { \begin{multline}  \frac{1}{4} e^{-2 x} (2 x^2 e^{2 x} \log (1-e^{-2 x})- \notag\\ 2 i_ 2 L x-i_ 3 L)  \end{multline} } & \scriptsize{ $\frac{1}{2} x^2 \log \left(1-e^{-2 x}\right)-\frac{1}{4} L e^{-2 x} \left(2 i_ 2 x+i_ 3\right)$ }      \\
+
+\label{comparison_simplification}
 \end{tabular}
@@
 \includegraphics[height=4.2 cm]{visio_drawings/architecture.png}
-\label{comparison_sw_table}
+\label{system_arch}
 \caption{High level deployment architecture}
@@
 \includegraphics[height=8 cm]{figures/input_interface.png}
-\label{comparison_sw_table}
+\label{input_interface}
 \caption{Web interface of $5e^{x+y}$: Query input screen}
@@
 \includegraphics[height=8 cm]{figures/results_interface.png}
-\label{comparison_sw_table}
+\label{results_interface}
 \caption{Web interface of $5e^{x+y}$: Results screen}

### 2014-03-04 docs/thesis/chap-evaluation.tex
Work on thesis doc: Added intro section and status of MIR.

@@
 \chapter{Evaluation}
-...
+When building an IR system there are two main aspects that should be considered.
+One is the quality of the presented results and the second one is the performance of the system since web users currently tolerate some milliseconds of latency for retrieving results.
 
@@
 The machine used for experiments has a Intel Core i7 processor running at 3.4Ghz with 4 cores.
-The available RAM is 8Gb, and the Java Virtual Machine used for running Solr was run with the $-Xms2G -Xmx5G$ parameters.
+The available RAM is 8Gb, and the Java Virtual Machine used for running Solr was run with the {\codefont -Xms2G -Xmx5G} parameters.
 The complete specifications of the used software is presented in table \ref{sw_used}
@@
 
-We present results for three metrics: Partial precision (Document either partially relevant or completely relevant) strict precision and discounted cumulative gain.
+We present results for three metrics: Partial precision (Document either partially relevant or completely relevant) strict precision and discounted cumulative gain ($ \mathrm{DCG_{p}} = \sum_{i=1}^{p} \frac{ 2^{rel_{i}} - 1 }{ \log_{2}(i+1)} $).
 
 \section{Comparison against other systems}
-In this section we compared our implementation of MASE(CDS) with the public available systems presented in the related work chapter.
+In this section we compared our implementation of $5e^{x+y}$(CDS) with the public available systems presented in the related work chapter.
 We judged if the fetched results of each system were relevant or not using the same criteria as for the previous section.

### 2014-03-04 docs/thesis/chap-introduction.tex
work on document: added graphics
added section of dlmf
Work on thesis doc: Added intro section and status of MIR.

@@
 
-\section{CERN Document Server}
+\section{Context}
 
-\section{Invenio}
+\subsection{CERN}
+CERN (Conseil Europ\'{e}en pour la Recherche Nucl\'{e}aire or European Organization for Nuclear Research)\cite{CERN}, founded in 1952, is the biggest research center in the area of particle physics.
+It is located in the French-Swiss border, near Geneva.
+Even though CERN directly employs around 2400 people, more than 10000 scientist from around 113 countries have visited CERN to deepen their research.
+As an example of its contributions to science, recently, in July of 2012, CERN announced that two different experiments (ATLAS and CMS) confirmed the existence of the particle named Higgs Boson, which lead to the award of the Nobel Prize to Peter Higgs and Fran\c{c}ois Englert.
+
+Even though the main focus of CERN relies on the study of particle physics, the strong research environment has lead to important advances in several different areas, and one of the main inventions that CERN has contributed to the world is the Web.
+Tim Berners-Lee, in 1989, proposed a solution\cite{web_proposal} to the increasing problem of keeping track all the information related to the different experiments held at CERN, through a hypertext system.
+
+\subsection{CDS Invenio}
+CDS\cite{CDS1} (CERN Document Server) Invenio is the integrated digital library system developed and used at CERN\cite{CDS2}.
+To the date, it contains more than one million records and more than 400000 full-text documents.
+It provides tools to manage the complete workflow of a document taking care of the submission, annotation, edition, storage, searching, retrieval, displaying among other phases.
+Figure \ref{cds_screenshot} presents the search results for a simple query in CDS.
+
+\begin{figure}
+\centering
+\includegraphics[height=7 cm]{figures/cds_screenshot.png}
+\label{cds_screenshot}
+\caption{CDS search result interface}
+\end{figure}
+
+Invenio\cite{invenio} is the software running behind CDS and is an open source project developed in parallel to CDS at CERN.
+Besides CDS, Invenio also supports around thirty scientific institutions worldwide including Fermilab, SLAC National Laboratory, INSPIRE and EPFL.
+Invenio is composed of several modules where each one can be mapped to a specific step in the workflow of a record.
+Figure \ref{invenio_architecture} presents the global architecture of Invenio.
+A detailed explanation of each module can be accessed in\cite{invenio_modules}
+
+\begin{figure}
+\centering
+\includegraphics[height=10 cm]{figures/invenio.jpeg}
+\label{invenio_architecture}
+\caption{Invenio global architecture}
+\end{figure}
+
+\section{Project overview}
+\subsection{Motivation}
+The initial statement for this project was more generic and was encompassed as New ways to programmatically, accurately and efficiently extract data and metadata from digital files.
+During a first exploration around this topic, we focused our attention to the mathematical content that is stored in these files.
+After more discussions we identified that the extraction, storage, indexing and finally searching for mathematical content would be an and very useful project for CDS and an interesting research direction.
+CDS groups records in different categories or Collections such as Published Articles, Preprint, Photos, Books, General Talks among others.
+Some of these collections contain scientific documents in all of the different research areas where CERN is involved, and therefore a big amount of mathematical expressions are contained there.
+Only the Preprints collection contains 698581 records to the date, which harvest documents from services like ArXiV\cite{arxiv} where most of the documents are in the areas of physics, mathematics and statistics which are very rich in mathematical content.
+Currently Invenio provides different ways of searching for records by specifying metadata fields like author:"Albert Einstein" or by keywords.
+However, there is no way to search for a given mathematical expression.
+The current workarounds would be to try to search for the name of the given expression if it is common enough to have been named like \emph{Schr\"oodinger equation}.
+This approach most of the times is not enough since most of the equations are not named and even named ones can be rewritten in several ways and each one may have a different importance to the user.
+This combination of factors, motivates the development of a complete system that allows users to search for relevant documents, based on mathematical expressions.
+
+\subsection{Goals}
+
+The specific goals of this project can be summarized as:
+
+\begin{itemize}
+\item Explore ways to automatically extract the mathematical content from a document collection
+\item Investigate different approaches and formats to store mathematical expressions
+\item Identify relevant features in a mathematical expression and how to use them to index equations
+\item Using the created index, propose ways to efficiently retrieve relevant expressions and articles given an input query
+\item Implement the previous steps into a complete system (A search engine) and integrate it into the Invenio software
+\item Evaluate different approaches and the quality of the provided results
+\item Identify deficiencies in our work and propose solutions and further direction on work
+\end{itemize}

### 2014-03-04 docs/thesis/chap-related_work.tex
Added more characters/categories. Work on document: some drawings, graphics, and added comparison on simplification methods.
Work on thesis doc: Added intro section and status of MIR.

@@
 \chapter{Related Work}
-\label{chapter-related_work}
-\section{Status of MIR}
-\subsection{TREC}
-\subsection{TREC}
-\subsection{CLEF}
-\subsection{NTCIR}
+\label{chap-related_work}
+\section{Status of Mathematical Information Retrieval}
+Even though Information Retrieval has been a research field from around the 1950s where the first metrics for such systems were developed and in the 1960s where SMART (System for Mechanical Analysis and Retrieval of Text), the first computer based system was developed; only in the last couple years focus have been put into adapting the same techniques to mathematical content.
+
+The Mathematics Information Retrieval Workshop\cite{mir_worksop} held in the context of the Conference of Intelligent Computer Mathematics in July 2012, was the first official event in the area of MIR.
+Here, a small competition was held to evaluate different systems and approaches.
+
+The NII\cite{nii} (National Institute of Informatics) is a Japanese research institute that hosts the project named NTCIR (NII Testbeds and Community for Information access Research) which aims to build evaluation frameworks for specific sub-fields of information retrieval.
+On 2013, in the context of the 10th NTCIR conference, it hosted the NTCIR-10 Math Task \cite{math_task} which was the first collaborative effort to evaluate different systems.
+The Math task was focused on two different subtasks: Math retrieval (Identifying relevant document based on given mathematical expressions and/or keywords) and Math understanding where the idea was to extract natural language information of a mathematical expression in a document.
+Currently submissions are open for the NTCIR-11 Math Task 2 which will be held on December 2014.
+
 \section{Mathematical based search projects}
+
 \subsection{MIaS}
@@
 The system, also as most of the current projects, is developed by using the Apache Lucene framework. The system adapts the default scoring equation such that the given weight is taken into account.  
+Publicly available instances of the system can be found at: \url{http://aura.fi.muni.cz:8085/webmias/ps?n=-1} running on the MREC\cite{mrec} dataset and  \url{ http://aura.fi.muni.cz:8085/webmias-ntcir/} (Running on the NTCIR dataset)
+
 \subsection{EgoMath}
@@
 Some additional effort is done into splitting large mathematical blocks like tables into single mathematical expressions.
+At the start of this work, EgoMath was publicly available at \url{http://egomath.projekty.ms.mff.cuni.cz/}, however at this moment the system seems to be unavailable.
 
@@
 In the report published in 2013 \cite{dlmf2}, it is reported to have indexed around 38000 equations.
+This project is publicly available at \url{http://dlmf.nist.gov/}
 
@@
 It represents the equations as a tree an recursively generalizes each sub-expression.
+A public available instance of the system is available at \url{http://search.mathweb.org/tema/} which runs on the Zentralblatt Math database\cite{zb}.
 
@@
 
-\section{Other related projects and initiatives}
-\subsection{arXMLiv}
-\thispagestyle{empty}
+Other systems that provide similar search functionalities are \url{Uniquation} and \url{http://www.symbolab.com/}, however detailed information about the systems are not provided.
+Finally Wolfram Alpha\cite{wolframalpha} is a very powerful tool that allows to find information about lots of mathematical concepts and a wide variety of other objects (Even pokemons).

### 2014-03-04 src/cern/ch/mathexplorer/servlets/InputServlet.java

@@ -8,7 +8,7 @@ import javax.servlet.http.HttpServlet;
 import javax.servlet.http.HttpServletRequest;
 import javax.servlet.http.HttpServletResponse;
 
-import cern.ch.mathexplorer.core.MathExplorer;
+import cern.ch.mathexplorer.standalone.MathExplorer;
 import cern.ch.mathexplorer.utils.Constants;
 
 /**

### 2014-03-04 src/cern/ch/mathexplorer/servlets/QueryServlet.java

@@ -10,8 +10,8 @@ import javax.servlet.http.HttpServlet;
 import javax.servlet.http.HttpServletRequest;
 import javax.servlet.http.HttpServletResponse;
 
-import cern.ch.mathexplorer.core.EquationResult;
-import cern.ch.mathexplorer.core.MathExplorer;
+import cern.ch.mathexplorer.standalone.EquationResult;
+import cern.ch.mathexplorer.standalone.MathExplorer;
 
 /**
  * Servlet implementation class QueryServlet

### 2014-03-04 src/cern/ch/mathexplorer/standalone/EquationResult.java

@@ -1,4 +1,4 @@
-package cern.ch.mathexplorer.core;
+package cern.ch.mathexplorer.standalone;
 
 import java.io.Serializable;
 

### 2014-03-04 src/cern/ch/mathexplorer/standalone/MathExplorer.java

@@ -1,4 +1,4 @@
-package cern.ch.mathexplorer.core;
+package cern.ch.mathexplorer.standalone;
 
 import java.io.BufferedReader;
 import java.io.File;
@@ -46,12 +46,12 @@ import org.apache.lucene.util.Version;
 import uk.ac.ed.ph.snuggletex.SnuggleEngine;
 import uk.ac.ed.ph.snuggletex.SnuggleInput;
 import uk.ac.ed.ph.snuggletex.SnuggleSession;
-import cern.ch.mathexplorer.core.EquationResult.EquationBuilder;
 import cern.ch.mathexplorer.lucene.analysis.VecTextField;
 import cern.ch.mathexplorer.lucene.analysis.analyzers.SolrNotationalAnalyzer;
 import cern.ch.mathexplorer.lucene.analysis.analyzers.SolrNormalizerNotationalAnalyzer;
 import cern.ch.mathexplorer.lucene.analysis.analyzers.SolrStructuralAnalyzer;
 import cern.ch.mathexplorer.lucene.query.MathQueryParser;
+import cern.ch.mathexplorer.standalone.EquationResult.EquationBuilder;
 import cern.ch.mathexplorer.utils.Console;
 import cern.ch.mathexplorer.utils.Constants;
 import cern.ch.mathexplorer.utils.Constants.MATH_FIELD;

### 2014-03-04 src/cern/ch/mathexplorer/webbeans/MathBean.java

@@ -14,8 +14,8 @@ import javax.faces.context.FacesContext;
 import javax.faces.model.SelectItem;
 import javax.servlet.ServletContext;
 
-import cern.ch.mathexplorer.core.EquationResult;
-import cern.ch.mathexplorer.core.MathExplorer;
+import cern.ch.mathexplorer.standalone.EquationResult;
+import cern.ch.mathexplorer.standalone.MathExplorer;
 import cern.ch.mathexplorer.utils.Constants;
 
 @ManagedBean(name="mathBean")

### 2014-03-05 docs/thesis/chap-evaluation.tex
work on document: added the quality results

@@
 From the given dataset, the simpler equations were filtered out (The ones containing one or two elements).
+The total number of indexed equations is 1412297.
 
@@
 
-\begin{longtable}{|m{2cm}|>
+\begin{longtable}{|m{4cm}|>
 {\centering\arraybackslash}m{4cm}|>
@@
 
-\section{Results quality}
+\section{Quality resukts}
 In this section we are interested in evaluating the quality of the results provided by our system.
@@
 
-\subsection{Equations}
 The evaluated queries were provided by physics experts working at CERN from their own research topics. The queries were provided in \LaTeX format as the users used them in their own publications.
@@
 
+For each metric we compared three different scenarios:
+
+\begin{itemize}
+\item N : Only notational features over the original expression were used
+\item N+S : Notational and structural features over the original expression
+\item N+S+NN : Notational and structural features over the original expression and notational features over the normalized string using Mathematica's Simplify function
+\end{itemize}
+
 We present results for three metrics: Partial precision (Document either partially relevant or completely relevant) strict precision and discounted cumulative gain ($ \mathrm{DCG_{p}} = \sum_{i=1}^{p} \frac{ 2^{rel_{i}} - 1 }{ \log_{2}(i+1)} $).
 
-\section{Comparison against other systems}
-In this section we compared our implementation of $5e^{x+y}$(CDS) with the public available systems presented in the related work chapter.
-We judged if the fetched results of each system were relevant or not using the same criteria as for the previous section.
-The systems were tested using Firefox 26.0
-Table \ref{comparison_sw_table} presents the results of our test.
+\begin{longtable}{|c|c|c|c|}
+\hline 
+\textbf{Scenario} & \textbf{Top 5} & \textbf{Top 10} & \textbf{Top 20} \\ 
+\hline 
+N & 0.84 & 0.77 & 0.76 \\ 
+\hline 
+N+S & 0.89 & 0.83 & 0.74 \\ 
+\hline 
+N+S+NN & 0.91 & 0.93 & 0.87 \\ 
+\hline 
+\caption{Loose Precision}
+\label{loose_precision}
+\end{longtable}
 
-\begin{figure}
-\includegraphics[height=15 cm]{figures/comparison_table.png}
-\label{comparison_sw_table}
-\caption{Results of comparison of available mathematical search systems}
-\end{figure}
+\begin{longtable}{|c|c|c|c|}
+\hline 
+\textbf{Scenario} & \textbf{Top 5} & \textbf{Top 10} & \textbf{Top 20} \\ 
+\hline 
+N & 0.73 & 0.57 & 0.46 \\ 
+\hline 
+N+S & 0.82 & 0.67 & 0.52 \\ 
+\hline 
+N+S+NN & 0.82 & 0.81 & 0.62 \\ 
+\hline 
+\caption{Strict Precision}
+\label{stric_precision}
+\end{longtable}
 
-The first result about this evaluation is that only two different instances developed and running. The other ones seems to have been abandoned.
+\begin{longtable}{|c|c|c|c|}
+\hline 
+\textbf{Scenario} & \textbf{Top 5} & \textbf{Top 10} & \textbf{Top 20} \\ 
+\hline 
+N & 6.99 & 9.39 & 12.07 \\ 
+\hline 
+N+S & 7.47 & 10.83 & 13.87 \\ 
+\hline 
+N+S+NN & 7.53 & 11.61 & 15.80 \\ 
+\hline 
+\caption{Discounted Cumulative Gain}
+\label{loose_precision}
+\end{longtable}
 
@@
 Our four scenarios were organized as follows:
-\begin{itemize}
-\item N : Only notational features over the original expression were used
-\item N+S : Notational and structural features over the original expression
-\item N+S+NN : Notational and structural features over the original expression and notational features over the normalized string using Mathematica's Simplify function
-\item N+S+FN : Notational and structural features over the original expression and notational features over the normalized string using Mathematica's Full Simplify function
-\end{itemize}
+We tested the same three scenarios as for the quality results and we added a fourth one N+S+FN where we used the fully normalized form of the expressions as opposed to the standard simplified form in the N+S+NN scenario.
 

### 2014-03-05 docs/thesis/chap-evaluation.tex
typo quality resukts

@@
 
-\section{Quality resukts}
+\section{Quality results}
 In this section we are interested in evaluating the quality of the results provided by our system.
@@
 \end{itemize}
+
+We also were interested in also using the Fully Simplify function in Mathematica but we found no difference between both forms and the results were the same.
 
@@
 
-%%
-%\begin{longtable}{|m{3.5cm}|>
-%{\centering\arraybackslash}m{3cm}|>
-%{\centering\arraybackslash}m{3cm}|>
-%{\centering\arraybackslash}m{5cm}|
-%}
-%\hline 
-%\textbf{\LaTeX} & 
-%\textbf{Presentation MathML} & 
-%\textbf{Content MathML + Presentation Markups} & 
-%\textbf{OpenMath}  \\ \hline
-%%%
-
 \begin{longtable}{|>{\centering\arraybackslash}m{3.5cm}|>

### 2014-03-10 docs/thesis/chap-advanced_techniques.tex
wrote clusring results work on document

@@
-\chapter{Advanced Techniques}
-\label{chap-advances_techniques}
+\chapter{Further Data Analysis}
+\label{chap-data_analysis}
 
-\section{Latent Semantic Indexing with Semantic Vectors}
+In parallel to the development of $5e^{x+y}$ we perform some analysis over our datasets to have a better understanding of the data.
+Even though this series of analysis did were not directly introduced into the codebase of the system, they provide valuable insights and allowed us to identify future directions of work.
+
+\section{Clustering}
+
+We used Apache Mahout v0.9 for performing the clustering task. 
+The following set of commands were used to create and analyse our dataset:
+
+To convert the solr index to a mahout compatible format (Mahout vector):
+
+\small{{\codefont ./mahout lucene.vector -d <path to solr index>  -o ../results/vectors -t ../results/dict -f math           \_notational\_field -st ../results/dict\_seq -x 20 -md 2 -w TFIDF -n 2}}
+
+To run the canopy clustering on the data:
+
+\small{{\codefont ./mahout canpoy -t1 0.15 -t2 0.1 -i ../results/vectors -o ../results/clustering/canopy -dm org.apache.mahout.common.distance.CosineDistanceMeasure}}
+
+To run k-means algorithm on the resulting canopies:
+
+\small{{\codefont ./mahout kmeans -i ../results/vectors -o ../results/clustering\_kmeans -xm sequential  -c ../results/clustering/canopy -x 50 -cd 0.1 -cl -dm org.apache.mahout.common.distance.CosineDistanceMeasure}}
+
+To get the resulting points with their assigned cluster in a human readable format:
+\small{{\codefont ./mahout seqdumper -i ../results/clustering\_kmeans/clusteredPoints/part-m-0 > ../results/clustering\_kmeans/clusteredPoints/cluster-points.txt}}
+
+Since the estimation of a good number of clusters k is a challenging task, we also tried to estimate it  by evaluating intra and inter cluster distances for different values of k.
+Table \ref{cluster_measurements} shows that around k=500 the inter-cluster distance begins to remain stable and by increasing k to 1024, its value is affected only by less than 1\% indicating that a good k number is around 500.
+
+\begin{longtable}{|c|c|c|}
+\hline 
+\textbf{K} & \textbf{Average Intra-cluster distance} & \textbf{Average Inter-cluster distance} \\ 
+\hline 
+2 & 0.916 & 0.376  \\ \hline 
+4 & 0.907 & 0.557  \\ \hline 
+8 & 0.881 & 0.538  \\ \hline 
+16 & 0.859 & 0.628  \\ \hline 
+32 & 0.818 & 0.781  \\ \hline 
+64 & 0.772 & 0.833  \\ \hline 
+128 & 0.732 & 0.910  \\ \hline 
+256 & 0.694 & 0.938  \\ \hline 
+512 & 0.655 & 0.955  \\ \hline 
+1024 & 0.610 & 0.963  \\ \hline 
+\caption{Cluster measurements for different values of k}
+\label{cluster_measurements}
+\end{longtable}
+
+The resulting clusters can help us to identify common structures and further improve our results by either adding frequent structures that are common to a cluster, or by reducing the number of elements to perform comparisons against and allow to speed-up the querying process.
+Table \ref{} shows the top terms in 2 different clusters that were identified.
+By simple inspection, it is possible to identify the first one as a cluster grouping trigonometric expressions (Sines and Cosines) and the second one grouping limits where the variable goes to infinity.
+
+{\footnotesize
+\begin{longtable}{|>{\centering\arraybackslash}m{3.5cm}c|>{\centering\arraybackslash}m{3.5cm}c|}
+\hline 
+\textbf{Term} & \textbf{Relative frequence} & \textbf{Term} & \textbf{Relative frequence} \\ 
+\hline 
+<mi>cos</mi> <mo></mo>	&0.163661208&		<mi>∞</mi>&	0.233151718\\ \hline 
+<mi>cos</mi>&	0.157439621	&	<mo>→</mo> <mi>∞</mi>&	0.108867782\\ \hline 
+<mo></mo>&	0.121893736&		<mo>→</mo>&	0.108017583\\ \hline 
+<mi>θ</mi>&	0.097241797&		<mo>ARROWS</mo>&	0.105854015\\ \hline 
+<mo></mo> <mi>θ</mi>&	0.095168449&		<mo>-</mo> <mi>∞</mi>&	0.105012368\\ \hline 
+<mrow> <mi>cos</mi> <mo>⁡</mo> <mi>θ</mi> </mrow>&	0.088535288&		<mrow> <mo>-</mo> <mi>∞</mi> </mrow>&	0.102411785\\ \hline 
+<mi>cos</mi> <mo></mo> <mi>θ</mi> &	0.088535288&		<mrow> <mo>+</mo> <mi>∞</mi> </mrow>&	0.055650946\\ \hline 
+<mi>sin</mi> <mo></mo>&	0.068049679&		<mo>+</mo> <mi>∞</mi>&	0.055490528\\ \hline 
+<mi>sin</mi>&	0.066531563&		<mrow> <mrow> <mo>-</mo> <mi>∞</mi> </mrow>&	0.043459138\\ \hline 
+<mrow> <mi>sin</mi> <mo></mo> <mi>θ</mi> </mrow>&	0.032338911&		<mo>,</mo> <mi>∞</mi> & 0.021523067\\ \hline 
+<mi>sin</mi> <mo></mo> <mi>θ</mi> &	0.032338911&		<mrow> <mo>(</mo> <mrow> <mrow> <mo>-</mo> <mi>∞</mi> </mrow> &	0.020583379\\ \hline 
+<mi>φ</mi>&	0.031248212&		<mi>t</mi> <mo>→</mo>&	0.016400033\\ \hline 
+<mi>ϕ</mi>&	0.019359824&		<mrow> <mo>[</mo> <mrow> <mrow> <mo>-</mo> <mi>∞</mi> </mrow>& 0.01478247\\ \hline 
+<mi></mi>&	0.018438684&		<mi>t</mi>&	0.014620022\\ \hline 
+<mo></mo> <mi>ϕ</mi> & 0.017617149 & <mrow> <mo>$\pm$ </mo ><mi>∞ </mi> </mrow> & 0.014477746\\ \hline 
+<mrow> <mrow> <mi>cos</mi> <mo></mo> <mi>θ</mi> </mrow>&	0.016889963& <mo>$\pm$</mo> <mi>$\infty$</mi>& 0.014348642\\ \hline 
+<mi>cos</mi> <mo></mo> <mi>ϕ</mi>&	0.016157276	&	<mo>|</mo>&	0.012372129\\ \hline 
+<mrow> <mi>cos</mi> <mo></mo> <mi>ϕ</mi> </mrow> &	0.016157276	&	<mo>lim</mo>&	0.012214223\\ \hline 
+<mo>φ</mo>&	0.015344056 &		<mi>C</mi>	& 0.010421859\\ \hline 
+<mi>α</mi>&	0.014598769 &		<mo>∈</mo>	& 0.009871146\\ \hline
+
+\caption{Top 20 terms for two different identified clusters }
+\label{cluster_measurements}
+\end{longtable} 
+}
 

### 2014-03-10 docs/thesis/chap-evaluation.tex
wrote clusring results work on document

@@
 The type of queries that $5e^{x+y}$ was designed for, are typical equations that can be found in a physics scientific publication. 
-Out main user case is that a user of CDS is interested in finding documents inside the collection whose equations are related to the one that is provided.
+Our main user case is that a user of CDS is interested in finding documents inside the collection whose equations are related to the one that is provided.
 
 The evaluated queries were provided by physics experts working at CERN from their own research topics. The queries were provided in \LaTeX format as the users used them in their own publications.
-Table \ref{equations_table} presents the set of queries that were evaluated, and a simple explanation about it. 
+Table \ref{equations_table} presents the set of queries that were evaluated, and a simple explanation about each one. 
 Each of the users evaluated the results only for the equations he/she provided.
@@
 \item N+S+NN : Notational and structural features over the original expression and notational features over the normalized string using Mathematica's Simplify function
+\item N+S+NN (BM25): Same scenario as before but using BM25 similarity function instead of TF-IDF. This scoring function is implemented in Lucene through the class {\codefont BM25Similarity}
 \end{itemize}
@@
 
-We present results for three metrics: Partial precision (Document either partially relevant or completely relevant) strict precision and discounted cumulative gain ($ \mathrm{DCG_{p}} = \sum_{i=1}^{p} \frac{ 2^{rel_{i}} - 1 }{ \log_{2}(i+1)} $).
+We present results for three metrics: Partial precision (Document either partially relevant or completely relevant) strict precision and discounted cumulative gain ($ \mathrm{DCG_{p}} = \sum_{i=1}^{p} \frac{ 2^{rel_{i}} - 1 }{ \log_{2}(i+1)} $) which measures, in addition, the order of the results..
 
@@
 \hline 
-N & 0.84 & 0.77 & 0.76 \\ 
+N & 0.86 & 0.79 & 0.0.78 \\ 
 \hline 
-N+S & 0.89 & 0.83 & 0.74 \\ 
+N+S & 0.9 & 0.85 & 0.77 \\ 
 \hline 
-N+S+NN & 0.91 & 0.93 & 0.87 \\ 
+N+S+NN & 0.92 & 0.94 & 0.88 \\ 
 \hline
+N+S+NN (BM25) & 0.92 & 0.94 & 0.87 \\ 
+\hline
+
 \caption{Loose Precision}
@@
 \hline 
-N & 0.73 & 0.57 & 0.46 \\ 
+N & 0.76 & 0.61 & 0.50 \\ 
 \hline 
-N+S & 0.82 & 0.67 & 0.52 \\ 
+N+S & 0.84 & 0.70 & 0.56 \\ 
 \hline 
-N+S+NN & 0.82 & 0.81 & 0.62 \\ 
+N+S+NN & 0.84 & 0.83 & 0.65 \\ 
 \hline 
+N+S+NN (BM25) & 0.84 & 0.83 & 0.67 \\ 
+\hline
+
 \caption{Strict Precision}
@@
 \hline 
-N & 6.99 & 9.39 & 12.07 \\ 
+N & 7.17 & 9.81 & 12.00 \\ 
 \hline 
-N+S & 7.47 & 10.83 & 13.87 \\ 
+N+S & 7.61 & 10.7 & 14.59 \\ 
 \hline 
-N+S+NN & 7.53 & 11.61 & 15.80 \\ 
+N+S+NN & 7.66 & 11.81 & 16.32 \\ 
+\hline 
+N+S+NN (BM25) & 7.66 & 11.82 & 16.42 \\ 
 \hline
 \caption{Discounted Cumulative Gain}
-\label{loose_precision}
+\label{dcg}
 \end{longtable}
 
-\section{Querying Performance}
+Results show that for the selected queries, the system performs reasonably well achieving a precision of 0.84 in the top 5 results in the best scenario and 0.65 in the top 20 results. 
+Even more important than the absolute values, it is more interesting to see how the addition of structural features and the addition of normalization to the expressions, allows the system to improve its performance reasonably.
+In the top 20 results there was an increase of 15\% from the N scenario to the N+S+NN one.
+Also we see that in the case of the top 5 results going from N+S to N+S+NN resulted in the same strict precision of 0.84, it still represented and increase in the DCG metric which means still results were improved.
+A final remark is that there was not a significant difference between the two different similarity functions that were evaluated, and in at least one case, BM25 performed worse than standard tf-idf.
 
@@
 
-\begin{longtable}{|c|c|p{2cm}|p{2cm}|p{2cm}|}
+\begin{longtable}{|c|c|>
+{\centering\arraybackslash}m{2cm}|>
+{\centering\arraybackslash}m{2cm}|>
+{\centering\arraybackslash}m{2cm}|}
 \hline 
-Feature Set & Total time (sec) & Index Size (kb) & Avg. time per equation & Avg. size of equation (kb) \\ 
+\textbf{Feature Set} & \textbf{Total time (sec)} & \textbf{Index Size (kb)} & \textbf{Avg. time per equation} & \textbf{Avg. size of equation (kb)} \\ 
 \hline 
@@
 
+\section{Querying Performance}
+Similarly, we were also interested in evaluating how the query performance of the queries was affected with the different scenarios.
+For this set of queries we used the complete dataset, and evaluated the N and the N+S+NN scenarios for queries of different length.
+
+\begin{longtable}{|>{\centering\arraybackslash}m{5cm}|>
+{\centering\arraybackslash}m{4cm}|>
+{\centering\arraybackslash}m{4cm}|
+}
+\hline 
+\textbf{Expression Length(Number of characters in MathML)}& \textbf{N} & \textbf{N+S+NN} \\ \hline 
+70 & 0.178 & 0.327  \\ \hline
+198 & 0.179 & 0.810  \\ \hline
+452 & 0.323 & 1.692  \\ \hline
+771 & 0.393 & 2.066  \\ \hline
+
+\caption{Query performance in seconds}
+\label{query_performance}
+\end{longtable}
+
+Table \ref{query_performance} shows that for smaller queries, the querying time increases from an average of 0.178 seconds to 0.327 which represents an increase of 83\%.
+For the largest evaluated set of queries, the querying time passed from 0.393 to 2.066 seconds which represents an increase of around 425\%.
+The absolute values, however, show that in the worst case the slower query took a little more than 2 seconds in average which is still acceptable for a specialized search engine.
+
 \section{Alternative Metrics}
@@
 
-\begin{longtable}{|>{\centering\arraybackslash}m{3.5cm}|>
-{\centering\arraybackslash}m{3cm}|>
-{\centering\arraybackslash}m{3cm}|
+\begin{longtable}{|>{\centering\arraybackslash}m{5cm}|>
+{\centering\arraybackslash}m{4cm}|>
+{\centering\arraybackslash}m{4cm}|
 }
 \hline 
-Expression Length (Number of leaf nodes)& Angular Distance Time (msec) & Tree Edit Distance Time(msec) \\ \hline 
+\textbf{Expression Length (Number of leaf nodes)}& \textbf{Angular Distance Time (msec)} & \textbf{Tree Edit Distance Time(msec)} \\ \hline 
 3 & 0.01195 & 2.65  \\ \hline

### 2014-03-10 docs/thesis/chap-technical_considerations.tex
wrote clusring results work on document

--- 2014-02-21 docs/thesis/chap-technical_considerations.tex
@@
 
-\begin{longtable}{|m{3.5cm}|>
+\begin{longtable}{|>{\centering\arraybackslash}m{3.5cm}|>
 {\centering\arraybackslash}m{3cm}|>
@@
 
-\begin{longtable}{|
-m{2.8cm}|>{\centering\arraybackslash}
-m{2cm}|>{\centering\arraybackslash}
-m{1.65cm}|>{\centering\arraybackslash}
-m{1.65cm}|>{\centering\arraybackslash}
-m{1.65cm}|>{\centering\arraybackslash}
-m{1.95cm}|>{\centering\arraybackslash}
-m{1.65cm}|>{\centering\arraybackslash}
-m{1.65cm}|
+\begin{longtable}{|>{\centering\arraybackslash}
+m{2.93cm}|>{\centering\arraybackslash}
+m{1.8cm}|>{\centering\arraybackslash}
+m{1.6cm}|>{\centering\arraybackslash}
+m{1.9cm}|>{\centering\arraybackslash}
+m{1.6cm}|>{\centering\arraybackslash}
+m{1.8cm}|>{\centering\arraybackslash}
+m{1.4cm}|
 }
 \hline 
-\textbf{Software} & \textbf{Type} & \textbf{Tested version} & \textbf{Input Format(s)} & \textbf{Output Format(s)} & \textbf{Licence Type} & \textbf{Latest Update}  \\
+\small{\textbf{Software}} & \small{\textbf{Type}} & \small{\textbf{Tested version}} & \small{\textbf{Input Format(s)}} & \small{\textbf{Output Format(s)}} & \small{\textbf{Licence Type}} & \small{\textbf{Latest Update}}  \\
 \hline
-LaTeXML\cite{latexml} & Standalone Executable &0.7.9alpha & \LaTeX & XML + MathML & Open Source & 13 Feb 2014  \\
+\small{LaTeXML}\cite{latexml} & \small{Standalone Executable} & \small{0.7.9alpha} & \small{\LaTeX} & \small{XML + MathML} & \small{Open Source} & \small{13 Feb 2014}  \\
 \hline
-TeX4ht\cite{tex4ht1}\cite{tex4ht2} & Standalone Executable & 2009-01-31-07 & \LaTeX & XML + MathML & Open Source & 11 Jun 2009  \\
+\small{TeX4ht}\cite{tex4ht2} & \small{Standalone Executable} & \small{ 2009-01-31-07} & \small{\LaTeX} & \small{XML + MathML} & \small{ Open Source} & \small{11 Jun 2009}  \\
 \hline
-LaTeXmathML\cite{latexmathml} & Javascript Library & 30-October-2007 & \LaTeX & XML + MathML & Open Source & 30 Oct 2007  \\
+\small{SnuggleTex}\cite{snuggletex} & \small{Java Library} & \small{1.2.2} & \small{\LaTeX (Small fragments)} & \small{MathML} & \small{Open Source} & \small{24 May 2010}  \\
 \hline
-Maxtract\cite{maxtract1}\cite{maxtract2} & Standalone Executable & v.1752 & PDF & \LaTeX / Annotated PDF & Free to download & 15 Nov 2012  \\
+\small{LaTeXmathML}\cite{latexmathml} & \small{Javascript Library} & \small{30-October-2007} & \small{\LaTeX} & \small{XML + MathML} & \small{Open Source} & \small{30 Oct 2007}  \\
 \hline
-InftyReader\cite{infty1}\cite{infty2} & Standalone Executable (On Windows) & 2.9.6.2 & PDF, TIFF, BMP, GIF, PNG & \LaTeX, XML + MathML & Commercial & 22 Dec 2013  \\
+\small{Maxtract}\cite{maxtract1}\cite{maxtract2} & \small{Standalone Executable} & \small{v.1752} & \small{PDF} & \small{\LaTeX / Annotated PDF} & \small{Free to download} & \small{15 Nov 2012}  \\
+\hline
+\small{InftyReader}\cite{infty1}\cite{infty2} & \small{Standalone Executable (On Windows)} & \small{2.9.6.2} & \small{PDF, TIFF, BMP, GIF, PNG} & \small{\LaTeX, XML + MathML} & \small{Commercial} & \small{22 Dec 2013}  \\
 
@@
 
-\begin{longtable}{|m{2cm}|>
+\begin{longtable}{|>
 {\centering\arraybackslash}m{2cm}|>
-{\centering\arraybackslash}m{1.65cm}|>
-{\centering\arraybackslash}m{1.65cm}|>
-{\centering\arraybackslash}m{1.65cm}|>
-{\centering\arraybackslash}m{1.95cm}|>
-{\centering\arraybackslash}m{1.65cm}|>
-{\centering\arraybackslash}m{1.65cm}|
+{\centering\arraybackslash}m{2.1cm}|>
+{\centering\arraybackslash}m{1.9cm}|>
+{\centering\arraybackslash}m{1.55cm}|>
+{\centering\arraybackslash}m{1.83cm}|>
+{\centering\arraybackslash}m{1.95cm}|
 }
 \hline 
-\textbf{CAS} & 
-\textbf{Imports MathML} & 
-\textbf{Expression normalization} & 
-\textbf{Pattern Matching}  &
-\textbf{License Type}  &
-\textbf{Supported APIs}
+\textbf{\small{CAS}} & 
+\textbf{\small{Imports MathML}} & 
+\textbf{\small{Expression normalization}} & 
+\textbf{\small{Pattern Matching}}  &
+\textbf{\small{License Type}}  &
+\textbf{\small{Supported APIs}}
 \\
 \hline
-Maple &  Yes & Yes & Yes & Commercial & C, Java, VB \\ \hline
-MatLab (Symbolic Math Toolbox) & Experimental & Yes & Yes & Commercial & C/C++, Fortran \\ \hline
-Mathematica &  Yes & Yes & Yes & Commercial & C, Java, .NET \\ \hline 
-Maxima &  Experimental & Yes & Yes & Open Source  & C++, Java (External Project) \\ \hline
-SymPy & No & Yes & Yes & Open Source & Python \\ \hline
+\small{Maple} &  \small{Yes} & \small{Yes} & \small{Yes} & \small{Commercial} & \small{C, Java, VB} \\ \hline
+\small{MatLab (Symbolic Math Toolbox)} & \small{Experimental} & \small{Yes} & \small{Yes} & \small{Commercial} & \small{C/C++, Fortran} \\ \hline
+\small{Mathematica} & \small{Yes} & \small{Yes} & \small{Yes} & \small{Commercial} & \small{C, Java, .NET} \\ \hline 
+\small{Maxima} &  \small{Experimental} & \small{Yes} & \small{Yes} & \small{Open Source} & \small{C++, Java (External Project)} \\ \hline
+\small{SymPy} & \small{No} & \small{Yes} & \small{Yes} & \small{Open Source} & \small{Python} \\ \hline
 

### 2014-03-10 src/cern/ch/mathexplorer/mahout/MahoutTasks.java

@@ -1,0 +1,11 @@
+package cern.ch.mathexplorer.mahout;
+
+import javax.security.auth.login.Configuration;
+
+import org.apache.mahout.text.LuceneStorageConfiguration;
+
+public class MahoutTasks {
+	public static void main(String[] args) {
+		LuceneStorageConfiguration storageConfig = new LuceneStorageConfiguration();
+	}
+}

### 2014-03-10 docs/thesis/chap-related_work.tex
work on thesis

@@
 
-The Mathematics Information Retrieval Workshop\cite{mir_worksop} held in the context of the Conference of Intelligent Computer Mathematics in July 2012, was the first official event in the area of MIR.
+The Mathematics Information Retrieval Workshop\cite{mir_workshop} held in the context of the Conference of Intelligent Computer Mathematics in July 2012, was the first official event in the area of MIR.
 Here, a small competition was held to evaluate different systems and approaches.
@@
 Other systems that provide similar search functionalities are \url{Uniquation} and \url{http://www.symbolab.com/}, however detailed information about the systems are not provided.
-Finally Wolfram Alpha\cite{wolframalpha} is a very powerful tool that allows to find information about lots of mathematical concepts and a wide variety of other objects (Even pokemons).
+Finally Wolfram Alpha\cite{wolframalpha} is a very powerful tool that allows to find information about lots of mathematical concepts and a wide variety of other objects (Even Pokemon).

### 2014-03-10 src/cern/ch/mathexplorer/clusteranalysis/ClusterAnalyzer.java
more work on thesis

@@ -1,98 +1,0 @@
-package cern.ch.mathexplorer.clusteranalysis;
-
-import java.util.ArrayList;
-import java.util.List;
-
-import org.apache.hadoop.conf.Configuration;
-import org.apache.hadoop.fs.FileSystem;
-import org.apache.hadoop.fs.Path;
-import org.apache.hadoop.io.SequenceFile;
-import org.apache.hadoop.io.Writable;
-import org.apache.mahout.clustering.Cluster;
-import org.apache.mahout.clustering.cdbw.CDbwEvaluator;
-import org.apache.mahout.clustering.evaluation.ClusterEvaluator;
-import org.apache.mahout.clustering.iterator.ClusterWritable;
-import org.apache.mahout.common.distance.CosineDistanceMeasure;
-import org.apache.mahout.common.distance.DistanceMeasure;
-
-/**
- * Clusters created with:
- * ./mahout kmeans 
- * -i ../results/vectors 
- * -o ../results/clustering_kmeans/k256 
- * -xm sequential 
- * -k 256 
- * --clusters ../results/clustering_kmeans/k256 
- * -x 50 
- * -cd 0.1 
- * -cl 
- * -dm org.apache.mahout.common.distance.CosineDistanceMeasure
- *
- */
-
-public class ClusterAnalyzer {
-	static List<Cluster> clusters = new ArrayList<Cluster>();
-
-	public static void main(String args[]) throws Exception {
-		int k = 2;
-		
-		String inputFile = "/home/cern/Desktop/Thesis/sw/mahout-distribution-0.9_2/results/clustering_kmeans/k"+k+""
-				+ "/clusters-2-final/";
-		for( int i = 0; i<k; i++) {
-			String ending = "part-0";
-			if(i<10){
-				ending += "000"+i;
-			} else if (i < 100) {
-				ending += "00"+i;
-			} else if (i < 1000) {
-				ending += "0" +i ;
-			}
-			
-			Configuration conf = new Configuration();
-			Path path = new Path(inputFile+ending);
-			System.out.println("Input Path: " + path);
-			FileSystem fs = FileSystem.get(path.toUri(), conf);
-			SequenceFile.Reader reader = new SequenceFile.Reader(fs, path, conf);
-			Writable key = (Writable) reader.getKeyClass().newInstance();
-			Writable value = (Writable) reader.getValueClass().newInstance();
-
-			while (reader.next(key, value)) {
-				Cluster cluster = ((ClusterWritable) value).getValue();
[…]

### 2014-03-10 docs/thesis/chap-cern_math_explorer.tex
wrote clusring results work on document
proofreading fixes

@@
 CDS already uses Solr as a search engine layer, so developing $5e^{x+y}$(CDS) using this technology supposed a reasonable choice.
-One of the main steps while building an IR tool, is understanding the data and what kind of features can be extracted from it: If the system is based on text, then tasks as stemming, handling of synonyms, misspelling and so on, such be taken into consideration; if the system being developed is based on images, then examples of features can be histograms of colors, geometrical features and so on.
+One of the main steps while building an IR tool, is understanding the data and what kind of features can be extracted from it: If the system is based on text, then tasks such as stemming, handling of synonyms, misspelling and so on, should be taken into consideration; if the system being developed is based on images, then examples of features can be histograms of colors, geometrical features and so on.
 During the literature review, we discovered that most of the projects handled the notational aspects of the expressions, that is, the real naming of the terms in a given equation and each project developed its own set of heuristics to handle the structural component.
@@
 <mi>, <mn>, <mo> tags), and simple constructs like subscript and superscript elements, fractions, roots.
-We also extract bi-grams and tri-grams as analogue to that is done for text indexing in current systems.
+We also extract bi-grams and tri-grams as an analogy to what is done for text indexing in current systems.
 
@@
 \subsubsection{Unicode Normalizing} 
-The first issue we discovered is that because of the big wide of different characters to represent the possible mathematical symbols, there is need for an automatic way to match different possible variations of a single character.
-An example of this situation is specification of an natural number, sometimes denoted by the letter N.
+The first issue we discovered is that because of the wide range of different characters to represent the possible mathematical symbols, there is need for an automatic way to match different possible variations of a single character.
+An example of this situation is the specification of an natural number, sometimes denoted by the letter N.
 In this case, at least three different common representations were identified: $ N = 1 $ (Using character with unicode code point 0x004e), $\mathcal{N} = 1$ (0xd835 0xdc41 or in latex expressed as \lstinline|\mathcal{N}|) and $\mathbb{N} = 1$ (0x2115 or in latex expressed as \lstinline|\mathbb{N}|).
 \\
-  For addressing this situation, we rely on the Unicode equivalence framework.
-In the unicode specification, sometimes the same character have two or more different code-points because of backwards compatibility with other encoding standards or because the same character has different essential meanings.
+  To address this situation, we rely on the Unicode equivalence framework.
+In the unicode specification, sometimes the same character has two or more different code-points because of backwards compatibility with other encoding standards or because the same character has different essential meanings.
 Another group of equal characters with different code-points are pre-combined characters such as the Latin letter \~{N} which has Unicode point 0x00D1 and also is the sequence of code-points 0x004E (Latin letter N) and 0x0303 (the combining character tilde).
@@
 
-Since our goal is to match as much as possible similar characters, our system employs the NFKD representation of a character.
+Since our goal is to match as many similar characters as possible, our system employs the NFKD representation of a character.
 For a given token, we test whether if it is already equal to its NFKD.
@@
 \subsubsection{Operator grouping}
-Even though the Unicode normalization step work for a big part of the cases presented in table \ref{unicode_characters}, there are still some groups of characters which would not be matched (Even partially), such as some types of integrals.
-For addressing these groups, a precomputed table was created for some general groups of operators which have some similar meaning.
+Even though the Unicode normalization step works for a big part of the cases presented in table \ref{unicode_characters}, there are still some groups of characters which would not be matched (even partially), such as some types of integrals.
+To address these groups, a precomputed table was created for some general groups of operators which have some similar meaning.
 For each token that belongs to some of this predefined groups, a second token is created identifying the group.
-For example the token <mo>{\unicodefont ∮}</mo> is expanded into <mo>{\unicodefont ∮}</mo><mo>INTEGRALS</mo>, similarly the token token <mo>{\unicodefont ∫}</mo> is expanded into <mo>{\unicodefont ∫}</mo><mo>INTEGRALS</mo> and then both will have a partial match in the INTEGRALS token.
-Unicode specification does not define a strict rule to group similar characters based on their semantics.
+For example the token <mo>{\unicodefont ∮}</mo> is expanded into <mo>{\unicodefont ∮}</mo><mo>INTEGRALS</mo>, similarly the token <mo>{\unicodefont ∫}</mo> is expanded into <mo>{\unicodefont ∫}</mo><mo>INTEGRALS</mo> and then both will have a partial match in the INTEGRALS token.
+The Unicode specification does not define a strict rule to group similar characters based on their semantics.
 For general operators, we used the grouping provided by Xah Lee in his website\cite{math_groups}.
@@
 \subsubsection{Numeric Approximation} 
-Some equations relate specific numeric quantities.
-While most of the previously explorer systems, handled <mn> tags by only representing them as a constant identifier, this approach is not suitable.
+Some equations relate to specific numeric quantities.
+While most of the previously explorer systems handled <mn> tags by only representing them as a constant identifier, this approach is not suitable.
 A lot of articles in CDS relate to specific experiments under certain conditions, and require a high level of precision in the measurements.
@@
 \subsection{Structural Features}
-The structure of a mathematical expression compliments the information that an be obtained over generic substructures where the naming of the variables is irrelevant.
+The structure of a mathematical expression compliments the information that can be obtained over generic substructures where the naming of the variables is irrelevant.
 
 \subsubsection{Algebraic structures}
-The first set of structures consist on purely algebraic relationships between the expressions.
-Inspired by predefined integral tables for different kinds of expressions, we decided to extract from a given equation, whether it has the occurrence of these kind of patterns.
+The first set of structures consists of purely algebraic relationships between the expressions.
+Inspired by predefined integral tables for different kinds of expressions, we decided to extract, from a given equation, whether it has an occurrence of these kinds of patterns or not.
 An example of this type of structures would be: $X\textunderscore*(X\textunderscore + A\textunderscore)$ where $X\textunderscore$ and $A\textunderscore$ can be any type of expression.
@@
 \subsubsection{Subscript/Superscript variations}
-This set of structures represent common operations that cat appear in a given expression, but its identification is based on notation factors.
+This set of structures represent common operations that can appear in a given expression, but its identification is based on notation factors.
 A simple example of this can be the matrix decomposition $A = VDV^{-1}$ where the actual name of the variables $A$ and $V$ is not meaningful but the real importance is the fact that a given variable appears alongside its inverse in a matrix multiplication form.
 We would like to assign a partial match to any other kind of this decomposition say $B = MRM^{-1}$.
-these types of structures live in-between the notational and structural categories but since we identify them using Mathematica, we encompass them as structural features.
+These types of structures live in-between the notational and structural categories but since we identify them using Mathematica, we encompass them as structural features.
 For this type of structures, we identify simple operations between an element and some possible variations of the same element with some subscript/superscript.
@@
 Additionally, there are common patterns to specific domains which can improve the quality of the retrieved results.
-Some specific patterns we identified include: $originalParticle \rightarrow subparticle1, subparticle2, subparticle3$ (For representing particle decaying processes) $S = \int^{t2}_{t1} \mathcal{L} dt$ (For an action in terms of its Lagrangian) and $SU(n)$ (For describing special unitary groups).
-The main drawback of this approach is the need to manually detect, implement and maintain long lists of patterns and for this reason we did not tried to do an exhaustive list of them.
+Some specific patterns we identified include: $originalParticle \rightarrow subparticle1, subparticle2, subparticle3$ (for representing particle decaying processes) $S = \int^{t2}_{t1} \mathcal{L} dt$ (for an action in terms of its Lagrangian) and $SU(n)$ (for describing special unitary groups).
+The main drawback of this approach is the need to manually detect, implement and maintain long lists of patterns and for this reason we did not try to assemble an exhaustive list.
 
@@
 
-Lucene framework defines some key concepts which ultimately are mapped into concrete classes.
+The Lucene framework defines some key concepts which ultimately are mapped into concrete classes.
 A {\codefont Document} is the minimum retrieval unit.
 For $5e^{x+y}$ we could either use a complete article as a document or a single equation.
-We choose the latter because it makes easier to focus on extracting features from a single equation.
+We choose the latter because it makes it easier to focus on extracting features from a single equation.
 A document contains a set of {\codefont fields} which represent different types of information that it can store.
@@
 An analyzer is a specific class that handles an element from a field and groups all the operations that are to be performed.
-For this purpose we wrote {\codefont SolrNotationalAnalyzer}, {\codefont SolrStructuralAnalyzer} and {\codefont SolrNormalizedNotationalAnalyzer}.
-The Solr prefix is added to make clear the fact that the class extends a {\codefont SolrAnalyzer} which extends a normal lucene {\codefont Analyzer}.
+For this purpose we implemented {\codefont SolrNotationalAnalyzer}, {\codefont SolrStructuralAnalyzer} and {\codefont SolrNormalizedNotationalAnalyzer}.
+The Solr prefix is added to clarify the fact that the class extends a {\codefont SolrAnalyzer} which extends a normal lucene {\codefont Analyzer}.
 
@@
 \item {\codefont SynonymExpandingFilter}: This class verifies if the received token belongs to a predefined category of elements and emits an additional token with it.
-\item {\codefont NumericalRoundingFilter}: This class process {\codefont <mn>} tokens.
+\item {\codefont NumericalRoundingFilter}: This class processes {\codefont <mn>} tokens.
 When a number contains a decimal part, it applies the standard rounding mode iteratively and for each one, it emits a token for each step.
@@
 \subsubsection{Error handling}
-Sometimes, after certain time, the connection between {\codefont KernelLink} and {\codefont Mathematica} will be lost launch an exception and following invocations would fails as well.
-Also, re-instantiating a KernelLink will yield an Exception.
+Sometimes, after certain time, the connection between {\codefont KernelLink} and {\codefont Mathematica} would be lost launching an exception and all following invocations would fail as well.
+Also, re-instantiating a KernelLink would yield an Exception.
 For this scenario, killing the associated processes to Mathematica was necessary with {\codefont killall -s 9 Mathematica; killall -s 9 MathKernel
@@
 In the ideal case we would be able to identify the malformed expressions and pass to Mathematica only well-formed equations to be processed but as this simple example shows, that is a very challenging task and may require more work.
-As a remedial situation, we used a fixed timeout to stop the processing of a given expression.
+As a remedial situation, we used a fixed timeout to stop the processing of such expressions.
 
@@
 
-A demo interface over the {\codefont pu} branch was developed to showcase the system, however to have a complete integration with CDS, a more deep work is required.
+A demo interface over the {\codefont pu} branch was developed to showcase the system, however to have a complete integration with CDS, more work is required.
 The demo setup employs the same dataset as used for experimentation.
@@
 \includegraphics[height=8 cm]{figures/input_interface.png}
-\label{input_interface}
+\label{input_int}
 \caption{Web interface of $5e^{x+y}$: Query input screen}
@@
 \includegraphics[height=8 cm]{figures/results_interface.png}
-\label{results_interface}
+\label{results_int}
 \caption{Web interface of $5e^{x+y}$: Results screen}

### 2014-03-10 docs/thesis/chap-introduction.tex
wrote clusring results work on document
proofreading fixes

@@
 To the date, it contains more than one million records and more than 400000 full-text documents.
-It provides tools to manage the complete workflow of a document taking care of the submission, annotation, edition, storage, searching, retrieval, displaying among other phases.
+It provides tools to manage the complete workflow of a document taking care of the submission, annotation, editing, storage, searching, retrieval, displaying among other phases.
 Figure \ref{cds_screenshot} presents the search results for a simple query in CDS.
@@
 Besides CDS, Invenio also supports around thirty scientific institutions worldwide including Fermilab, SLAC National Laboratory, INSPIRE and EPFL.
-Invenio is composed of several modules where each one can be mapped to a specific step in the workflow of a record.
+Invenio is composed of several modules, each one of which can be mapped to a specific step in the workflow of a record.
 Figure \ref{invenio_architecture} presents the global architecture of Invenio.
-A detailed explanation of each module can be accessed in\cite{invenio_modules}
+A detailed explanation of each module can be accessed in \cite{invenio_modules}
 
@@
 \subsection{Motivation}
-The initial statement for this project was more generic and was encompassed as New ways to programmatically, accurately and efficiently extract data and metadata from digital files.
+The initial statement for this project was more generic and was encompassed as "New ways to programmatically, accurately and efficiently extract data and metadata from digital files".
 During a first exploration around this topic, we focused our attention to the mathematical content that is stored in these files.
-After more discussions we identified that the extraction, storage, indexing and finally searching for mathematical content would be an and very useful project for CDS and an interesting research direction.
+After more discussions we identified that the extraction, storage, indexing and finally searching for mathematical content would be a very useful project for CDS and an interesting research direction.
 CDS groups records in different categories or Collections such as Published Articles, Preprint, Photos, Books, General Talks among others.
 Some of these collections contain scientific documents in all of the different research areas where CERN is involved, and therefore a big amount of mathematical expressions are contained there.
-Only the Preprints collection contains 698581 records to the date, which harvest documents from services like ArXiV\cite{arxiv} where most of the documents are in the areas of physics, mathematics and statistics which are very rich in mathematical content.
+Only the Preprints collection contains 698581 records to date, harvesting documents from services like ArXiV\cite{arxiv} where most of the documents are in the areas of physics, mathematics and statistics which are very rich in mathematical content.
 Currently Invenio provides different ways of searching for records by specifying metadata fields like author:"Albert Einstein" or by keywords.
@@
 \item Using the created index, propose ways to efficiently retrieve relevant expressions and articles given an input query
-\item Implement the previous steps into a complete system (A search engine) and integrate it into the Invenio software
+\item Implement the previous steps into a complete system (a search engine) and integrate it into the Invenio software
 \item Evaluate different approaches and the quality of the provided results
-\item Identify deficiencies in our work and propose solutions and further direction on work
+\item Identify deficiencies in our work and propose solutions and further directions
 \end{itemize}

### 2014-03-10 docs/thesis/chap-theoretical_background.tex
cleaned useless docs
proofreading fixes

@@
 \label{chapter-theoretical_background}
-Information Retrieval (IR) consists on the activity of identifying relevant documents from a collection based on some input parameters.
-Different models have been developed through the evolution of the field. In the subsequent sections, the most relevant to this work are presented.
+Information Retrieval (IR) consists of the activity of identifying relevant documents from a collection based on some input parameters.
+Different models have been developed through the evolution of the field. In the subsequent sections, the most relevant models to this work are presented.
 
@@
 
+\section{Latent Dirichlet Allocation}
+
 \section{Tree Edit Distance}

### 2014-03-11 src/cern/ch/mathexplorer/lucene/query/MathQueryParser.java
merge conflict

@@ -96,6 +96,7 @@ public class MathQueryParser extends QParser {
 
 	@Override
 	public Query parse() throws SyntaxError {
+		Long timeInit = System.currentTimeMillis(); 
 		aLogger.info("Query before: " + qstr);
 		qstr = Regex.cleanQuery(qstr);
 
@@ -139,7 +140,8 @@ public class MathQueryParser extends QParser {
 
 		}
 		query.setMinimumNumberShouldMatch(1);
-
+		Long timeEnd = System.currentTimeMillis();
+		System.out.println("Total processing time: " + (timeEnd - timeInit));
 		return returnQuery(query);
 	}
 
@@ -147,7 +149,7 @@ public class MathQueryParser extends QParser {
 		for (BooleanClause a : q.getClauses()) {
 			Console.print(a);
 		}
-
+		
 		return q;
 	}
 

### 2014-03-11 src/cern/ch/mathexplorer/clusteranalysis/ClusterAnalyzer.java
cluster analysis code
Conflicts:
	src/cern/ch/mathexplorer/clusteranalysis/ClusterAnalyzer.java

@@ -1,0 +1,132 @@
+package cern.ch.mathexplorer.clusteranalysis;
+
+import java.io.BufferedReader;
+import java.io.File;
+import java.io.FileReader;
+import java.util.ArrayList;
+import java.util.List;
+import java.util.Scanner;
+import java.util.regex.Matcher;
+import java.util.regex.Pattern;
+
+import org.apache.hadoop.conf.Configuration;
+import org.apache.hadoop.fs.FileSystem;
+import org.apache.hadoop.fs.Path;
+import org.apache.hadoop.io.SequenceFile;
+import org.apache.hadoop.io.Writable;
+import org.apache.mahout.clustering.Cluster;
+import org.apache.mahout.clustering.iterator.ClusterWritable;
+import org.apache.mahout.common.distance.CosineDistanceMeasure;
+import org.apache.mahout.common.distance.DistanceMeasure;
+
+/**
+ * Clusters created with:
+ * ./mahout kmeans 
+ * -i ../results/vectors 
+ * -o ../results/clustering_kmeans/k256 
+ * -xm sequential 
+ * -k 256 
+ * --clusters ../results/clustering_kmeans/k256 
+ * -x 50 
+ * -cd 0.1 
+ * -cl 
+ * -dm org.apache.mahout.common.distance.CosineDistanceMeasure
+ *
+ */
+
+public class ClusterAnalyzer {
+	static List<Cluster> clusters = new ArrayList<Cluster>();
+	static int k=1024;
+	public static void main(String args[]) throws Exception {
+		
+		
+		
+		computeInterClusterDistance();
+		computerIntraClusterDistance();
+				
+	}
+	
+	/**
+	 * Computer the average distance of the points with the centroid of the cluster it was assigned.
+	 * 
+	 */
+	static void computerIntraClusterDistance() throws Exception{
+		String filePath = "/home/cern/Desktop/Thesis/sw/mahout-distribution-0.9_2/results/clustering_kmeans/k"+k+
+				"/clusteredPoints/cluster-points.txt";
+		String number = "0\\.[0-9]*?";
+		Pattern numberPattern = Pattern.compile(number);
+		Pattern distancePattern = Pattern.compile("distance: "+number+" ");
+		BufferedReader br = new BufferedReader(new FileReader(new File(filePath)));
+		String line = "";
+		double sum = 0.0;
+		int count = 0;
+		while ((line=br.readLine())!=null) {
+			Matcher m = distancePattern.matcher(line);
+			
[…]

### 2014-03-11 docs/thesis/chap-advanced_techniques.tex
work on document: added conclussions, future work, general review.

@@
 <mo></mo>&	0.121893736&		<mo>→</mo>&	0.108017583\\ \hline 
-<mi>θ</mi>&	0.097241797&		<mo>ARROWS</mo>&	0.105854015\\ \hline 
-<mo></mo> <mi>θ</mi>&	0.095168449&		<mo>-</mo> <mi>∞</mi>&	0.105012368\\ \hline 
-<mrow> <mi>cos</mi> <mo>⁡</mo> <mi>θ</mi> </mrow>&	0.088535288&		<mrow> <mo>-</mo> <mi>∞</mi> </mrow>&	0.102411785\\ \hline 
+<mi>$\theta$</mi>&	0.097241797&		<mo>ARROWS</mo>&	0.105854015\\ \hline 
+<mo></mo> <mi>$\theta$</mi>&	0.095168449&		<mo>-</mo> <mi>∞</mi>&	0.105012368\\ \hline 
+<mrow> <mi>cos</mi> <mo>⁡</mo> <mi>$\theta$</mi> </mrow>&	0.088535288&		<mrow> <mo>-</mo> <mi>∞</mi> </mrow>&	0.102411785\\ \hline 
 <mi>cos</mi> <mo></mo> <mi>θ</mi> &	0.088535288&		<mrow> <mo>+</mo> <mi>∞</mi> </mrow>&	0.055650946\\ \hline 
@@
 <mrow> <mi>sin</mi> <mo></mo> <mi>θ</mi> </mrow>&	0.032338911&		<mo>,</mo> <mi>∞</mi> & 0.021523067\\ \hline 
-<mi>sin</mi> <mo></mo> <mi>θ</mi> &	0.032338911&		<mrow> <mo>(</mo> <mrow> <mrow> <mo>-</mo> <mi>∞</mi> </mrow> &	0.020583379\\ \hline 
-<mi>φ</mi>&	0.031248212&		<mi>t</mi> <mo>→</mo>&	0.016400033\\ \hline 
-<mi>ϕ</mi>&	0.019359824&		<mrow> <mo>[</mo> <mrow> <mrow> <mo>-</mo> <mi>∞</mi> </mrow>& 0.01478247\\ \hline 
+<mi>sin</mi> <mo></mo> <mi>$\theta$</mi> &	0.032338911&		<mrow> <mo>(</mo> <mrow> <mrow> <mo>-</mo> <mi>∞</mi> </mrow> &	0.020583379\\ \hline 
+<mi>$\phi$</mi>&	0.031248212&		<mi>t</mi> <mo>→</mo>&	0.016400033\\ \hline 
+<mi>$\Phi$</mi>&	0.019359824&		<mrow> <mo>[</mo> <mrow> <mrow> <mo>-</mo> <mi>∞</mi> </mrow>& 0.01478247\\ \hline 
 <mi></mi>&	0.018438684&		<mi>t</mi>&	0.014620022\\ \hline 
-<mo></mo> <mi>ϕ</mi> & 0.017617149 & <mrow> <mo>$\pm$ </mo ><mi>∞ </mi> </mrow> & 0.014477746\\ \hline 
+<mo></mo> <mi>$\Phi$</mi> & 0.017617149 & <mrow> <mo>$\pm$</mo > <mi>∞</mi> </mrow> & 0.014477746\\ \hline 
 <mrow> <mrow> <mi>cos</mi> <mo></mo> <mi>θ</mi> </mrow>&	0.016889963& <mo>$\pm$</mo> <mi>$\infty$</mi>& 0.014348642\\ \hline 
-<mi>cos</mi> <mo></mo> <mi>ϕ</mi>&	0.016157276	&	<mo>|</mo>&	0.012372129\\ \hline 
-<mrow> <mi>cos</mi> <mo></mo> <mi>ϕ</mi> </mrow> &	0.016157276	&	<mo>lim</mo>&	0.012214223\\ \hline 
-<mo>φ</mo>&	0.015344056 &		<mi>C</mi>	& 0.010421859\\ \hline 
-<mi>α</mi>&	0.014598769 &		<mo>∈</mo>	& 0.009871146\\ \hline
+<mi>cos</mi> <mo></mo> <mi>$\Phi$</mi>&	0.016157276	&	<mo>|</mo>&	0.012372129\\ \hline 
+<mrow> <mi>cos</mi> <mo></mo> <mi>$\Phi$</mi> </mrow> &	0.016157276	&	<mo>lim</mo>&	0.012214223\\ \hline 
+<mo>$\phi$</mo>&	0.015344056 &		<mi>C</mi>	& 0.010421859\\ \hline 
+<mi>$\alpha$</mi>&	0.014598769 &		<mo>$\in$</mo>	& 0.009871146\\ \hline
 

### 2014-03-11 docs/thesis/chap-cern_math_explorer.tex
work on document: added conclussions, future work, general review.

@@
 The main class for communicating java code and {\codefont Mathematica} is {\codefont KernelLink} and the main used method was {\codefont evaluateToOutputForm(String expr, int pageWidth)} where {\codefont expr} is the expression to be evaluated and {\codefont pageWidth} affects the formatting of the result.
+Once all the boilerplate has been written, the steps followed to define and find patterns in the expression are as follow: We import the string in MathML format through the command {\codefont ImportString["<mathmlExpression>", "MathML"]}.
+This creates the expression in the box form, but no further analysis is possible from this form.
+We then try to interpret this form into a fully Mathematica compatible expression by using {\codefont MakeExpression}
 
 \subsubsection{Pattern Extraction}
+Once the expression is created, finding a pattern is easy by using the command {\codefont Position[<variable holding the interpreted expression> , Pattern]}.
+A simple pattern for a quadratic expression is: {\codefont a\_.x\^{} 2 + b\_.x + c\_.}
+
+\subsection{Cleaning of variables}
+After each operation, all of the variables should be cleaned or it may lead to deadlocks, wrong results or other issues since the {\codefont MakeExpression} command also interprets the expression so if the expression is, for example {\codefont a = b + c} Mathematica remembers the assignment of the new value of {\codefont a} and uses it in further evaluations.
+The cleaning is done through the command {\codefont Remove["Global`*"]}
 
@@
 
-\begin{tabular}{|>{\centering\arraybackslash}m{4.5cm}|>
+\begin{longtable}{|>{\centering\arraybackslash}m{4.5cm}|>
 {\centering\arraybackslash}m{4.5cm}|>
@@
 \hline
-Original Form & {\codefont Simplify} & {\codefont FullSimplify} \\
+\small{Original Form} & \small{{\codefont Simplify}} & \small{{\codefont FullSimplify}} \\
 \hline
@@
 \scriptsize{ $\frac{1}{2} x^2 \log \left(1-e^{-2 x}\right) - \frac{1}{2} x L i_ 2 \left(e^{-2 x}\right)-\frac{1}{4} L i_ 3 \left(e^{-2 x}\right)$ }          & \scriptsize { \begin{multline}  \frac{1}{4} e^{-2 x} (2 x^2 e^{2 x} \log (1-e^{-2 x})- \notag\\ 2 i_ 2 L x-i_ 3 L)  \end{multline} } & \scriptsize{ $\frac{1}{2} x^2 \log \left(1-e^{-2 x}\right)-\frac{1}{4} L e^{-2 x} \left(2 i_ 2 x+i_ 3\right)$ }      \\
+\hline
+\caption{Comparison of different simplification modes}
 
 \label{comparison_simplification}
-\end{tabular}
 
+\end{longtable}
 \subsubsection{Recursive interpretation}
@@
 The demo setup employs the same dataset as used for experimentation.
+We include an online \LaTeX editor\cite{latex_editor} that renders the input expression as the user types it.
 

### 2014-03-11 docs/thesis/chap-conclusions.tex
work on document: added conclussions, future work, general review.

@@
 \chapter{Conclusions}
-\label{chapter-conclusions}
+\label{chap-conclusions}
+
+The area of Mathematical Information Retrieval is still very young and different systems, algorithms, datasets are being developed.
+Our work, $5e^{x+y}$, proposes a complete MIR system for a concrete digital library as the Cern Document Server.
+In terms of our proposed goals we can conclude:
+
+\begin{itemize}
+\item We explored and identified different tools and approaches to automatically detect and extract mathematical content from digital files.
+We conclude that Latexml and InftyReader are currently the best suitable set of tools to process Latex and PDF files respectively.
+We automatized the extraction process and incorporated it into the invenio workflow.
+\item Our exploration of the extraction tools, lead us to identify the MathML format as the best format to store and process mathematical content.
+It is the recommended language for web documents, and the best extraction tools agree in it.
+\item Once the mathematical expression is extracted and parsed to a suitable format the next step is identifying suitable features to index.
+We separated our features into notational and structural ones.
+For the first category, we developed some issues that have not yet been addressed in previous work and developed heuristics that allow to match more cases by normalizing unicode characters, grouping similar operators and expanding different numeric quantities.
+For the structural features, we explored the integration of a CAS to perform pattern matching and simplification of the given expression.
+\item We explored different IR frameworks and models to store and retrieve the indexed expressions and found the standard vector space model a suitable one for our needs.  
+\item We implemented our system in top of the Solr/Lucene framework.
+We took advantage of the modular design of Lucene to structure our work in independent classes where each one has a defined role.
+This structure also allows to easily implement and incorporate further heuristics to handle more cases.
+Our system is deployed as a Solr plugin making it very easy to be used from an external application.
+As a final component in our system, we developed the glue code to integrate our search engine with Invenio and developed a simple to use web interface.
+\item We performed different set of evaluation on our system to explore the queality of the retrieved results and the performance of our system.
+Our quality evaluations showed that a combination of notational and structural features allowed to achieved significantly better results.
+Our performance results showed that for indexing time, the extraction of structural features through the Mathematica CAS, imposes a heavy overhead of more than 10x, but as discussed previously, the extra work is worth with an improved set of results.
+The extra overhead at querying time is not insignificant but it is still acceptable for today's web usage standards.
+Our evaluation discarded the tree edit distance because the running time was 200 times than the time needed by a simple angular distance used in standard vector space model implementations, making this approach impractical for a big system.
+\item Finally, during this work we identified areas of improvement which are worth looking for. This are presented in the next section.
+\end{itemize}

### 2014-03-11 docs/thesis/chap-future_work.tex
added section of dlmf
more diagrams: main packages, query
work on document: added the quality results
work on document: added conclussions, future work, general review.

--- 2014-02-21 docs/thesis/chap-conclusions.tex
@@
-\chapter{Conclusions}
-\label{chapter-conclusions}
+\chapter{Future work}
+\label{chap-future_work}
+
+Several different work direction were identified during the development of this work.
+
+\section{Features extraction}
+MathML specification include hundreds of different tags, which were not addressed in our work.
+They can affect drastically the semantic of an expression.
+A simple example is the fact that sometimes to stress that a variable represents a vector, it is standard to use a bold font.
+Also an arrow in top of a variable signifies the same.
+Dozens and even hundreds of this notations contain important information which is not taken into account by our system, since each of this requires some coding time and handling all of the cases is impractical.
+Also, there is the limitation of the extracting tools to handle complex constructs like matrices or embedded text.
+
+\section{Data Analysis}
+Different algorithms and techniques have been developed to overcome some of the shortcomings of the vector space model.
+Latent semantic indexing together with singular value decomposition, allow to automatically identify synonyms which can improve the recall of an IR system.
+During our work, we tested different projects such as Semantic Vectors\cite{semantic_vectors} and \cite{mallet} and Mahout.
+However, the tools are not yet ready for a big deployment and lots of time and effort was spent on trying to integrate the formats from the Lucene index to the input format of each tool, and debugging and fixing code of some tools to make them work.
+Several times we got errors because of the in-memory implementations of the algorithms.
+Work on integrating the results of this techniques to the workflow of the system, can provide better results.
+
+In our work, we explored the clustering of the expressions and managed to find a reasonable parameter k.
+However more insight from this should be developed and the information gained with the clustering step should be integrated in the workflow to both improve the results and the querying time.
+
+\section{End to end system}
+In our implementation, we explored and incorporated \LaTeX extraction to our system.
+For a full integration on CDS, PDF extraction becomes an important need since most of the records that do not come from ArXiV, do not include the source files.

### 2014-03-11 docs/thesis/chap-introduction.tex
work on document: added conclussions, future work, general review.

@@
 \item Investigate different approaches and formats to store mathematical expressions
-\item Identify relevant features in a mathematical expression and how to use them to index equations
-\item Using the created index, propose ways to efficiently retrieve relevant expressions and articles given an input query
+\item Identify relevant features in a mathematical expression 
+\item Explore ways to efficiently store and retrieve the set of features
 \item Implement the previous steps into a complete system (a search engine) and integrate it into the Invenio software

### 2014-03-11 docs/thesis/chap-related_work.tex
work on document: added conclussions, future work, general review.

@@
 
+\subsection{WikiMirs}
+WikiMirs\cite{wikimirs} is a system that, as EgoMath, allows to find relevant Wikipedia entries by providing mathematical expression in \LaTeX.
+It combines the information about the semantic tree with the layout tree of a given expression and uses a similar approach to index different generalization levels.
+
 Other systems that provide similar search functionalities are \url{Uniquation} and \url{http://www.symbolab.com/}, however detailed information about the systems are not provided.

### 2014-03-12 docs/thesis/chap-conclusions.tex
Proofreading conclusions and future work

--- 2014-02-21 docs/thesis/chap-conclusions.tex
@@
 \chapter{Conclusions}
-\label{chapter-conclusions}
+\label{chap-conclusions}
+
+The area of Mathematical Information Retrieval (MIR) is still very young and different systems, algorithms and datasets are being developed.
+Our work, $5e^{x+y}$, proposes a complete MIR system for a concrete digital library, such as the CERN Document Server based on the Invenio digital library software platform.
+In terms of our proposed goals we can conclude that:
+
+\begin{itemize}
+\item We explored and identified different tools and approaches to automatically detect and extract mathematical content from digital files.
+We concluded that LaTeXML and InftyReader are currently the most suitable set of tools to process Latex and PDF files respectively.
+We automatized the extraction process and incorporated it into the Invenio workflow.
+\item Our exploration of the extraction tools, lead us to identify the MathML format as the best format to store and process mathematical content.
+It is the recommended language for web documents, and the best extraction tools agree on it.
+\item Once a mathematical expression is extracted and parsed to a suitable format the next step is to identify suitable features to index.
+We separated our features into notational and structural ones.
+For the first category, we developed (TODO: suggested / introduced?) some issues (TODO: features / techniques?) that have not yet been addressed in previous work and developed heuristics that allow to match more cases by normalizing unicode characters, grouping similar operators and expanding different numeric quantities.
+For the structural features, we explored the integration of a CAS (expand the acronym in case the reader only reades the Intro and conclusion?) to perform pattern matching and simplification of the given expression.
+\item We explored different IR frameworks and models to store and retrieve the indexed expressions and found that the standard vector space model is suitable for our needs.  
+\item We implemented our system in top of the Solr/Lucene framework.
+We took advantage of the modular design of Lucene to structure our work in independent classes where each one has a defined role.
+This structure also allows to easily implement and incorporate further heuristics to handle more cases.
+Our system is deployed as a Solr plugin making it very easy to be used from an external application.
+As a final component in our system, we developed the glue code to integrate our search engine with Invenio and developed a simple web interface.
+\item We performed different sets of evaluation on our system to explore the quality of the retrieved results and the performance of our system.
+Our quality evaluations showed that a combination of notational and structural features allow us to achieve significantly better results.
+Our performance results showed that the extraction of structural features through the Mathematica CAS imposes a heavy overhead of more than 10x on the indexing time, but as discussed previously, the extra work is worth investing in, given the improved set of results.
+The extra overhead at querying time is not insignificant but it is still acceptable for today's web usage standards.
+Our evaluation discarded the tree edit distance because the running time was 200 times more than the time needed by a simple angular distance used in standard vector space model implementations, making this approach impractical for a big system.
+\item Finally, during this work we identified areas of improvement which are worth looking into. They are presented in the next section (TODO: shouldn't the future work be before the conclusions?).
+\end{itemize}

### 2014-03-12 docs/thesis/chap-future_work.tex
Proofreading conclusions and future work

--- 2014-02-21 docs/thesis/chap-conclusions.tex
@@
-\chapter{Conclusions}
-\label{chapter-conclusions}
+\chapter{Future work}
+\label{chap-future_work}
+
+Several different work directions were identified during the development of this work.
+
+\section{Features extraction}
+The MathML specification include hundreds of different tags, which were not addressed in our work.
+They can affect drastically the semantics of a mathematical expression.
+A simple example is the fact that sometimes to stress that a variable represents a vector, it is standard to use a bold font.
+The same can be signigied by an arrow on top of a variable.
+Dozens and even hundreds of these notations contain important information which is not taken into account by our system, since each one of them requires some coding time (TODO: explicit treatment?), therefore handling all of the cases is impractical.
+Also, there is the limitation of the extracting tools to handle complex constructs like matrices or embedded text.
+
+\section{Data Analysis}
+Different algorithms and techniques have been developed to overcome some of the shortcomings of the vector space model.
+Latent semantic indexing together with singular value decomposition, allow to automatically identify synonyms which can improve the recall of an IR system.
+During our work, we tested different projects such as Semantic Vectors\cite{semantic_vectors} and \cite{mallet} and Mahout.
+However, these tools are not yet ready for a big deployment and a considerable amount of time and effort was spent on trying to integrate the formats from the Lucene index to the input format of each tool, as well as debugging and fixing code of some of the tools to make them work.
+Several times we encountered errors due to the in-memory implementations of the algorithms.
+Further work on integrating the results of these techniques to the workflow of the system could provide better results.
+
+In our work, we explored the clustering of the expressions and managed to find a reasonable parameter k (TODO: what is k?).
+However more insight from this should be developed and the information gained with the clustering step should be integrated in the workflow to improve both the results and the querying time.
+
+\section{End to end system}
+In our implementation, we explored and incorporated \LaTeX extraction to our system.
+For a full integration on CDS, PDF extraction becomes an important need since most of the records that do (not come from ArXiV, do) not include the source files.

### 2014-03-12 docs/thesis/chap-conclusions.tex
Addressed pendings from previous proofreading

@@
 We separated our features into notational and structural ones.
-For the first category, we developed (TODO: suggested / introduced?) some issues (TODO: features / techniques?) that have not yet been addressed in previous work and developed heuristics that allow to match more cases by normalizing unicode characters, grouping similar operators and expanding different numeric quantities.
-For the structural features, we explored the integration of a CAS (expand the acronym in case the reader only reades the Intro and conclusion?) to perform pattern matching and simplification of the given expression.
+For the first category, we discovered  some issues that have not yet been addressed in previous work and developed heuristics that allow to match more cases by normalizing unicode characters, grouping similar operators and expanding different numeric quantities.
+For the structural features, we explored the integration of a Computer Algebra System  to perform pattern matching and simplification of the given expression.
 \item We explored different IR frameworks and models to store and retrieve the indexed expressions and found that the standard vector space model is suitable for our needs.  
@@
 Our evaluation discarded the tree edit distance because the running time was 200 times more than the time needed by a simple angular distance used in standard vector space model implementations, making this approach impractical for a big system.
-\item Finally, during this work we identified areas of improvement which are worth looking into. They are presented in the next section (TODO: shouldn't the future work be before the conclusions?).
+\item Finally, during this work we identified areas of improvement which are worth looking into. They are presented in the next section.
 \end{itemize}

### 2014-03-12 docs/thesis/chap-future_work.tex
Addressed pendings from previous proofreading

@@
 A simple example is the fact that sometimes to stress that a variable represents a vector, it is standard to use a bold font.
-The same can be signigied by an arrow on top of a variable.
-Dozens and even hundreds of these notations contain important information which is not taken into account by our system, since each one of them requires some coding time (TODO: explicit treatment?), therefore handling all of the cases is impractical.
+The same can be signified by an arrow on top of a variable.
+Dozens and even hundreds of these notations contain important information which is not taken into account by our system, since each one of them requires explicit treatment, therefore handling all of the cases is impractical.
 Also, there is the limitation of the extracting tools to handle complex constructs like matrices or embedded text.
@@
 
-In our work, we explored the clustering of the expressions and managed to find a reasonable parameter k (TODO: what is k?).
+In our work, we explored the clustering of the expressions and managed to find a reasonable number of clusters for k-means.
 However more insight from this should be developed and the information gained with the clustering step should be integrated in the workflow to improve both the results and the querying time.
@@
 In our implementation, we explored and incorporated \LaTeX extraction to our system.
-For a full integration on CDS, PDF extraction becomes an important need since most of the records that do (not come from ArXiV, do) not include the source files.
+For a full integration on CDS, PDF extraction becomes an important need since most of the records that do not include the source files.

### 2014-03-12 docs/thesis/chap-cern_math_explorer.tex
recursive interpretation subsection

@@
 \subsubsection{Recursive interpretation}
+Unfortunately, Mathematica cannot always interpret correctly an input expression.
+In this case, it can, however interpret some sub-expressions from the original one.
+Our system takes advantage of this, and the first attempt is to try to interpret the original string.
+If this step is not successful (the result variable equals the string "{}"), we identify the occurrences of {\codefont RowBox} which identify all the subexpressions in the tree.
+For each of this elements we call the {\codefont MakeExpression} and if it was successful we search for structural pattern in it.
+A first thought would tell us that if sub-tree was interpreted successfully, there is no need to try to go further down in that sub-tree, however, even if a sub-expression is interpreted correctly, the result sometimes is not complete and processing further down, gives better results.
+For this reason, we do not discard any of the subexpressions and try to interpret all of them.
+For this same reason, we do not store the number of occurrences of a given pattern, but only whether it contains is or not.
 
 \subsubsection{Error handling}
-Sometimes, after certain time, the connection between {\codefont KernelLink} and {\codefont Mathematica} would be lost launching an exception and all following invocations would fail as well.
+Sometimes, after certain time, the connection between {\codefont KernelLink} and {\codefont Mathematica} is lost and it launches an exception and all following invocations fail as well.
 Also, re-instantiating a KernelLink would yield an Exception.
@@
 The communication between Solr and Invenio was through the library {\codefont solrpy}. 
-Figure \ref{system_arch} presents the main components of our deployment.
+Figure 5.3 presents the main components of our deployment.
 
-\begin{figure}
+\begin{figure}[h!]
 \includegraphics[height=4.2 cm]{visio_drawings/architecture.png}
@@
 \begin{figure}
-\includegraphics[height=8 cm]{figures/input_interface.png}
+\center
+\includegraphics[height=6.2 cm]{figures/input_interface.png}
 \label{input_int}
@@
 \begin{figure}
-\includegraphics[height=8 cm]{figures/results_interface.png}
+\center
+\includegraphics[height=6.2 cm]{figures/results_interface.png}
 \label{results_int}

### 2014-03-13 docs/thesis/chap-cern_math_explorer.tex
minor fixes to document

@@
 
-\subsubsection{Pattern Extraction}
+\subsection{Pattern Extraction}
 Once the expression is created, finding a pattern is easy by using the command {\codefont Position[<variable holding the interpreted expression> , Pattern]}.
@@
 
-\subsubsection{Expression simplification}
+\subsection{Expression simplification}
 The second feature that we are interested in is automatic expression simplification.
@@
 \end{longtable}
-\subsubsection{Recursive interpretation}
+\subsection{Recursive interpretation}
 Unfortunately, Mathematica cannot always interpret correctly an input expression.
@@
 
-\subsubsection{Error handling}
+\subsection{Error handling}
 Sometimes, after certain time, the connection between {\codefont KernelLink} and {\codefont Mathematica} is lost and it launches an exception and all following invocations fail as well.
@@
 
-\subsubsection{Timeout Handling}
+\subsection{Timeout Handling}
 Unfortunately, checking the quality of a LaTeX document is a difficult job and users have a lot of freedom in the way they write their document since the only visible result is the rendered version. 

### 2014-03-13 docs/thesis/chap-cern_math_explorer.tex
proofreading fixes

@@
   \begin{itemize}
+  \itemsep0em
   \item NFD: Normalization Form Canonical Decomposition
@@
 For each token that belongs to some of this predefined groups, a second token is created identifying the group.
-For example the token <mo>{\unicodefont ∮}</mo> is expanded into <mo>{\unicodefont ∮}</mo><mo>INTEGRALS</mo>, similarly the token <mo>{\unicodefont ∫}</mo> is expanded into <mo>{\unicodefont ∫}</mo><mo>INTEGRALS</mo> and then both will have a partial match in the INTEGRALS token.
+For example the token <mo>{\unicodefont ∮}</mo> is expanded into <mo>{\unicodefont ∮}</mo> <mo>INTEGRALS</mo>, similarly the token <mo>{\unicodefont ∫}</mo> is expanded into <mo>{\unicodefont ∫}</mo> <mo>INTEGRALS</mo> and then both will have a partial match in the INTEGRALS token.
 The Unicode specification does not define a strict rule to group similar characters based on their semantics.
@@
 Our system takes advantage of this, and the first attempt is to try to interpret the original string.
-If this step is not successful (the result variable equals the string "{}"), we identify the occurrences of {\codefont RowBox} which identify all the subexpressions in the tree.
-For each of this elements we call the {\codefont MakeExpression} and if it was successful we search for structural pattern in it.
-A first thought would tell us that if sub-tree was interpreted successfully, there is no need to try to go further down in that sub-tree, however, even if a sub-expression is interpreted correctly, the result sometimes is not complete and processing further down, gives better results.
+If this step is not successful (the result variable equals the string "\{\}"), we identify the occurrences of {\codefont RowBox} which identify all the subexpressions in the tree.
+For each of this elements we call the {\codefont MakeExpression} and if it was successful we search for structural patterns in it.
+A first thought would tell us that if sub-tree was interpreted successfully, there is no need to try to go further down in that sub-tree, however, even if a sub-expression is interpreted correctly, the result sometimes is not complete and processing further down gives better results.
 For this reason, we do not discard any of the subexpressions and try to interpret all of them.
@@
 Also, some extra configurations should be added.
-Details on this can be found in appendix \ref{appendix-conf_files}
+Details on this can be found in appendix \ref{appendix-conf_files}.
 The communication between Solr and Invenio was through the library {\codefont solrpy}. 

### 2014-03-13 docs/thesis/chap-related_work.tex
work on title page
proofreading fixes

@@
 
-\subsection{LaTEXSearch}
-LaTEXSearch \url{http://latexsearch.com/} is a system developed by the scientific publisher Springer that allows to search over a database of around eight million latex snippets extracted from their publications.
-The system, unfortunately, is proprietary and no details are provided about the internals of the system.
+\subsection{LaTeXSearch}
+LaTeXSearch \url{http://latexsearch.com/} is a system developed by the scientific publisher Springer that allows to search over a database of around eight million latex snippets extracted from their publications.
+The system, unfortunately, is proprietary and no further details are provided.
 
@@
 It combines the information about the semantic tree with the layout tree of a given expression and uses a similar approach to index different generalization levels.
+The system is available at \url{http://www.icst.pku.edu.cn/cpdp/wikimirs/} \\
 
-Other systems that provide similar search functionalities are \url{Uniquation} and \url{http://www.symbolab.com/}, however detailed information about the systems are not provided.
+Other systems that provide similar search functionalities are Uniquation(\url{http://uniquation.com}) and Symbolab(\url{http://www.symbolab.com/}), however detailed information about the systems are not provided.
 Finally Wolfram Alpha\cite{wolframalpha} is a very powerful tool that allows to find information about lots of mathematical concepts and a wide variety of other objects (Even Pokemon).

### 2014-03-13 docs/thesis/chap-technical_considerations.tex
proofreading fixes

@@
 It is mainly used now for defining mathematical concepts into standard content dictionaries which can be imported.
-MathML is compatible with this dictionaries.
+MathML is compatible with these dictionaries.
 
@@
 
-\LaTeX allows the most compact representations of the equations and it is the closest language to the community.
+\LaTeX \ allows the most compact representations of the equations and it is the closest language to the community.
 However, its processing is not straightforward because a given equation can include multiple commands from different packages.
@@
 Smaller portions of other documents are stored in other formats like Microsoft Word, OpenOffice Documents.
-In practice, the main options from where to do the extraction from, are PDFs and \LaTeX  files.
+In practice, the main options from where to do the extraction from, are PDFs and \LaTeX\ files.
 Also taking into account the previous discussion on the available format for representing mathematics, we focused our attention in tools that output MathML.

### 2014-03-13 docs/thesis/appendix-conf_files.tex
Work on thesis doc: Added intro section and status of MIR.
added clustering section

@@
 \chapter{Configuration files}
+\label{appendix-conf_files}
 
-\section{Solr Schema}
+\section{Solr schema}
 The Solr schema file \verb|schema.xml| indicates which are the fields that are going to be used in this instance, and what type of analyzer is going to be used for each one.

### 2014-03-13 docs/thesis/chap-clustering.tex
added clustering section

--- 2014-03-11 docs/thesis/chap-advanced_techniques.tex
@@
-\chapter{Further Data Analysis}
-\label{chap-data_analysis}
+\chapter{Clustering}
+\label{chap-clustering}
 
@@
 
-\section{Clustering}
+\section{Technical details}
 
-We used Apache Mahout v0.9 for performing the clustering task. 
+We used Apache Mahout v0.9\cite{mahout} for performing the clustering task. 
 The following set of commands were used to create and analyse our dataset:
@@
 
-\small{{\codefont ./mahout lucene.vector -d <path to solr index>  -o ../results/vectors -t ../results/dict -f math           \_notational\_field -st ../results/dict\_seq -x 20 -md 2 -w TFIDF -n 2}}
+\small{{\codefont ./mahout lucene.vector -d <path to solr index>  -o ../results/vectors -t ../results/dict -f math\_notational\_field -st ../results/dict\_seq -x 20 -md 2 -w TFIDF -n 2}}
 
@@
 \small{{\codefont ./mahout seqdumper -i ../results/clustering\_kmeans/clusteredPoints/part-m-0 > ../results/clustering\_kmeans/clusteredPoints/cluster-points.txt}}
+
+\section{Estimating number of clusters}
 
@@
 The resulting clusters can help us to identify common structures and further improve our results by either adding frequent structures that are common to a cluster, or by reducing the number of elements to perform comparisons against and allow to speed-up the querying process.
-Table \ref{} shows the top terms in 2 different clusters that were identified.
+Table \ref{top_terms} shows the top terms in 2 different clusters that were identified.
 By simple inspection, it is possible to identify the first one as a cluster grouping trigonometric expressions (Sines and Cosines) and the second one grouping limits where the variable goes to infinity.
@@
 \caption{Top 20 terms for two different identified clusters }
-\label{cluster_measurements}
+\label{top_terms}
 \end{longtable} 
 }
-
-\section{Latent Dirichlet Allocation with Apache Mahout}

### 2014-03-13 docs/thesis/chap-future_work.tex
proofreading fixes
minor fixes to the document: distributed system(s) latex_editor (that)

@@
 Latent semantic indexing together with singular value decomposition, allow to automatically identify synonyms which can improve the recall of an IR system.
-During our work, we tested different projects such as Semantic Vectors\cite{semantic_vectors} and \cite{mallet} and Mahout.
+During our work, we tested different projects such as Semantic Vectors\cite{semantic_vectors} and Mallet\cite{mallet} and Mahout.
 However, these tools are not yet ready for a big deployment and a considerable amount of time and effort was spent on trying to integrate the formats from the Lucene index to the input format of each tool, as well as debugging and fixing code of some of the tools to make them work.
@@
 In our implementation, we explored and incorporated \LaTeX extraction to our system.
-For a full integration on CDS, PDF extraction becomes an important need since most of the records that do not include the source files.
+For a full integration on CDS, PDF extraction becomes an important need since most of the records do not include the source files.

### 2014-03-13 docs/thesis/chap-cern_math_explorer.tex
minor fixes to the document: distributed system(s) latex_editor (that)
Syntax and grammar fixes

@@
 Our main goal is to develop a system that compliments the already available search capabilities in Invenio and in particular the CDS instance.
-Our system was developed on top of the  the Apache Solr/Lucene framework.
+Our system was developed on top of the  the Apache Lucene/Solr framework.
 CDS already uses Solr as a search engine layer, so developing $5e^{x+y}$(CDS) using this technology supposed a reasonable choice.
@@
 	\includegraphics[height=2 cm]{figures/greater_less.png}
-	\caption{List of different types of grater/less than related characters in Unicode}
+	\caption{List of different types of greater/less than related characters in Unicode}
 	\label{less_greater}
@@
 \section{Development with Lucene/Solr}
-This section explains how the described components were implemented in the {\codefont Apache Solr/Lucene} framework.
+This section explains how the described components were implemented in the {\codefont Apache Lucene/Solr} framework.
 One focus of our work was to develop a modular system that allowed easily to deploy new heuristics as they were identified.
@@
 The demo setup employs the same dataset as used for experimentation.
-We include an online \LaTeX editor\cite{latex_editor} that renders the input expression as the user types it.
+We include an online \LaTeX\ editor\cite{latex_editor} that renders the input expression as the user types it.
 

### 2014-03-13 docs/thesis/chap-introduction.tex
proofreading fixes
Syntax and grammar fixes

@@
 Even though the main focus of CERN relies on the study of particle physics, the strong research environment has lead to important advances in several different areas, and one of the main inventions that CERN has contributed to the world is the Web.
-Tim Berners-Lee, in 1989, proposed a solution\cite{web_proposal} to the increasing problem of keeping track all the information related to the different experiments held at CERN, through a hypertext system.
+Tim Berners-Lee, in 1989, proposed a solution\cite{web_proposal} to the increasing problem of keeping track of all the information related to the different experiments held at CERN, through a hypertext system.
 
-\subsection{CDS Invenio}
-CDS\cite{CDS1} (CERN Document Server) Invenio is the integrated digital library system developed and used at CERN\cite{CDS2}.
-To the date, it contains more than one million records and more than 400000 full-text documents.
-It provides tools to manage the complete workflow of a document taking care of the submission, annotation, editing, storage, searching, retrieval, displaying among other phases.
+\subsection{CDS & Invenio}
+CDS\cite{CDS1} (CERN Document Server) is the institutional digital library system developed and used at CERN\cite{CDS2}.
+To this date, it contains more than one million records and more than 400000 full-text documents.
+It provides tools to manage the complete workflow of a document taking care of the submission, annotation, editing, storage, searching, retrieval and displaying, among other phases.
 Figure \ref{cds_screenshot} presents the search results for a simple query in CDS.
@@
 
-Invenio\cite{invenio} is the software running behind CDS and is an open source project developed in parallel to CDS at CERN.
+Invenio\cite{invenio} is the open-source digital library software platform running behind CDS and it is a project developed in parallel to CDS at CERN.
 Besides CDS, Invenio also supports around thirty scientific institutions worldwide including Fermilab, SLAC National Laboratory, INSPIRE and EPFL.
 Invenio is composed of several modules, each one of which can be mapped to a specific step in the workflow of a record.
-Figure \ref{invenio_architecture} presents the global architecture of Invenio.
+Figure 1.2 presents the global architecture of Invenio.
 A detailed explanation of each module can be accessed in \cite{invenio_modules}
@@
 \centering
-\includegraphics[height=10 cm]{figures/invenio.jpeg}
+\includegraphics[height=15 cm]{figures/invenio.jpeg}
 \label{invenio_architecture}

### 2014-03-13 docs/thesis/chap-introduction.tex
Syntax and grammar fixes

@@
 Invenio\cite{invenio} is the open-source digital library software platform running behind CDS and it is a project developed in parallel to CDS at CERN.
-Besides CDS, Invenio also supports around thirty scientific institutions worldwide including Fermilab, SLAC National Laboratory, INSPIRE and EPFL.
+Besides CDS, Invenio supports around thirty scientific institutions worldwide including INSPIRE (a collaboration between Fermilab, CERN, DESY and SLAC) EPFL and ILO.
 Invenio is composed of several modules, each one of which can be mapped to a specific step in the workflow of a record.

### 2014-03-13 docs/thesis/chap-technical_considerations.tex
Syntax and grammar fixes

@@
 Smaller portions of other documents are stored in other formats like Microsoft Word, OpenOffice Documents.
-In practice, the main options from where to do the extraction from, are PDFs and \LaTeX\ files.
+In practice, the main options from where to do the extraction from, are PDF and \LaTeX\  files.
 Also taking into account the previous discussion on the available format for representing mathematics, we focused our attention in tools that output MathML.
@@
 A conscious exploration of available software for extracting mathematical content from this two types of documents allowed us to identify different tools with different approaches. 
-\LaTeX  files are easier to process and all of the tools implement their own compiler that XML + MathML outputs instead of the typical.
+\LaTeX\  files are easier to process and all of the tools implement their own compiler that XML + MathML outputs instead of the typical.
 Since the original math equation is provided in the document, there is relatively little ambiguity in the equation, and the major issues that the systems struggle with is in the coverage of all the possible commands and packages that are available.
@@
 
-For extraction from \LaTeX  files we concluded that the best option is LaTeXML.
+For extraction from \LaTeX\  files we concluded that the best option is LaTeXML.
 The tool is still in current development and has lot of support from the academic community.
@@
 For PDF files, the trial version of InftyReader worked very well giving better results and processing successfully more files than Maxtract.
-As said previously, a big portion of the documents stored in CDS, come from pre-printing services like ArXiV were fortunately the source code of an article is available and because of this reason, our base set for this work will consist on extracting equations from \LaTeX files.
+As said previously, a big portion of the documents stored in CDS, come from pre-printing services like ArXiV were fortunately the source code of an article is available and because of this reason, our base set for this work will consist on extracting equations from \LaTeX\  files.
 For licensing reasons, for this project we will not integrate our system with InftyReader for the moment and will proceed with LaTeXML as our extraction tool.

### 2014-04-08 docs/thesis/chap-theoretical_background.tex
work on document: added conclussions, future work, general review.
work on title page
fixes to the thesis document

@@
 
-A further variation that takes into account structure in the form of a document containing different fields and each of them having its own length and importance (boost) can be formulated as follows, known as BM25F can be expressed as follows:
+A further variation that takes into account structure in the form of a document containing different fields and each of them having its own length and importance (boost), known as BM25F can be expressed as follows:
 
@@
 where $m$ is the number of different fields, $boost_j$ is the relative importance for each field, $b_j$ is analogous to the $b$ constant in the BM25 group of equations, $|l_j|$ is the length of the $field_j$ and $avgfl_j$ is the average length of the $field_j$.
-
-\section{Latent Semantic Indexing}
-
-\section{Latent Dirichlet Allocation}
 

### 2014-11-04 docs/thesis/chap-clustering.tex
First load of the JCDL paper files.

@@
 
-\small{{\codefont ./mahout canpoy -t1 0.15 -t2 0.1 -i ../results/vectors -o ../results/clustering/canopy -dm org.apache.mahout.common.distance.CosineDistanceMeasure}}
+\small{{\codefont ./mahout canopy -t1 0.15 -t2 0.1 -i ../results/vectors -o ../results/clustering/canopy -dm org.apache.mahout.common.distance.CosineDistanceMeasure}}
 

### 2014-11-04 jcdl2015/paper/main.tex
First load of the JCDL paper files.

% This is "sig-alternate.tex" V2.0 May 2012
% This file should be compiled with V2.5 of "sig-alternate.cls" May 2012
%
% This example file demonstrates the use of the 'sig-alternate.cls'
% V2.5 LaTeX2e document class file. It is for those submitting
% articles to ACM Conference Proceedings WHO DO NOT WISH TO
% STRICTLY ADHERE TO THE SIGS (PUBS-BOARD-ENDORSED) STYLE.
% The 'sig-alternate.cls' file will produce a similar-looking,
% albeit, 'tighter' paper resulting in, invariably, fewer pages.
%
% ----------------------------------------------------------------------------------------------------------------
% This .tex file (and associated .cls V2.5) produces:
%       1) The Permission Statement
%       2) The Conference (location) Info information
%       3) The Copyright Line with ACM data
%       4) NO page numbers
%
% as against the acm_proc_article-sp.cls file which
% DOES NOT produce 1) thru' 3) above.
%
% Using 'sig-alternate.cls' you have control, however, from within
% the source .tex file, over both the CopyrightYear
% (defaulted to 200X) and the ACM Copyright Data
% (defaulted to X-XXXXX-XX-X/XX/XX).
% e.g.
% \CopyrightYear{2007} will cause 2007 to appear in the copyright line.
% \crdata{0-12345-67-8/90/12} will cause 0-12345-67-8/90/12 to appear in the copyright line.
%
% ---------------------------------------------------------------------------------------------------------------
% This .tex source is an example which *does* use
% the .bib file (from which the .bbl file % is produced).
% REMEMBER HOWEVER: After having produced the .bbl file,
% and prior to final submission, you *NEED* to 'insert'
% your .bbl file into your source .tex file so as to provide
% ONE 'self-contained' source file.
%
% ================= IF YOU HAVE QUESTIONS =======================
% Questions regarding the SIGS styles, SIGS policies and
% procedures, Conferences etc. should be sent to
% Adrienne Griscti (griscti@acm.org)
%
% Technical questions _only_ to
% Gerald Murray (murray@hq.acm.org)
% ===============================================================
%
% For tracking purposes - this is V2.0 - May 2012

\documentclass{sig-alternate}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%Imports%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{amsmath}
\usepackage{fontspec}
\usepackage[utf8x]{inputenc}
\usepackage{listings}
\usepackage{longtable}
\usepackage{url}

\newfontfamily\unicodefont{Arial Unicode MS}
\newfontfamily\codefont{Courier}

\begin{document}
%
% --- Author Metadata here ---
\conferenceinfo{JCDL}{2014 Knoxville, USA}
%\CopyrightYear{2007} % Allows default copyright year (20XX) to be over-ridden - IF NEED BE.
%\crdata{0-12345-67-8/90/01}  % Allows default copyright data (0-89791-88-6/97/05) to be over-ridden - IF NEED BE.
% --- End of Author Metadata ---

\title{$5e^{x+y}$: A Math Aware Search Engine (for CDS)}

%
% You need the command \numberofauthors to handle the 'placement
% and alignment' of the authors beneath the title.
%
% For aesthetic reasons, we recommend 'three authors at a time'
% i.e. three 'name/affiliation blocks' be placed beneath the title.
%
% NOTE: You are NOT restricted in how many 'rows' of
% "name/affiliations" may appear. We just ask that you restrict
% the number of 'columns' to three.
%
% Because of the available 'opening page real-estate'
% we ask you to refrain from putting more than six authors
% (two rows with three columns) beneath the article title.
% More than six makes the first-page appear very cluttered indeed.
%
% Use the \alignauthor commands to handle the names
% and affiliations for an 'aesthetic maximum' of six authors.
% Add names, affiliations, addresses for
% the seventh etc. author(s) as the argument for the
% \additionalauthors command.
% These 'additional authors' will be output/set for you
% without further effort on your part as the last section in
% the body of your article BEFORE References or any Appendices.

\numberofauthors{3} %  in this sample file, there are a *total*
% of EIGHT authors. SIX appear on the 'first-page' (for formatting
% reasons) and the remaining two appear in the \additionalauthors section.
%
% You can go ahead and credit any number of authors here,
% e.g. one 'row of three' or two rows (consisting of one row of three
% and a second row of one, two or three).
%
% The command \alignauthor (no curly braces needed) should
% precede each author name, affiliation/snail-mail address and
% e-mail address. Additionally, tag each line of
% affiliation/address with \affaddr, and tag the
% e-mail address with \email.
%
% 1st. author
\author{
\alignauthor Arthur Oviedo\\
  \affaddr{EPFL, Switzerland.}\\%
  \affaddr{arthur.oviedo@alumini.epfl.ch}%
\alignauthor Nikolaos Kasioumis \\
  \affaddr{CERN, Switzerland.}\\%
  \affaddr{nikos.kasioumis@cern.ch}%
\alignauthor Karl Aberer\\%
  \affaddr{EPFL, Switzerland.}\\%
  \affaddr{karl.aberer@epfl.ch}%
}

\maketitle
\begin{abstract}
This paper presents $5e^{x+y}$, a system that complements CERN Document Server (CDS), by adding extracting, indexing and querying of mathematical content, expressed as mathematical equations.
\end{abstract}

% A category with the (minimum) three required fields
\category{X.X}{Digital Libraries}{Miscellaneous}
%A category including the fourth, optional field follows...
\category{Y.Y}{Information Retrieval}{Metrics}

\terms{Theory}

\keywords{ACM proceedings, \LaTeX, text tagging}

\section{Introduction}
\include{section-introduction}
\include{section-related_work}
\include{section-system_description}
\include{section-evaluation}
\include{section-conclusions}

%ACKNOWLEDGMENTS are optional
\section{Acknowledgments}
We would like to thanks the ScienceWISE team for the help and important insights that they provided for the realization of this project.

%
% The following two commands are all you need in the
% initial runs of your .tex file to
% produce the bibliography for the citations in your paper.
\bibliographystyle{abbrv}
\bibliography{bibliography}  % sigproc.bib is the name of the Bibliography in this case
% You must have a proper ".bib" file
%  and remember to run:
% latex bibtex latex latex
% to resolve all references
%
% ACM needs 'a single self-contained file'!
%
%APPENDICES are optional
%\balancecolumns
\end{document}

### 2014-11-04 jcdl2015/paper/section-evaluation.tex
First load of the JCDL paper files.

--- 2014-03-10 docs/thesis/chap-evaluation.tex
@@
-\chapter{Evaluation}
+\section{Evaluation}
 When building an IR system there are two main aspects that should be considered.
@@
 
-\section{Dataset}
+\subsection{Dataset}
 Our dataset consists on 12234 latex documents fetched from ArXiV.
@@
 
-\section{Setup}
+\subsection{Setup}
 
@@
 The complete specifications of the used software is presented in table \ref{sw_used}
-
-\begin{longtable}{|m{4cm}|>
-{\centering\arraybackslash}m{4cm}|>
-{\centering\arraybackslash}m{4cm}|
-}
-\hline 
-\textbf{Software} & 
-\textbf{Version} 
-\\
-\hline
-Operative System & Linux Mint 16 Petra (Ubuntu based) \\ \hline
-Linux Kernel & 3.11.0-15 \\ \hline
-Java Virtual Machine & 1.7.0-45 \\ \hline
-Apache Solr & 4.6 \\ \hline
-Python & 2.7.5+ \\ \hline
-\caption{Software used during evaluations}
-\label{sw_used}
-\end{longtable}
 
@@
 
-The evaluated queries were provided by physics experts working at CERN from their own research topics. The queries were provided in \LaTeX format as the users used them in their own publications.
+The evaluated queries were provided by physics experts working at CERN from their own research topics. The queries were provided in \LaTeX\ format as the users used them in their own publications.
 Table \ref{equations_table} presents the set of queries that were evaluated, and a simple explanation about each one. 
@@
 
-\begin{longtable}{|c|c|c|c|}
-\hline 
-\textbf{Scenario} & \textbf{Top 5} & \textbf{Top 10} & \textbf{Top 20} \\ 
-\hline 
-N & 0.86 & 0.79 & 0.0.78 \\ 
-\hline 
-N+S & 0.9 & 0.85 & 0.77 \\ 
-\hline 
-N+S+NN & 0.92 & 0.94 & 0.88 \\ 
-\hline
-N+S+NN (BM25) & 0.92 & 0.94 & 0.87 \\ 
-\hline
-
-\caption{Loose Precision}
-\label{loose_precision}
-\end{longtable}
-
-\begin{longtable}{|c|c|c|c|}
-\hline 
-\textbf{Scenario} & \textbf{Top 5} & \textbf{Top 10} & \textbf{Top 20} \\ 
-\hline 
-N & 0.76 & 0.61 & 0.50 \\ 
-\hline 
-N+S & 0.84 & 0.70 & 0.56 \\ 
-\hline 
-N+S+NN & 0.84 & 0.83 & 0.65 \\ 
-\hline 
-N+S+NN (BM25) & 0.84 & 0.83 & 0.67 \\ 
-\hline
-
-\caption{Strict Precision}
-\label{stric_precision}
-\end{longtable}
-
-\begin{longtable}{|c|c|c|c|}
-\hline 
-\textbf{Scenario} & \textbf{Top 5} & \textbf{Top 10} & \textbf{Top 20} \\ 
-\hline 
-N & 7.17 & 9.81 & 12.00 \\ 
-\hline 
-N+S & 7.61 & 10.7 & 14.59 \\ 
-\hline 
-N+S+NN & 7.66 & 11.81 & 16.32 \\ 
-\hline 
-N+S+NN (BM25) & 7.66 & 11.82 & 16.42 \\ 
-\hline
-\caption{Discounted Cumulative Gain}
-\label{dcg}
-\end{longtable}
-
 Results show that for the selected queries, the system performs reasonably well achieving a precision of 0.84 in the top 5 results in the best scenario and 0.65 in the top 20 results. 
@@
 
-\section{Indexing Performance}
+\subsection{Indexing Performance}
 For this set of evaluations, we were only interested in observing how the performance of the indexing stage is affected by the different types of features that are employed.
@@
 
-\begin{longtable}{|c|c|>
-{\centering\arraybackslash}m{2cm}|>
-{\centering\arraybackslash}m{2cm}|>
-{\centering\arraybackslash}m{2cm}|}
-\hline 
-\textbf{Feature Set} & \textbf{Total time (sec)} & \textbf{Index Size (kb)} & \textbf{Avg. time per equation} & \textbf{Avg. size of equation (kb)} \\ 
-\hline 
-N & 58 & 13926 & 0.00524 & 1.237 \\ 
-\hline 
-N+S & 884 & 14438 & 0.0785 & 1.282 \\ 
-\hline 
-N+S+NN & 1273 & 25780 & 0.113 & 2.345 \\ 
-\hline 
-N+S+FN & 1377 & 25548 & 0.122 & 2.269 \\ 
-\hline
-\caption{Indexing performance}
-\label{indexing_performance}
-\end{longtable}
-
-\section{Querying Performance}
+\subsection{Querying Performance}
 Similarly, we were also interested in evaluating how the query performance of the queries was affected with the different scenarios.
 For this set of queries we used the complete dataset, and evaluated the N and the N+S+NN scenarios for queries of different length.
-
-\begin{longtable}{|>{\centering\arraybackslash}m{5cm}|>
-{\centering\arraybackslash}m{4cm}|>
-{\centering\arraybackslash}m{4cm}|
-}
-\hline 
-\textbf{Expression Length(Number of characters in MathML)}& \textbf{N} & \textbf{N+S+NN} \\ \hline 
-70 & 0.178 & 0.327  \\ \hline
-198 & 0.179 & 0.810  \\ \hline
-452 & 0.323 & 1.692  \\ \hline
-771 & 0.393 & 2.066  \\ \hline
-
-\caption{Query performance in seconds}
-\label{query_performance}
-\end{longtable}
 
@@
 
-\section{Alternative Metrics}
+\subsection{Alternative Metrics}
 According to some experimental evaluations presented in \cite{tree_comparison}, Tree Edit Distance provides an interesting alternative metric to the standard vector space model using angular distance.
@@
 
-\begin{longtable}{|>{\centering\arraybackslash}m{5cm}|>
-{\centering\arraybackslash}m{4cm}|>
-{\centering\arraybackslash}m{4cm}|
-}
-\hline 
-\textbf{Expression Length (Number of leaf nodes)}& \textbf{Angular Distance Time (msec)} & \textbf{Tree Edit Distance Time(msec)} \\ \hline 
-3 & 0.01195 & 2.65  \\ \hline
-8 & 0.0142 & 9.97  \\ \hline
-7 & 0.0129 & 9.165  \\ \hline
-12 & 0.0194 & 15.15  \\ \hline
-18 & 0.0201 & 29.5  \\ \hline
-20 & 0.0245 & 27.75  \\ \hline
-22 & 0.0264 & 32.4  \\ \hline
-24 & 0.02502 & 32.1 \\ \hline
-
-\caption{Distance computation using two different metrics}
-\label{comparison_tree_times}
-\end{longtable}
-
 This result show that for shorter expressions, using tree edit distance represent an increase in time in more than 200x, and a factor of around 1200x for the longer expressions, making it impractical for implementing a system that needs to be responsive.

### 2014-11-04 jcdl2015/paper/section-introduction.tex
First load of the JCDL paper files.

--- 2014-03-13 docs/thesis/chap-introduction.tex
@@
-\chapter{Introduction}
-
-\section{Context}
+\section{Introduction}
 
@@
 
-\subsection{CDS & Invenio}
+\subsection{CDS \& Invenio}
 CDS\cite{CDS1} (CERN Document Server) is the institutional digital library system developed and used at CERN\cite{CDS2}.
@@
 \centering
-\includegraphics[height=7 cm]{figures/cds_screenshot.png}
+\includegraphics[height=3 cm]{images/figures/cds_screenshot.png}
 \label{cds_screenshot}
@@
 \centering
-\includegraphics[height=15 cm]{figures/invenio.jpeg}
+\includegraphics[height=4 cm]{images/figures/invenio.jpeg}
 \label{invenio_architecture}
@@
 
-\section{Project overview}
+\subsection{Project overview}
 \subsection{Motivation}

### 2014-11-04 jcdl2015/paper/section-related_work.tex
First load of the JCDL paper files.

--- 2014-03-13 docs/thesis/chap-related_work.tex
@@
-\chapter{Related Work}
-\label{chap-related_work}
-\section{Status of Mathematical Information Retrieval}
+\section{Related Work}
+\subsection{Status of Mathematical Information Retrieval}
 Even though Information Retrieval has been a research field from around the 1950s where the first metrics for such systems were developed and in the 1960s where SMART (System for Mechanical Analysis and Retrieval of Text), the first computer based system was developed; only in the last couple years focus have been put into adapting the same techniques to mathematical content.
@@
 
-\section{Mathematical based search projects}
+\subsection{Mathematical based search projects}
 

### 2014-11-04 jcdl2015/paper/section-system_description.tex
First load of the JCDL paper files.

--- 2014-03-13 docs/thesis/chap-cern_math_explorer.tex
@@
-\chapter{$5e^{x+y}$(CDS)}
+\section{$5e^{x+y}$(CDS)}
 \label{chapter-cern_math_explorer}
@@
 
-\section{Features Extraction}
+\subsection{Features Extraction}
 Our main goal is to develop a system that compliments the already available search capabilities in Invenio and in particular the CDS instance.
@@
 
-\begin{longtable}{|m{4cm}|>{\centering\arraybackslash}m{2.15cm}|>{\centering\arraybackslash}m{1.65cm}|>{\centering\arraybackslash}m{1.65cm}|>{\centering\arraybackslash}m{1.65cm}|>{\centering\arraybackslash}m{1.65cm}|}
-\hline 
-\textbf{Character Name} & \textbf{Visual Rendering} & \textbf{NFC} & \textbf{NFD} & \textbf{NFKC} & \textbf{NFKD} \\ 
-\hline 
-LATIN CAPITAL LETTER A & A & 0x41 & 0x41 & 0x41 & 0x41 \\ 
-\hline 
-LATIN CAPITAL LETTER A WITH MACRON & \={A} & 0x100 & 0x41 0x304 & 0x100 & 0x41 0x304 \\
-\hline 
-LATIN CAPITAL LETTER A WITH RING ABOVE & \r{A} & 0xc5 & 0x41 0x30a & 0xc5 & 0x41 0x30a \\
-\hline 
-ANGSTROM SIGN (0x212b) &	\r{A} &	0xc5 &	0x41 0x30a &	0xc5 &	0x41 0x30a \\
-\hline
-LATIN CAPITAL LIGATURE IJ &	Ĳ &	0x132 &	0x132 &	0x49(I) 0x4a(J) &	0x49 0x4a \\
-\hline
-CYRILLIC CAPITAL LIGATURE A IE & {\unicodefont Ӕ} &	0x4d4 &	0x4d4 &	0x4d4 &	0x4d4 \\
-\hline
-LATIN CAPITAL LETTER AE	& {\unicodefont Ӕ}	& 0xc6	& 0xc6	& 0xc6	& 0xc6 \\
-\hline
-DOUBLE-STRUCK CAPITAL N	& {\unicodefont ℕ}	& 0x2115 & 0x2115 & 0x2115 & 0x4e \\
-\hline
-LATIN CAPITAL LETTER N	& N & 0x4e	& 0x4e & 	0x4e	& 0x4e \\
-\hline 
-MATHEMATICAL ITALIC CAPITAL N & $\mathcal{N}$	& 0xd835  0xdc41 &	0xd835  0xdc41 &	0x4e	 & 0x4e \\
-\hline 
-ROMAN NUMERAL TWELVE	& {\unicodefont Ⅻ}	&0x216b &	0x216b	& 0x58 0x49 0x49 &	0x58 0x49 0x49 \\
-\hline
-LATIN CAPITAL LETTER X - LATIN CAPITAL LETTER I - LATIN CAPITAL LETTER I &	XII &	0x58 0x49 0x49 &	0x58 0x49 0x49&	0x58(X) 0x49(I) 0x49(I) &	0x58 0x49 0x49 \\
-\hline
-VULGAR FRACTION ONE QUARTER	& \char"00BC &	0xbc &	0xbc &	0x31(1) 0x2044(/) 0x34(4) &	0x31 0x2044 0x34 \\
-\hline
-DIGIT ONE - SOLIDUS - DIGIT 4 &	1⁄4 &	0x31  0x2f 0x34 &	0x31 0x2f 0x34	& 0x31 0x2f 0x34 &	0x31 0x2f 0x34\\
-\hline
-DIGIT ONE - SOLIDUS - DIGIT 4 &	1⁄4 &	0x31  0x2f 0x34 &	0x31 0x2f 0x34	& 0x31 0x2f 0x34 &	0x31 0x2f 0x34\\
-\hline
-DIGIT ONE - FRACTION SLASH - DIGIT 4 & 1⁄4 &	0x31 0x2044 0x34 &	0x31 0x2044 0x34 &	0x31 0x2044 0x34 &	0x31 0x2044 0x34 \\
-\hline
-THERE EXISTS	& {\unicodefont ∃}&	0x2203 &	0x2203 &	0x2203 &	0x2203 \\
-\hline
-THERE DOES NOT EXIST	& {\unicodefont ∄} & 	0x2204	& 0x2203 0x338& 	0x2204 &	0x2203 0x338\\
-\hline
-LATIN CAPITAL LETTER OPEN E	& {\unicodefont Ɛ} &	0x190 &	0x190 &	0x190 &	0x190 \\
-\hline
-EULER CONSTANT	& {\unicodefont ℇ} & 0x2107 & 0x2107 & 0x190 & 0x190 \\
-\hline
-PLANCK CONSTANT	& {\unicodefont ℎ} &	0x210e &	0x210e &	0x68 &	0x68 \\
-\hline
-LATIN SMALL LETTER H &	h &	0x68 &	0x68 &	0x68 &	0x68 \\
-\hline
-PLANCK CONSTANT OVER TWO PI	& {\unicodefont ℏ} &	0x210f &	0x210f	& 0x127 &	0x127 \\
-\hline
-LATIN SMALL LETTER H WITH STROKE & ħ &	0x127	& 0x127	& 0x127	& 0x127 \\
-\hline
-GREEK CAPITAL LETTER OMEGA	& Ω &	0x3a9 &	0x3a9 &	0x3a9 &	0x3a9 \\
-\hline
-OHM SIGN & Ω &	0x2126 &	0x2126 &	0x3a9 &	0x3a9 \\
-\hline
-INTEGRAL & {\unicodefont ∫} &	0x222b &	0x222b &	0x222b &	0x222b \\
-\hline
-DOUBLE INTEGRAL	& {\unicodefont ∬} & 	0x222c &	0x222c &	0x222b 0x222b &	0x222b 0x222b \\
-\hline
-CONTOUR INTEGRAL	& {\unicodefont ∮} &	0x222e	 &0x222e &	0x222e &	0x222e \\
-\hline
-NABLA	& {\unicodefont ∇} &	0x2207	 &0x2207 &	0x2207 &	0x2207 \\
-\hline
-WHITE DOWN-POINTING TRIANGLE	& {\unicodefont ▽} &	0x25bd	 &0x25bd &	0x25bd &	0x25bd \\
-\hline
-
-\caption{Characters with similar glyphs and/or semantics}
-\label{unicode_characters}
-\end{longtable}
-
 Since our goal is to match as many similar characters as possible, our system employs the NFKD representation of a character.
@@
 	\centering
-	\includegraphics[height=2 cm]{figures/integrals.png}
+	\includegraphics[height=2 cm]{images/figures/integrals.png}
 	\caption{List of different types of integral related characters in Unicode}
@@
 	\centering
-	\includegraphics[height=2 cm]{figures/greater_less.png}
+	\includegraphics[height=2 cm]{images/figures/greater_less.png}
 	\caption{List of different types of greater/less than related characters in Unicode}
@@
 
-\section{Integration with Mathematica}
+\subsection{Integration with Mathematica}
 This section describes some aspects that had to be considered while implementing the integration with Mathematica.
@@
 
-\begin{longtable}{|>{\centering\arraybackslash}m{4.5cm}|>
-{\centering\arraybackslash}m{4.5cm}|>
-{\centering\arraybackslash}m{4.5cm}|}
-\hline
-\small{Original Form} & \small{{\codefont Simplify}} & \small{{\codefont FullSimplify}} \\
-\hline
-\scriptsize{\codefont <math> <mrow> <mrow> <mfrac> <msup> <mi>Φ</mi> <mo>′</mo> </msup> <mrow> <mn>2</mn> <mo>⁢</mo> <mrow> <mo>(</mo> <mrow> <mn>1</mn> <mo>+</mo> <mi>Φ</mi> </mrow> <mo>)</mo> </mrow> </mrow> </mfrac> <mo>+</mo> <mfrac> <mn>1</mn> <mi>r</mi> </mfrac> </mrow> <mo>=</mo> <mn>0</mn> </mrow> </math> }      & \scriptsize{\codefont <math> <mrow> <mrow> <mfrac> <mn>1</mn> <mi>r</mi> </mfrac> <mo>+</mo> <mfrac> <msup> <mi>Φ</mi> <mo>′</mo> </msup> <mrow> <mrow> <mn>2</mn> <mo>⁢</mo> <mi>Φ</mi> </mrow> <mo>+</mo> <mn>2</mn> </mrow> </mfrac> </mrow> <mo></mo> <mn>0</mn> </mrow> </math>}    & \scriptsize{\codefont <math> <mrow> <mrow> <mfrac> <mn>2</mn> <mi>r</mi> </mfrac> <mo>+</mo> <mfrac> <msup> <mi>Φ</mi> <mo>′</mo> </msup> <mrow> <mi>Φ</mi> <mo>+</mo> <mn>1</mn> </mrow> </mfrac> </mrow> <mo></mo> <mn>0</mn> </mrow> </math>}     \\
-$\frac{\Phi '}{2 (1+\Phi )}+\frac{1}{r}=0$          & $\frac{1}{r}+\frac{\Phi '}{2 \Phi +2}=0$ & $\frac{2}{r}+\frac{\Phi '}{\Phi +1}=0$       \\
-
-\hline
-
-\scriptsize{\codefont <math> <mrow> <mrow> <mfrac> <mn>1</mn> <mn>2</mn> </mfrac> <mo>⁢</mo> <msup> <mi>x</mi> <mn>2</mn> </msup> <mo>⁢</mo> <mrow> <mi>log</mi> <mo>⁡</mo> <mrow> <mo>(</mo> <mrow> <mn>1</mn> <mo>-</mo> <msup> <mi>e</mi> <mrow> <mo>-</mo> <mrow> <mn>2</mn> <mo>⁢</mo> <mi>x</mi> </mrow> </mrow> </msup> </mrow> <mo>)</mo> </mrow> </mrow> </mrow> <mo>-</mo> <mrow> <mfrac> <mn>1</mn> <mn>2</mn> </mfrac> <mo>⁢</mo> <mi>x</mi> <mo>⁢</mo> <mi>L</mi> <mo>⁢</mo> <msub> <mi>i</mi> <mn>2</mn> </msub> <mo>⁢</mo> <mrow> <mo>(</mo> <msup> <mi>e</mi> <mrow> <mo>-</mo> <mrow> <mn>2</mn> <mo>⁢</mo> <mi>x</mi> </mrow> </mrow> </msup> <mo>)</mo> </mrow> </mrow> <mo>-</mo> <mrow> <mfrac> <mn>1</mn> <mn>4</mn> </mfrac> <mo>⁢</mo> <mi>L</mi> <mo>⁢</mo> <msub> <mi>i</mi> <mn>3</mn> </msub> <mo>⁢</mo> <mrow> <mo>(</mo> <msup> <mi>e</mi> <mrow> <mo>-</mo> <mrow> <mn>2</mn> <mo>⁢</mo> <mi>x</mi> </mrow> </mrow> </msup> <mo>)</mo> </mrow> </mrow> </mrow> </math> }      & \scriptsize{\codefont <math> <mrow> <mfrac> <mn>1</mn> <mn>4</mn> </mfrac> <mo>⁢</mo> <msup> <mi>e</mi> <mrow> <mrow> <mo>-</mo> <mn>2</mn> </mrow> <mo>⁢</mo> <mi>x</mi> </mrow> </msup> <mo>⁢</mo> <mrow> <mo>(</mo> <mrow> <mrow> <mn>2</mn> <mo>⁢</mo> <msup> <mi>x</mi> <mn>2</mn> </msup> <mo>⁢</mo> <msup> <mi>e</mi> <mrow> <mn>2</mn> <mo>⁢</mo> <mi>x</mi> </mrow> </msup> <mo>⁢</mo> <mrow> <mi>log</mi> <mo>⁡</mo> <mo>(</mo> <mrow> <mn>1</mn> <mo>-</mo> <msup> <mi>e</mi> <mrow> <mrow> <mo>-</mo> <mn>2</mn> </mrow> <mo>⁢</mo> <mi>x</mi> </mrow> </msup> </mrow> <mo>)</mo> </mrow> </mrow> <mo>-</mo> <mrow> <mn>2</mn> <mo>⁢</mo> <msub> <mi>i</mi> <mn>2</mn> </msub> <mo>⁢</mo> <mi>L</mi> <mo>⁢</mo> <mi>x</mi> </mrow> <mo>-</mo> <mrow> <msub> <mi>i</mi> <mn>3</mn> </msub> <mo>⁢</mo> <mi>L</mi> </mrow> </mrow> <mo>)</mo> </mrow> </mrow> </math> }    & \scriptsize{\codefont <math> <mrow> <mrow> <mfrac> <mn>1</mn> <mn>2</mn> </mfrac> <mo>⁢</mo> <msup> <mi>x</mi> <mn>2</mn> </msup> <mo>⁢</mo> <mrow> <mi>log</mi> <mo>⁡</mo> <mo>(</mo> <mrow> <mn>1</mn> <mo>-</mo> <msup> <mi>e</mi> <mrow> <mrow> <mo>-</mo> <mn>2</mn> </mrow> <mo>⁢</mo> <mi>x</mi> </mrow> </msup> </mrow> <mo>)</mo> </mrow> </mrow> <mo>-</mo> <mrow> <mfrac> <mn>1</mn> <mn>4</mn> </mfrac> <mo>⁢</mo> <mi>L</mi> <mo>⁢</mo> <msup> <mi>e</mi> <mrow> <mrow> <mo>-</mo> <mn>2</mn> </mrow> <mo>⁢</mo> <mi>x</mi> </mrow> </msup> <mo>⁢</mo> <mrow> <mo>(</mo> <mrow> <mrow> <mn>2</mn> <mo>⁢</mo> <msub> <mi>i</mi> <mn>2</mn> </msub> <mo>⁢</mo> <mi>x</mi> </mrow> <mo>+</mo> <msub> <mi>i</mi> <mn>3</mn> </msub> </mrow> <mo>)</mo> </mrow> </mrow> </mrow> </math>}     \\
-\scriptsize{ $\frac{1}{2} x^2 \log \left(1-e^{-2 x}\right) - \frac{1}{2} x L i_ 2 \left(e^{-2 x}\right)-\frac{1}{4} L i_ 3 \left(e^{-2 x}\right)$ }          & \scriptsize { \begin{multline}  \frac{1}{4} e^{-2 x} (2 x^2 e^{2 x} \log (1-e^{-2 x})- \notag\\ 2 i_ 2 L x-i_ 3 L)  \end{multline} } & \scriptsize{ $\frac{1}{2} x^2 \log \left(1-e^{-2 x}\right)-\frac{1}{4} L e^{-2 x} \left(2 i_ 2 x+i_ 3\right)$ }      \\
-\hline
-\caption{Comparison of different simplification modes}
-
-\label{comparison_simplification}
-
-\end{longtable}
 \subsection{Recursive interpretation}
@@
 \begin{figure}[h!]
-\includegraphics[height=4.2 cm]{visio_drawings/architecture.png}
+\includegraphics[height=3 cm]{images/visio_drawings/architecture.png}
 \label{system_arch}
@@
 \center
-\includegraphics[height=6.2 cm]{figures/input_interface.png}
+\includegraphics[height=3 cm]{images/figures/input_interface.png}
 \label{input_int}
@@
 \center
-\includegraphics[height=6.2 cm]{figures/results_interface.png}
+\includegraphics[height=3 cm]{images/figures/results_interface.png}
 \label{results_int}

### 2014-11-23 jcdl2015/paper/main.tex
Completed v1 of demo version of paper.

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\usepackage{amsmath}
+
+\usepackage[mathletters]{ucs}
+\usepackage{amssymb}
+\usepackage[utf8x]{inputenc}
+\usepackage[cyr]{aeguill}
+\usepackage[english]{babel}
+\usepackage{fancyhdr, ifpdf}
+\usepackage{array}
+\usepackage{multirow}
+\usepackage{textcomp}
+\usepackage{verbatim} 
+\usepackage{listings}
+\usepackage{hyperref}
+\usepackage{dsfont}
 \usepackage{fontspec}
-\usepackage[utf8x]{inputenc}
-\usepackage{listings}
+\usepackage{booktabs}
+\usepackage{amsmath,amssymb,amstext,mathtext}
+\usepackage{tabularx}
 \usepackage{longtable}
 \usepackage{url}
+\usepackage{spverbatim}
+\usepackage{changepage}
+\usepackage{caption}
+\usepackage{subcaption}
 
+\makeatletter
+\def\url@leostyle{%
+  \@ifundefined{selectfont}{\def\UrlFont{\sf}}{\def\UrlFont{\small\ttfamily}}}
+\makeatother
+
+\newcommand{\loadencoding}[1]{%
+  \begingroup
+  \def\DeclareUnicodeCharacter##1##2{%
+    \expandafter\gdef\csname uni\number"##1\endcsname
+      {{\fontencoding{#1}\selectfont##2}}}
+  \makeatletter
+  \lowercase{\input{#1enc.dfu}}%
+  \endgroup}
+\newcommand\unisymbol[1]{\csname uni\number#1\endcsname}
+\loadencoding{T1}
+\loadencoding{T2A}
 \newfontfamily\unicodefont{Arial Unicode MS}
@@
 \section{Introduction}
-\include{section-introduction}
-\include{section-related_work}
-\include{section-system_description}
-\include{section-evaluation}
-\include{section-conclusions}
+CDS\cite{CDS1} (CERN Document Server) is the institutional digital library system
+developed and used at CERN\cite{CERN}.
+It contains more than 1 million records and stores more than 400000 full text documents, organized in different collections among published articles, books, preprints.
+Invenio\cite{invenio} is the open-source digital library software platform behind CDS and is developed in parallel to CDS at CERN.
+Besides CDS, Invenio supports around thirty scientific institutions worldwide including INSPIRE (a collaboration between Fermilab, CERN, DESY and SLAC) EPFL and ILO.
+An important part of the CDS content contains mathematical content, represented in the form of equations.
+Only the Preprints collection contains more than 700000 records, harvesting documents from services like ArXiV\cite{arxiv} where most of the documents are in the areas of physics, mathematics and statistics which are very rich in this type of content.
+Even though Invenio provides a powerful searching mechanism that allows to query the stored records by different fields like author or keywords, these approaches are not suitable to query this type of content.
+$5e^{x+y}$ is developed as a first attempt to address this limitation by allowing querying for records based on mathematical equations.
+
+\section{System Overview}
+In this section we provide a general overview of the main design points of $5e^{x+y}$. A more detailed description of the system can be found in \cite{mathexplorerweb}.
+\subsection{Features Extraction}
+Our initial focus in the project was to define a good set of features that we could extract and index from our equations.
+We divided them, into two different categories.
+The notational features relate to the actual naming and representation of the different elements of the equation.
+The selected format for representing and internal processing of the equations was MathML because it allows an easier processing.
+
+For notational features, we extracted the leave elements of the equation: variables, numbers and operator represented by the tags <mi>, <mn> and <mo> respectively.
+We indexed as well 2-grams and 3-grams of symbol-operator and symbol-operator-symbol.
+We perform some processing of these tokens such as normalizing and decomposing of complex characters.
+This allowed us to partially match characters with different unicode points but similar or equal visual rendering.
+For instance LATIN CAPITAL LETTER A WITH RING ABOVE with code 0xc5 and ANGSTROM SIGN with code 0x212b both are rendered as \r{A} and both can be used to refer to the Angstrom measurement unit.
+Following the example, we indexed both the original token <mi>\r{A}</mi> and the normalized form <mi>\r{A}</mi> <mi>A</mi>.
+Another set of rules that we applied take into account the different types of operators that are semantically related but whose unicode representation does not provide meaningful ways to match them.
+We grouped related operators, for example the INTEGRAL character with code 0x222b generates the tokens <mo>{\unicodefont ∫}</mo> and INT\_OP and the CONTOUR INTEGRAL character with code 0x222e generates the tokens <mo>{\unicodefont ∮} </mo> and INT\_OP.
+In this way, both have a partial matching in the second token.
+
+The second set of features relate to the structure of the equation.
+Two different properties of mathematical equations impose additional challenges for a MIR system.
+First, variables can be used indistinguishable and any character set of characters can be used to represent the same equation.
+$f(t) = vt + c $ and $g(x) = ac + b$ can represent the same linear equation though the context in which each variable is used follows certain conventions.
+For addressing this issue, we relied on pattern matching, a very powerful feature that current Computer Algebra System (CAS) provide.
+We integrated Mathematica into our system, to perform pattern matching on the equations and identify the occurrence of a predefined of patterns from a predefined set.
+This allows us to detect if the equation contained certain types of common algebraic structures.
+For instance, the pattern {\codefont a\_.x\^{} 2 + b\_.x + c\_.} is used to identify quadratic expression.
+This mechanism is very powerful since \.x represent any type of expression, not only a single term.
+
+A second additional challenge that math equations pose is the fact that a given equality can be rewritten in multiple ways taking into account properties of the different operators like associativity, distributivity, commutativity among others.
+Our approach was to rely again in the features provided by Mathematica and apply the {\codefont Simplify} operations which applies a set of predefined set of rules in a equation with the goal of having a unique and concise representation.
+
+\subsection{System architecture}
+$5e^{x+y}$ is implemented in top of the Lucene/Solr framework.
+We expanded the default schema with  several fields, being the most important ones: {\codefont math\_notational\_field} which stores all the described tokens and n-grams, \\ {\codefont math\_structural\_field} which stores the occurrences of predefined algebraic structures and {\codefont filename} which is used to store the file/record where the particular equation was found.
+In order to extend Lucene with the new use case, our work extends some of the base classes as follows: {\codefont MultiplePatternTokenizer} is in charge of producing a stream of tokens from a single equations.
+This tokens are identified by applying multiple regular expressions.
+{\codefont UnicodeNormalizingFilter} applies the unicode normalizing transformation described above.
+{\codefont SynonymExpandingFilter} expands operators, with a manually computed table, with the category they belong to.
+Finally {\codefont StructuralPatternsTokenizer} provides the pattern matching functionality by establishing  a communication with Mathematica's {\codefont Kernel Link} API.
+
+\section{Demonstration}
+As part of the demonstration of $5e^{x+y}$, we present a demo instance of the Invenio software with the searching by mathematical equations functionality.
+The user access the math searching functionality through a link in the main page.
+Once there, the user is presented with a classic search functionality where the user inputs his equation.
+He can choose between writing the query on \LaTeX or MathML.
+For writing the \LaTeX code, we include an online editor\cite{latex_editor} that renders the the input as the user types it.
+The first format is normally more familiar to users , however, the internal representation is in MathML since it allows an easier processing.
+The translation from \LaTeX  to MathML is done through the third party library SnuggleTex\cite{snuggletex} that have some shortcomings, so we allow users to input the query in MathML as well.
+When the query is ready, the user clicks the submit button and the system performs the search.
+Once the system has performed the lookup and got the results, these are presented in the results interface.
+The system shows up the 20 results with highest score. Each result shows the matched equation snippet, the title of the record containing the given equation and the link to the record.
+
+%\begin{figure}
+%\center
+%\includegraphics[height=3 cm]{images/figures/input_interface.png}
+%\label{input_int}
+%\caption{Web interface of $5e^{x+y}$: Query input screen}
+%\end{figure}
+%
+%\begin{figure}
+%\center
+%\includegraphics[height=3 cm]{images/figures/results_interface.png}
+%\label{results_int}
+%\caption{Web interface of $5e^{x+y}$: Results screen}
+%\end{figure}
+
+\begin{figure}
+\centering
+\begin{minipage}{.27\textwidth}
+  \includegraphics[width=0.9\linewidth]{images/figures/input_interface.png}
+  \captionof{figure}{Input interface.}
+  \label{fig:test1}
+\end{minipage}%
+\begin{minipage}{.27\textwidth}
+  \includegraphics[width=0.9\linewidth]{images/figures/results_interface.png}
+  \captionof{figure}{Result page.}
+  \label{fig:test2}
+\end{minipage}
+\end{figure}
+
+\section{Conclusions}
+
+\section{Availability}
+Both, the Invenio software and the $5e^{x+y}$ module are open source available through GPL Licence.
+Invenio can be downloaded from \url{http://invenio-software.org/}.
+$5e^{x+y}$ can be downloaded from \\ \url{https://github.com/arthoviedo/cern_math_explorer} .
 
 %ACKNOWLEDGMENTS are optional
-\section{Acknowledgments}
-We would like to thanks the ScienceWISE team for the help and important insights that they provided for the realization of this project.
-
 %

### 2015-01-08 jcdl2015/paper/main.tex
Some grammar, syntax etc fixes from Nikos

--- 2014-11-04 jcdl2015/paper/main.tex
@@
   \affaddr{arthur.oviedo@alumini.epfl.ch}%
-\alignauthor Nikolaos Kasioumis \\
+\alignauthor Nikos Kasioumis \\
   \affaddr{CERN, Switzerland.}\\%
@@
 \section{Introduction}
-\include{section-introduction}
-\include{section-related_work}
-\include{section-system_description}
-\include{section-evaluation}
-\include{section-conclusions}
+CDS\cite{CDS1} (CERN Document Server) is the institutional digital repository
+developed and used at CERN\cite{CERN}.
+It contains more than 1 million records and stores more than 400,000 full text documents, organized in different collections among published articles, books, preprints.
+Invenio\cite{invenio} is the open-source digital library software platform behind CDS and is developed in parallel to CDS at CERN.
+Besides CDS, Invenio supports around thirty scientific institutions worldwide including INSPIRE (a collaboration between Fermilab, CERN, DESY and SLAC) EPFL and ILO.
+A considerable amount of the full text documents on CDS contain mathematical content, represented in the form of equations.
+The Preprints collection alone contains more than 700,000 records, harvesting documents from services like ArXiV\cite{arxiv} where most of the documents are in the areas of physics, mathematics and statistics which are very rich in this type of content.
+Even though Invenio provides a powerful search engine that allows users to query records using different fields like author or keywords, it is not suitable for mathematical content.
+$5e^{x+y}$ is developed as a first attempt to address this limitation by allowing querying for records based on mathematical equations.
+
+\section{System Overview}
+In this section we provide a general overview of the main design points of $5e^{x+y}$. A more detailed description of the system can be found in \cite{mathexplorerweb}.
+
+\subsection{Features Extraction}
+Our initial focus in the project was to define a good set of features that we could extract and index from our equations.
+We divide them into two different categories: notational and structural features.
+
+The notational features relate to the actual naming and representation of the different elements of the equation.
+The selected format for representation and internal processing of the equations was MathML because it allows an easier processing.
+For the notational features we extract the leave elements of the equation: variables, numbers and operators represented by the <mi>, <mn> and <mo> tags respectively.
+In addition, we index 2-grams and 3-grams of symbol-operator and symbol-operator-symbol sequences.
+
+We perform some processing of these tokens such as normalizing and decomposing of complex characters.
+This allows us to partially match characters with different unicode points but similar or equal visual rendering.
+For instance LATIN CAPITAL LETTER A WITH RING ABOVE with code 0xc5 and ANGSTROM SIGN with code 0x212b both are rendered as \r{A} and can both be used to refer to the Angstrom measurement unit.
+Following this example, we index both the original token <mi>\r{A}</mi> and the normalized form <mi>\r{A}</mi> <mi>A</mi>.
+Another set of rules that we apply take into account the different types of operators that are semantically related but whose unicode representation does not provide meaningful ways to match them and groups them.
+For example the INTEGRAL character with code 0x222b generates the tokens <mo>{\unicodefont ∫}</mo> and INT\_OP and the CONTOUR INTEGRAL character with code 0x222e generates the tokens <mo>{\unicodefont ∮} </mo> and INT\_OP.
+In this way, both have a partial matching in the second token.
+
+The second set of features relate to the structure of the equation.
+Two different properties of mathematical equations impose additional challenges for a Mathematics Information Retrieval (MIR) system.
+First, variables can be used indistinguishably and any character set can be used to represent the same equation.
+For example, $f(t) = vt + c $ and $g(x) = ac + b$ can represent the same linear equation, however the context in which each variable is used follows certain conventions.
+To address this issue, we relied on pattern matching, a very powerful feature that current Computer Algebra Systems (CAS) provide.
+We integrated Mathematica into our system, to perform pattern matching on the equations and identify occurrences within a predefined set of patterns.
+This allows us to detect if the equation contains certain types of common algebraic structures.
+For instance, the pattern {\codefont a\_.x\^{} 2 + b\_.x + c\_.} is used to identify a quadratic expression.
+This mechanism is very powerful since \.x represents any type of expression, not only a single term.
+
+An additional challenge that mathematical equations pose is the fact that a given equality can be rewritten in multiple ways taking into account properties of the different operators like associativity, distributivity and commutativity among others.
+Our approach relies once more in the features provided by Mathematica: we perform the {\codefont Simplify} operation which applies a set of predefined rules on a given equation with the goal of providing a unique and concise representation.
+
+\subsection{System architecture}
+$5e^{x+y}$ is implemented on top of the Lucene/Solr framework.
+We expanded the default schema with several fields, the most important ones being: the {\codefont math\_notational\_field} which stores all the described tokens and n-grams, \\ the {\codefont math\_structural\_field} which stores the occurrences of predefined algebraic structures and the {\codefont filename} which is used to store the file/record where the particular equation was found.
+
+In order to extend Lucene with the new use case, our work extends some of the base classes as follows: {\codefont MultiplePatternTokenizer} is in charge of producing a stream of tokens from a single equation.
+These tokens are identified by applying multiple regular expressions.
+{\codefont UnicodeNormalizingFilter} applies the unicode normalizing transformation described above.
+{\codefont SynonymExpandingFilter} expands operators, using a manually computed table, with the category they belong to.
+Finally {\codefont StructuralPatternsTokenizer} provides the pattern matching functionality by establishing communication with Mathematica's {\codefont Kernel Link} API.
+
+\section{Demonstration}
+As part of the demonstration of $5e^{x+y}$, we present a demo instance of the Invenio software with the mathematical equations search functionality.
+The user can access the mathematical search functionality through a link in the main page.
+Once there, the user is presented with a classic search functionality where the he or she can input an equation.
+The equation can be expressed in either \LaTeX or MathML.
+To ease the writing of \LaTeX code, we include an online editor\cite{latex_editor} that renders the input as the user types it.
+\LaTeX code is usually more familiar to users, however, the internal representation is in MathML since it allows for easier processing.
+The translation from \LaTeX to MathML is done through the third party library SnuggleTex\cite{snuggletex} that has some shortcomings, so we allow users to input the query in MathML as well.
+When the query is ready, the user can click the submit button and the system then performs the search.
+Once the system has performed the lookup and produced the results, they are presented to the user.
+The system displays the 20 results with the highest score. Each result shows the matched equation snippet, the title of the record containing the given equation and the link to the record.
+
+%\begin{figure}
+%\center
+%\includegraphics[height=3 cm]{images/figures/input_interface.png}
+%\label{input_int}
+%\caption{Web interface of $5e^{x+y}$: Query input screen}
+%\end{figure}
+%
+%\begin{figure}
+%\center
+%\includegraphics[height=3 cm]{images/figures/results_interface.png}
+%\label{results_int}
+%\caption{Web interface of $5e^{x+y}$: Results screen}
+%\end{figure}
+
+\begin{figure}
+\centering
+\begin{minipage}{.27\textwidth}
+  \includegraphics[width=0.9\linewidth]{images/figures/input_interface.png}
+  \captionof{figure}{Input interface.}
+  \label{fig:test1}
+\end{minipage}%
+\begin{minipage}{.27\textwidth}
+  \includegraphics[width=0.9\linewidth]{images/figures/results_interface.png}
+  \captionof{figure}{Result page.}
+  \label{fig:test2}
+\end{minipage}
+\end{figure}
+
+\section{Conclusions}
+?
+
+\section{Availability}
+Both the Invenio software and the $5e^{x+y}$ module are open-source software available through GPL Licence.
+Invenio can be downloaded from \url{http://invenio-software.org/}.
+$5e^{x+y}$ can be downloaded from \\ \url{https://github.com/arthoviedo/cern_math_explorer}.
 
 %ACKNOWLEDGMENTS are optional
-\section{Acknowledgments}
-We would like to thanks the ScienceWISE team for the help and important insights that they provided for the realization of this project.
-
 %

### 2015-01-17 jcdl2015/paper/main.tex
Addressed comments from Nikos, minor fixes, added the fact that our system is easy to integrate with other DL, changed title

@@
 % --- Author Metadata here ---
-\conferenceinfo{JCDL}{2014 Knoxville, USA}
+\conferenceinfo{JCDL}{2015 Knoxville, USA}
 %\CopyrightYear{2007} % Allows default copyright year (20XX) to be over-ridden - IF NEED BE.
@@
 
-\title{$5e^{x+y}$: A Math Aware Search Engine (for CDS)}
+\title{$5e^{x+y}$: Enabling searching over mathematical content in digital libraries.}
 
@@
 This paper presents $5e^{x+y}$, a system that complements CERN Document Server (CDS), by adding extracting, indexing and querying of mathematical content, expressed as mathematical equations.
+We present the most important aspects of its design and provide a demonstration of its searching capabilities.
+
 \end{abstract}
@@
 developed and used at CERN\cite{CERN}.
-It contains more than 1 million records and stores more than 400,000 full text documents, organized in different collections among published articles, books, preprints.
+It contains more than 1 million records and stores more than 400,000 full text documents, organized in different collections among published articles, books and preprints.
 Invenio\cite{invenio} is the open-source digital library software platform behind CDS and is developed in parallel to CDS at CERN.
@@
 We divide them into two different categories: notational and structural features.
-
 The notational features relate to the actual naming and representation of the different elements of the equation.
-The selected format for representation and internal processing of the equations was MathML because it allows an easier processing.
-For the notational features we extract the leave elements of the equation: variables, numbers and operators represented by the <mi>, <mn> and <mo> tags respectively.
+The selected format for representation and internal processing of the equations was MathML.
+This language allows an easier processing because of its markup nature and has a stronger support from the W3C among other communities.
+For the notational features we extract the leaf elements of the equation: variables, numbers and operators represented by the <mi>, <mn> and <mo> tags respectively.
 In addition, we index 2-grams and 3-grams of symbol-operator and symbol-operator-symbol sequences.
@@
 For instance LATIN CAPITAL LETTER A WITH RING ABOVE with code 0xc5 and ANGSTROM SIGN with code 0x212b both are rendered as \r{A} and can both be used to refer to the Angstrom measurement unit.
-Following this example, we index both the original token <mi>\r{A}</mi> and the normalized form <mi>\r{A}</mi> <mi>A</mi>.
-Another set of rules that we apply take into account the different types of operators that are semantically related but whose unicode representation does not provide meaningful ways to match them and groups them.
+Following this example, we index both the original token <mi>\r{A}</mi> and the normalized form <mi>\r{A}</mi> <mi>A</mi>.For operators which are semantically related such as comparison, integrals and arithmetic, we apply another set of rules since their unicode characters do not provide an easy way to match them.
 For example the INTEGRAL character with code 0x222b generates the tokens <mo>{\unicodefont ∫}</mo> and INT\_OP and the CONTOUR INTEGRAL character with code 0x222e generates the tokens <mo>{\unicodefont ∮} </mo> and INT\_OP.
@@
 To address this issue, we relied on pattern matching, a very powerful feature that current Computer Algebra Systems (CAS) provide.
-We integrated Mathematica into our system, to perform pattern matching on the equations and identify occurrences within a predefined set of patterns.
+We integrated Mathematica\cite{mathematica} into our system, to perform pattern matching on the equations and identify occurrences within a predefined set of patterns.
 This allows us to detect if the equation contains certain types of common algebraic structures.
 For instance, the pattern {\codefont a\_.x\^{} 2 + b\_.x + c\_.} is used to identify a quadratic expression.
-This mechanism is very powerful since \.x represents any type of expression, not only a single term.
+This mechanism is very powerful since \_.x represents any type of expression, not only a single term.
 
-An additional challenge that mathematical equations pose is the fact that a given equality can be rewritten in multiple ways taking into account properties of the different operators like associativity, distributivity and commutativity among others.
-Our approach relies once more in the features provided by Mathematica: we perform the {\codefont Simplify} operation which applies a set of predefined rules on a given equation with the goal of providing a unique and concise representation.
+An additional challenge mathematical equations pose is the fact that a given equality can be rewritten in multiple ways taking into account properties of the different operators like associativity, distributivity and commutativity among others.
+Our approach relies once more in the features provided by Mathematica: we perform the {\codefont Simplify} operation which applies a set of predefined rules on a given equation with the goal of providing a canonical representation.
 
 \subsection{System architecture}
-$5e^{x+y}$ is implemented on top of the Lucene/Solr framework.
+$5e^{x+y}$ is implemented on top of the Lucene/Solr \cite{solr} framework.
 We expanded the default schema with several fields, the most important ones being: the {\codefont math\_notational\_field} which stores all the described tokens and n-grams, \\ the {\codefont math\_structural\_field} which stores the occurrences of predefined algebraic structures and the {\codefont filename} which is used to store the file/record where the particular equation was found.
@@
 {\codefont UnicodeNormalizingFilter} applies the unicode normalizing transformation described above.
-{\codefont SynonymExpandingFilter} expands operators, using a manually computed table, with the category they belong to.
+{\codefont SynonymExpandingFilter} expands operators, using a manually computed table based on \cite{math_groups}, with the category they belong to.
 Finally {\codefont StructuralPatternsTokenizer} provides the pattern matching functionality by establishing communication with Mathematica's {\codefont Kernel Link} API.
+
+To integrate $5e^{x+y}$ with Invenio, we used the {\codefont solrpy} library which communicates with an instance of Solr running $5e^{x+y}$ as a plugin.
+Since Solr provides different integrating mechanisms with external systems, $5e^{x+y}$ can be easily be incorporated into different digital libraries.
 
@@
 The user can access the mathematical search functionality through a link in the main page.
-Once there, the user is presented with a classic search functionality where the he or she can input an equation.
+Once there, the user is presented with a classic search functionality where they can input an equation.
 The equation can be expressed in either \LaTeX or MathML.
 To ease the writing of \LaTeX code, we include an online editor\cite{latex_editor} that renders the input as the user types it.
-\LaTeX code is usually more familiar to users, however, the internal representation is in MathML since it allows for easier processing.
+\LaTeX code is usually more familiar to users, however, the internal representation is in MathML as previously explained.
 The translation from \LaTeX to MathML is done through the third party library SnuggleTex\cite{snuggletex} that has some shortcomings, so we allow users to input the query in MathML as well.
@@
 \section{Conclusions}
-?
+In this demonstration, we presented $5e^{x+y}$, which complements CDS by enabling searching over mathematical content.
+We gave an overview of the main design points of the system, including the two types of features used to characterize and index equations, the integration with the Mathematica CAS which provides powerful functionalities such as pattern matching and equation simplification, our approach to extended the Lucene/Solr framework and our integration with the existing Invenio software through the solarpy library.
 

### 2015-01-25 jcdl2015/paper/main.tex
Slight rephrasing in the abstract and minor syntax fixes

@@
 \begin{abstract}
-This paper presents $5e^{x+y}$, a system that complements CERN Document Server (CDS), by adding extracting, indexing and querying of mathematical content, expressed as mathematical equations.
+This paper presents $5e^{x+y}$, a system that is able to extract, index and query mathematical content expressed as mathematical equations, complementing the CERN Document Server (CDS).
 We present the most important aspects of its design and provide a demonstration of its searching capabilities.
@@
 \section{Introduction}
-CDS\cite{CDS1} (CERN Document Server) is the institutional digital repository
-developed and used at CERN\cite{CERN}.
-It contains more than 1 million records and stores more than 400,000 full text documents, organized in different collections among published articles, books and preprints.
-Invenio\cite{invenio} is the open-source digital library software platform behind CDS and is developed in parallel to CDS at CERN.
+CDS\cite{CDS1} (CERN Document Server) is the institutional digital repository developed and used at CERN\cite{CERN}.
+It contains more than 1,000,000 records and stores more than 400,000 full text documents, organized in different collections among published articles, books and preprints.
+Invenio\cite{invenio} is the open-source digital library software platform behind CDS and it is developed in parallel to CDS at CERN.
 Besides CDS, Invenio supports around thirty scientific institutions worldwide including INSPIRE (a collaboration between Fermilab, CERN, DESY and SLAC) EPFL and ILO.
@@
 The selected format for representation and internal processing of the equations was MathML.
-This language allows an easier processing because of its markup nature and has a stronger support from the W3C among other communities.
+This language allows for easier processing because of its markup nature and has a stronger support from the W3C among other communities.
 For the notational features we extract the leaf elements of the equation: variables, numbers and operators represented by the <mi>, <mn> and <mo> tags respectively.
@@
 
-In order to extend Lucene with the new use case, our work extends some of the base classes as follows: {\codefont MultiplePatternTokenizer} is in charge of producing a stream of tokens from a single equation.
+In order to extend Lucene with the new use case, our work extends some of the base classes.
+{\codefont MultiplePatternTokenizer} is in charge of producing a stream of tokens from a single equation.
 These tokens are identified by applying multiple regular expressions.

### 2015-01-30 jcdl2015/paper/main.tex
Fix size of the project's name in the title. Fixed the url of one reference.
Changed minor details, rewrote conclussions, dropped keywords and general terms.

@@
+ 
 % This is "sig-alternate.tex" V2.0 May 2012
@@
 % --- Author Metadata here ---
-\conferenceinfo{JCDL}{2015 Knoxville, USA}
+\conferenceinfo{Joint Conference on Digital Libraries}{2015 Knoxville, USA}
 %\CopyrightYear{2007} % Allows default copyright year (20XX) to be over-ridden - IF NEED BE.
@@
 
-\title{$5e^{x+y}$: Enabling searching over mathematical content in digital libraries.}
+\title{  {\Huge $ \ttlfnt{5e^{x+y}}$}: Searching over mathematical content in digital libraries}
 
@@
 \begin{abstract}
-This paper presents $5e^{x+y}$, a system that is able to extract, index and query mathematical content expressed as mathematical equations, complementing the CERN Document Server (CDS).
-We present the most important aspects of its design and provide a demonstration of its searching capabilities.
+This paper presents $5e^{x+y}$, a system that is able to extract, index and query mathematical content expressed as mathematical equations, complementing the CERN Document Server (CDS)\cite{CDS1}.
+We present the most important aspects of its design, our approach to model the relevant features of the mathematical content, and provide a demonstration of its searching capabilities.
 
@@
 
-% A category with the (minimum) three required fields
-\category{X.X}{Digital Libraries}{Miscellaneous}
-%A category including the fourth, optional field follows...
-\category{Y.Y}{Information Retrieval}{Metrics}
-
-\terms{Theory}
-
-\keywords{ACM proceedings, \LaTeX, text tagging}
-
 \section{Introduction}
-CDS\cite{CDS1} (CERN Document Server) is the institutional digital repository developed and used at CERN\cite{CERN}.
+CDS (CERN Document Server) is the institutional digital repository developed and used at CERN\cite{CERN}.
 It contains more than 1,000,000 records and stores more than 400,000 full text documents, organized in different collections among published articles, books and preprints.
@@
 \section{Conclusions}
-In this demonstration, we presented $5e^{x+y}$, which complements CDS by enabling searching over mathematical content.
-We gave an overview of the main design points of the system, including the two types of features used to characterize and index equations, the integration with the Mathematica CAS which provides powerful functionalities such as pattern matching and equation simplification, our approach to extended the Lucene/Solr framework and our integration with the existing Invenio software through the solarpy library.
+
+In this demonstration, we presented an important limitation of CDS, and how our system, $5e^{x+y}$, provides efficient and precise searching capabilities over mathematical to our system.
+We presented our approach to model mathematical equations in terms of two different types of features.
+How we extended the Lucene/Solr Framework to handle our specific type of content and how through the Mathematica CAS, we were able to include powerful functionalities such as pattern matching and equation simplificiation to our system, and use them to improve the quality of the results.
+Finally we presented our integration mechanism with the Invenio software through the solarpy library.
 

### 2015-01-31 jcdl2015/paper/main.tex
Fixed a typo in conclusions, played with the size of the screenshots, managed to get them bigger without adding extra pages.

@@
 \centering
-\begin{minipage}{.27\textwidth}
-  \includegraphics[width=0.9\linewidth]{images/figures/input_interface.png}
+\begin{minipage}{.37\textwidth}
+  \includegraphics[width=0.95\linewidth]{images/figures/input_interface.png}
   \captionof{figure}{Input interface.}
@@
 \end{minipage}%
-\begin{minipage}{.27\textwidth}
-  \includegraphics[width=0.9\linewidth]{images/figures/results_interface.png}
+\end{figure}
+
+\begin{figure}
+\centering
+\begin{minipage}{.37\textwidth}
+  \includegraphics[width=0.95\linewidth]{images/figures/results_interface.png}
   \captionof{figure}{Result page.}
@@
 
-In this demonstration, we presented an important limitation of CDS, and how our system, $5e^{x+y}$, provides efficient and precise searching capabilities over mathematical to our system.
+In this demonstration, we focused on a limitation of CDS, and how our system, $5e^{x+y}$, provides efficient and precise searching capabilities over mathematical content.
 We presented our approach to model mathematical equations in terms of two different types of features.
-How we extended the Lucene/Solr Framework to handle our specific type of content and how through the Mathematica CAS, we were able to include powerful functionalities such as pattern matching and equation simplificiation to our system, and use them to improve the quality of the results.
+We extended the Lucene/Solr framework to handle specific type of content and through the Mathematica CAS we were able to include powerful functionalities such as pattern matching and equation simplificiation to our system, improving the quality of the results.
 Finally we presented our integration mechanism with the Invenio software through the solarpy library.

### 2015-02-01 jcdl2015/paper/main.tex

@@
 \centering
-\begin{minipage}{.37\textwidth}
-  \includegraphics[width=0.95\linewidth]{images/figures/input_interface.png}
+\begin{minipage}{.27\textwidth}
+  \includegraphics[width=0.9\linewidth]{images/figures/input_interface.png}
   \captionof{figure}{Input interface.}
@@
 \end{minipage}%
-\end{figure}
-
-\begin{figure}
-\centering
-\begin{minipage}{.37\textwidth}
-  \includegraphics[width=0.95\linewidth]{images/figures/results_interface.png}
+\begin{minipage}{.27\textwidth}
+  \includegraphics[width=0.9\linewidth]{images/figures/results_interface.png}
   \captionof{figure}{Result page.}
@@
 
-In this demonstration, we focused on a limitation of CDS, and how our system, $5e^{x+y}$, provides efficient and precise searching capabilities over mathematical content.
+In this demonstration, we focused on a a limitation of CDS, and how our system, $5e^{x+y}$, provides efficient and precise searching capabilities over mathematical content.
 We presented our approach to model mathematical equations in terms of two different types of features.

### 2015-04-12 jcdl2015/paper/main.tex
Fixed reviewers remarks.

--- 2015-01-31 jcdl2015/paper/main.tex
@@
   \affaddr{EPFL, Switzerland.}\\%
-  \affaddr{arthur.oviedo@alumini.epfl.ch}%
+  \affaddr{arthur.oviedo@alumni.epfl.ch}%
 \alignauthor Nikos Kasioumis \\
@@
 \begin{abstract}
-This paper presents $5e^{x+y}$, a system that is able to extract, index and query mathematical content expressed as mathematical equations, complementing the CERN Document Server (CDS)\cite{CDS1}.
+This paper presents $5e^{x+y}$, a system that is able to extract, index and query mathematical content expressed as mathematical expressions, complementing the CERN Document Server (CDS)\cite{CDS1}.
 We present the most important aspects of its design, our approach to model the relevant features of the mathematical content, and provide a demonstration of its searching capabilities.
@@
 $5e^{x+y}$ is developed as a first attempt to address this limitation by allowing querying for records based on mathematical equations.
+Several system have been developed in the context of Mathematical Information Retrieval (MIR).
+Our system, however, improves on them by modelling mathematical expressions in 2 different set of features and relying on specialized tools to manipulate and analyse them.
 
@@
 The second set of features relate to the structure of the equation.
-Two different properties of mathematical equations impose additional challenges for a Mathematics Information Retrieval (MIR) system.
+Two different properties of mathematical equations impose additional challenges for a MIR system.
 First, variables can be used indistinguishably and any character set can be used to represent the same equation.
@@
 Once the system has performed the lookup and produced the results, they are presented to the user.
-The system displays the 20 results with the highest score. Each result shows the matched equation snippet, the title of the record containing the given equation and the link to the record.
+The system displays the 20 results with the highest score.
+Each result shows the matched equation snippet, the title of the record containing the given equation and the link to the record as it can be observed in Figure \ref{fig:test2}.
 
@@
 
-\begin{figure}
-\centering
-\begin{minipage}{.37\textwidth}
-  \includegraphics[width=0.95\linewidth]{images/figures/input_interface.png}
-  \captionof{figure}{Input interface.}
-  \label{fig:test1}
-\end{minipage}%
-\end{figure}
+%\begin{figure}
+%\centering
+%\begin{minipage}{.37\textwidth}
+% \includegraphics[width=0.95\linewidth]{images/figures/input_interface.png}
+%  \captionof{figure}{Input interface.}
+%  \label{fig:test1}
+%\end{minipage}%
+%\end{figure}
 
@@
 \centering
-\begin{minipage}{.37\textwidth}
+\begin{minipage}{.55\textwidth}
   \includegraphics[width=0.95\linewidth]{images/figures/results_interface.png}
@@
 We presented our approach to model mathematical equations in terms of two different types of features.
-We extended the Lucene/Solr framework to handle specific type of content and through the Mathematica CAS we were able to include powerful functionalities such as pattern matching and equation simplificiation to our system, improving the quality of the results.
+We extended the Lucene/Solr framework to handle specific type of content and through the Mathematica CAS we were able to include powerful functionalities such as pattern matching and equation simplification to our system, improving the quality of the results.
 Finally we presented our integration mechanism with the Invenio software through the solarpy library.

### 2015-04-14 jcdl2015/paper/main.tex
Added copyright info

@@
 % --- Author Metadata here ---
-\conferenceinfo{Joint Conference on Digital Libraries}{2015 Knoxville, USA}
-%\CopyrightYear{2007} % Allows default copyright year (20XX) to be over-ridden - IF NEED BE.
-%\crdata{0-12345-67-8/90/01}  % Allows default copyright data (0-89791-88-6/97/05) to be over-ridden - IF NEED BE.
+\conferenceinfo{Joint Conference on Digital Libraries, JCDL'15}{June 21-25, 2015, Knoxville, TN, USA}
+\CopyrightYear{2015} % Allows default copyright year (20XX) to be over-ridden - IF NEED BE.
+\crdata{978-1-4503-3594-2/15/06 \\ http://dx.doi.org/10.1145/2756406.2756953}  % Allows default copyright data (0-89791-88-6/97/05) to be over-ridden - IF NEED BE.
 % --- End of Author Metadata ---
@@
 Invenio\cite{invenio} is the open-source digital library software platform behind CDS and it is developed in parallel to CDS at CERN.
-Besides CDS, Invenio supports around thirty scientific institutions worldwide including INSPIRE (a collaboration between Fermilab, CERN, DESY and SLAC) EPFL and ILO.
-A considerable amount of the full text documents on CDS contain mathematical content, represented in the form of equations.
+Besides CDS, Invenio supports around thirty scientific institutions worldwide including INSPIRE (a collaboration between Fermilab, CERN, DESY and SLAC), EPFL and ILO.
+A considerable amount of the full text documents on CDS contains mathematical content.
 The Preprints collection alone contains more than 700,000 records, harvesting documents from services like ArXiV\cite{arxiv} where most of the documents are in the areas of physics, mathematics and statistics which are very rich in this type of content.
 Even though Invenio provides a powerful search engine that allows users to query records using different fields like author or keywords, it is not suitable for mathematical content.
-$5e^{x+y}$ is developed as a first attempt to address this limitation by allowing querying for records based on mathematical equations.
+$5e^{x+y}$ is developed as a first attempt to address this limitation by allowing querying for records based on mathematical expressions.
 Several system have been developed in the context of Mathematical Information Retrieval (MIR).

### 2015-04-16 jcdl2015/paper/main.tex
Tiny corrections

@@
 $5e^{x+y}$ is developed as a first attempt to address this limitation by allowing querying for records based on mathematical expressions.
-Several system have been developed in the context of Mathematical Information Retrieval (MIR).
-Our system, however, improves on them by modelling mathematical expressions in 2 different set of features and relying on specialized tools to manipulate and analyse them.
+Compared to existing systems in the context of Mathematical Information Retrieval (MIR), our system improves on them by modelling mathematical expressions using 2 distinct set of features and relying on specialized tools to manipulate and analyse them.
 

### 2015-04-26 jcdl2015/paper/main.tex
Capitalized title

@@
 
-\title{  {\Huge $ \ttlfnt{5e^{x+y}}$}: Searching over mathematical content in digital libraries}
+\title{  {\Huge $ \ttlfnt{5e^{x+y}}$}: Searching over Mathematical Content in Digital Libraries}
 
@@
 \begin{minipage}{.55\textwidth}
-  \includegraphics[width=0.95\linewidth]{images/figures/results_interface.png}
+  \includegraphics[width=0.95\linewidth]{images/figures/results_interface_alt.png}
   \captionof{figure}{Result page.}
